### 2024-06-07 main.tex
Commit inicial
Retirado do Google Drive cuja a última versão era do dia 5 de junho.

\documentclass{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{subfigure}

\newcommand{\brho}{\boldsymbol{\rho}}
\newcommand{\brhop}{\boldsymbol{\rho^\prime}}
\newcommand{\Es}{\mathbf{E^S}}
\newcommand{\GS}{\mathbf{G^S}}
\newcommand{\X}{\boldsymbol{\chi}}
\newcommand{\E}{\mathbf{E}}
\newcommand{\Xo}{\boldsymbol{\bar{\chi}_o}}
\newcommand{\Xr}{\boldsymbol{\bar{\chi}_r}}

\begin{document}

    \title{To Be Decided}
    \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
        \thanks{This work has been supported by the Brazilian agencies Coordination for the Improvement of Higher Education Personnel - Brazil (CAPES) through the Academic Excellence Program (PROEX) under Grant 88887.815891/2023-00, FAPEMIG (Research Support Foundation of the State of Minas Gerais), and CNPq (The National Council for Scientific and Technological Development).}
        \thanks{A. C. Batista, R. Adriano, and L. S. Batista are with the Department of Electrical Engineering, Universidade Federal de Minas Gerais, Belo Horizonte, MG 31270-901, Brazil (e-mail: andre-costa@ufmg.br; rluiz@ufmg.br; lusoba@ufmg.br). A. C. Batista and L. S. Batista are also with Operations Research and Complex Systems Laboratory (ORCS Lab), Belo Horizonte, MG, Brazil.}}

    \maketitle

    \begin{abstract}
        To be written.
    \end{abstract}

    \begin{IEEEkeywords}
        Keyword 1, keyword 2, keyword 3. Remember: alphabetical order.
    \end{IEEEkeywords}

    \section{Introduction}\label{sec:introduction}

        \IEEEPARstart{H}{ere} we go.

        % O que é Microwave Imaging.

        % O papel dos algoritmos de inversão dentro de MWI para resolver o problema de espalhamento eletromagnético e quais desafios (ill-posedness etc). Destacar também a formulação 2D.

        % Quais classes de algoritmos e o que existe de mais novo.

        % Quais formas de avaliar soluções e quais ferramentas já existem (incluir aquele trabalho do Kurrant que é software para câncer de mama).

        % Descrever a lacuna para proposição de outros indicadores, tais como de posição e forma. Introduzir a minha proposta destacando vantagens, desvantagens e originalidade.

        % Organização do texto

	\section{Problem Statement}\label{sec:problemstatement}

		Let $D \in \mathbb{R}^2$ denote the Domain of Interest (DOI) embedded within a homogeneous, isotropic, nonmagnetic ($\mu = \mu_0 = 4\pi \times 10^{-7}$ H/m), and lossless ($\sigma = \sigma_0 = 0$ S/m) background medium with permittivity $\epsilon_b = \epsilon_{rb}\epsilon_0$, where $\epsilon_0 \approx 8.85 \times 10^{-12}$ F/m. We consider a 2D Transverse Magnetic (TMz) polarization where the DOI is illuminated by incident plane waves and assume the time convention $e^{j\omega t}$. All scatterers are located within the DOI, and the scattered field $E^s_z$ at point $\brho \in S$ outside $D$ is evaluated according to the following integral equation \cite{harrington2001time}:
		\begin{equation}
			E^s_z (\brho) = -\frac{k_b^2}{4} \int_D H_0^{(2)}(k_b|\brho-\brhop|)\chi(\brhop)E_z(\brhop) dS^\prime
		\end{equation}

		\noindent where $k_b = \omega\sqrt{\epsilon_b\mu_0} = 2\pi/\lambda_b$ is the background wave number, $\lambda_b$ is the wavelength of the incident wave, $H_0^{(2)}$ is the zero-order Hankel function of the second kind, $E_z$ is the total electric field in the DOI, and $\chi$ is the contrast function given by
		\begin{equation}
			\chi(\brho) = \frac{\epsilon_r(\brho)}{\epsilon_{rb}} - 1 - j\frac{\sigma(\brho)}{\omega\epsilon_b},
		\end{equation}

		\noindent which maps the relative permittivity $\epsilon_r(\brho)$ and conductivity $\sigma(\brho)$ distributions within $D$. It should be noted that the term $(-jk_b^2/4) H_0^{(2)}(k_b|\brho-\brhop|)$ corresponds to the Green's function in free space.

		In electromagnetic inverse scattering problems, we aim to recover the contrast function $\chi$ using a set of $N_M$ measurements of the scattered field collected for each of the $N_S$ sources. Additionally, $E_z$ is also unknown in $D$ and must be solved. For our formulation, the $N_S$ sources correspond to $N_S$ incidence angles of the plane wave, and the $N_M$ measurements are taken at $N_M$ points in $S$, arranged in a circular, equidistant array situated far from the center of the DOI by a radius $R_O$. By discretizing the DOI into $N_X \times N_Y = N$ pixels, the inverse problem is solved numerically according to the following equation:
		\begin{equation}
			E^s_{ms} = - \sum\limits_{n=1}^{N} G^S_{mn}\chi_{n}E_{ns} \label{eq:numerical}
		\end{equation}

		\noindent where $G^S$ is given according to the Richmond discretization \cite{richmond1965scattering, pastorino2010ch3}. Equation \eqref{eq:numerical} can also be expressed in matrix form:
		\begin{equation}
			\Es = \GS\X\E
		\end{equation}

		\noindent where $\Es$ is the $N_M \times N_S$ scattered field matrix, $\GS$ is the $N_M \times N$ Green's function matrix, $\X$ is the $N \times N$ contrast diagonal matrix, and $\E$ is the $N \times N_S$ total electric field matrix.

		It is important to highlight that, although assumptions are made regarding the scattered field domain and the incident field, the proposed indicators do not depend on these assumptions. They can be applied in any scenario where these entities are defined, and the assumptions in this paper serve only to clearly establish the context in which the indicators are tested.

	\section{Indicators}\label{sec:indicators}

		Once the reconstruction result of the contrast function is obtained by a given algorithm for the problem, the error in recovering the shape and location of the objects can be measured by comparing it with the original images. This means that the application of these metrics is relevant in studies where the exact response is known. Although in many real-world scenarios the imaged scatterer is unknown, applying these metrics to known cases can be valuable for comparing the performance of different algorithms and for estimating a confidence interval for the average performance of an algorithm in a given configuration. Therefore, these metrics are relevant tools that can contribute to the investigation and evaluation of algorithms for this problem.

		For the two indicators that will be explained below, the image of the original contrast function of the problem and the image reconstructed by any algorithm will be denoted by the matrices $\Xo$ and $\Xr$, both of size $N_X \times N_Y$. In other words, the elements of these matrices represent the pixels of the images.

		% Pressupostos:
		% 1. Função contraste (mapa) não seja uma função diferenciável (superfície).
		% 2. O algoritmo de reconstrução consegue discenir razoavelmente as bordas.
		% 3. No caso de múltiplos espalhadores com diferentes níveis de contraste, os menores níveis de constraste não estão abaixo da metade da diferença entre objeto de maior contraste e o fundo (**não ter contraste menor que zero**).
		% 4. Objetos de constraste diferentes não estejam sobrepostos (senão serão considerados como um objeto só).

		\subsection{Shape Error}\label{sec:indicators:shapeerror}

			% A função contraste tem valores complexos quando o meio ou os espalhadores possuem perdas. Portanto, o primeiro passo é tratar da possibilidade dos elementos das matrizes $\Xo$ e $\Xr$ terem partes reais e imaginárias. A abordagem mais simples é tomarmos o módulo das variáveis complexas como o valor de cada pixel. Esta escolha não elimina a possibilidade de que objetos com contrastes diferentes tenham o mesmo módulo. No entanto, nos casos onde somente existem materiais sem-perdas, esta abordagem não é problema porque o contraste é puramente real. Ao mesmo tempo, como o objetivo é verificar a forma dos espalhadores, o mais importante é fazer a separação entre meio-de-fundo e espalhador, sendo que o meio-de-fundo tem contraste zero. Portanto, esta escolha para simplificar a metodologia para mensurar o erro de forma não deve ter consequências relevantes em situações de verificação de desempenho do algoritmo.

			The contrast function has complex values when the medium or the scatterers have losses. Therefore, the first step is to account for the possibility that the elements of the matrices $\Xo$ and $\Xr$ have real and imaginary parts. The simplest approach is to use the magnitude of the complex variables as the value of each pixel. This choice does not eliminate the possibility that objects with different contrasts might have the same magnitude. However, in cases involving only lossless materials, this approach is not problematic because the contrast is purely real. Since the primary objective is to verify the shape of the scatterers, the critical aspect is distinguishing between the background medium and the scatterer, with the background medium having zero contrast. Thus, this approach to simplifying the methodology for measuring shape error should not have significant consequences in performance verification scenarios for the algorithm.

			% A função contraste reconstruída por muitos dos algoritmos -- tais como o BIM, DBIM, CSI, SOM, entre outros -- é comumente uma superfície contínua. Por isso, mesmo que a imagem original contenha apenas objetos de contorno bem definido e contraste homogêneo, a imagem destes objetos obtida pelos algoritmos possuem bordas suaves, i.e., o valor de contraste varia gradualmente entre o valor de meio-de-fundo e o valor do objeto. Por isso, identificar um contorno na imagem resultante é uma heurística porque é necessário escolher algum tipo de critério para definir a partir de que valor de contraste o pixel pode ser considerado como pertencente ao objeto. Por questões de simplicidade, o limiar $T$ para o qual vamos considerar que um píxel da imagem recuperada esteja dentro de um contorno de um objeto será definido como a metade da variação total do contraste na imagem, ou seja:

			The contrast function reconstructed by many algorithms -- such as BIM, DBIM, CSI, SOM, among others -- is commonly a continuous surface. Therefore, even if the original image contains only objects with well-defined boundaries and homogeneous contrast, the image of these objects obtained by the algorithms has smooth edges, i.e., the contrast value gradually varies between the background medium and the object's value. Consequently, identifying a contour in the resulting image is heuristic because it requires selecting a criterion to define the contrast value at which a pixel can be considered as belonging to the object. For simplicity, the threshold $T$ for considering a pixel in the recovered image to be within an object's contour will be defined as half of the total contrast variation in the image, i.e.:
			\begin{equation}
				T = \min(|\Xr|) + \frac{1}{2} \left[\max(|\Xr|)-\min(|\Xr|)\right]
			\end{equation}

			% Esta abordagem tem vantagens e desvantagens. Se a imagem reconstruída tiver múltiplos espalhadores no qual um ou mais deles possui um contraste abaixo desse limiar, a metodologia irá falhar em detectar o contorno deste ou destes objetos. No entanto, quando se trata de um caso onde há somente um espalhador na imagem -- o que é a maneira mais objetiva de se testar o potencial de um algoritmo em recuperar geometria, uma vez que a presença de múltiplos espalhadores pode deteriorar o desempenho de algoritmos por questões de influência das correntes induzidas em cada espalhador no espalhamento dos outros espalhadores -- é uma abordagem simples e objetiva e que não representa problemas para algoritmos que são capazes de captar bem os contornos, como métodos baseados aprendizado de máquina. Além disso, ao invés de utilizar os valores da imagem original, é mais interessante usar somente os valores da imagem reconstruída, tanto para isolar influência de erro na estimativa de contraste como para poder aplicar a métrica em métodos qualitativos que não fazem estimativa do contraste.

			This approach has advantages and disadvantages. If the reconstructed image contains multiple scatterers, and one or more of them has a contrast below this threshold, the methodology will fail to detect the contour of these objects. However, in scenarios where there is only one scatterer in the image, this approach is simple and effective. In fact, a single scatterer is the most objective way to test an algorithm's potential in recovering geometry, since the presence of multiple scatterers can degrade the algorithm's performance due to the influence of the induced currents in each scatterer on the scattering of the other. Furthermore, it poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods. Moreover, instead of using the values from the original image, it is more beneficial to use only the values from the reconstructed image, both to isolate the influence of error in the contrast estimate and to apply the metric to qualitative methods that do not estimate contrast. If, for some reason, the original contrast function involves soft boundaries of the objects, the threshold might also be applied to the original image.

			%Uma vez aplicada a etapa de limiarização, os contornos dos espalhadores podem ser determinados. Uma das técnicas que podem ser aplicadas neste caso é o algoritmo Marching Squares \cite{lorensen1987marching}. Este algoritmo é capaz de retornar um conjunto de pontos que especificam cada contorno. Vale lembrar que objetos vazados possuem dois ou mais contornos. Além disso, se o algoritmo de imageamento falhar em detectar um objeto, haverá uma discrepância no número de contornos da imagem original e da reconstruída. Por essas razões, ao invés de comparar as geometrias através de um cálculo feito a partir dos pontos de cada contorno, nós preferimos realizar a comparação baseada na quantidade de pixeis que foram classificados incorretamente. Em outras palavras, após identificarmos quais pixeis estão dentro de cada contorno em cada imagem, podemos verificar quais deles faziam parte dos espalhadores na imagem original e não foram captados na imagem reconstruída (falso-negativo) e quais deles não faziam parte dos espalhadores na imagem original mas foram considerados na reconstruída (falso-positivo). Um dos questionamentos que pode surgir dessa escolha é por que não aplicar diretamente o cálculo de falsos-positivos e falsos-negativos após a limiarização. Uma das razões é que, normalmente, imagens originais e reconstruídas têm resoluções diferentes. Embora o método de interpolação pelo vizinho mais próxima seja uma alternativa para essa tarefa, a abordagem escolhida pode ser mais adequada para captar e preservar contornos de objetos principalmente quando a resolução da imagem reconstruída é bem inferior, conforme exemplificado na Fig. \ref{fig:contourmotivation}.

			Once the thresholding step is applied, the contours of the scatterers can be determined. One of the techniques suitable for this task is the Marching Squares algorithm \cite{lorensen1987marching}. This algorithm efficiently returns a set of points that delineate each contour. It is important to note that hollow objects may have two or more contours. Additionally, if the imaging algorithm fails to detect an object, a discrepancy will arise in the number of contours between the original and reconstructed images.

			For these reasons, instead of comparing the geometries through calculations based on the points of each contour, we prefer to perform the comparison based on the number of pixels that were misclassified. Specifically, after identifying which pixels fall within each contour in each image, we can determine which pixels belonged to the scatterers in the original image but were not captured in the reconstructed image (false negatives) and which pixels did not belong to the scatterers in the original image but were classified as such in the reconstructed image (false positives).

			A potential question that may arise from this choice is why not directly calculate false positives and false negatives immediately after thresholding. One reason is that original and reconstructed images typically have different resolutions. While the nearest neighbor interpolation method is an alternative for addressing this issue, the chosen approach may be more effective for capturing and preserving object contours, particularly when the resolution of the reconstructed image is significantly lower. This is illustrated in Fig. \ref{fig:contourmotivation}.

			\begin{figure}[!t]
				\centering
				\subfigure[]{\includegraphics[width=.49\columnwidth]{./figs/batis01}}
				\subfigure[]{\includegraphics[width=.49\columnwidth]{./figs/batis02}} \\
				\subfigure[]{\includegraphics[width=.49\columnwidth]{./figs/batis03}}
				\subfigure[]{\includegraphics[width=.49\columnwidth]{./figs/batis04}}
				\caption{An example illustrating the differences between nearest neighbor interpolation and the adopted contour detection methodology. (a) Original image of the scatterer (resolution 100x100); (b) Image reconstructed by an imaging algorithm after thresholding (20x20); (c) Image reconstructed to the original resolution using nearest neighbor interpolation; (d) Image reconstructed to the original resolution using contour identification.}
				\label{fig:contourmotivation}
			\end{figure}

		\subsection{Position Error}\label{sec:indicators:positionerror}

	\section{Computational Experiments}\label{sec:results}

		% Destacar aqui tudo que for comum a todos experimentos. Por exemplo, a biblioteca.

		\subsection{Shape Recovering Study}\label{sec:results:shape}

			% Destacar aqui tudo o que for comum a esse tipo de estudo.

			\subsubsection{Single scatter}\label{sec:results:shape:star}

			\subsubsection{Varying contrast}\label{sec:results:shape:varying}

			\subsection{Average performance}\label{sec:results:shape:average}

		\subsection{Position Detection Study}\label{sec:results:position}

			\subsubsection{Single scatter}\label{sec:results:position:single}

			\subsubsection{Multiple scatterers}\label{sec:results:position:multiple}

			\subsubsection{Average performance}\label{sec:results:position:benchmark}

    \section{Conclusion}\label{sec:conclusion}
        A conclusion section is not required. Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion. A  conclusion might elaborate on the importance of the work or suggest applications and extensions. \cite{chen2018computational}

    \appendices

    \section*{Acknowledgment}

        Use the singular heading even if you have many acknowledgments. In most  cases, sponsor and financial support acknowledgments are placed in the  unnumbered footnote on the first page, not here.

    \bibliographystyle{IEEEtran}
    \bibliography{mybib}

    % \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a1.png}}]
    %     {First A. Author} (M'76--SM'81--F'87) and all authors may include biographies. Biographies are often not included in conference-related papers. This author became a Member (M) of IEEE in 1976, a Senior Member (SM) in 1981, and a Fellow (F) in 1987. The first paragraph may contain a place and/or date of birth (list place, then date). Next, the author's educational background is listed. The degrees should be listed with type of degree in what field, which institution, city, state, and country, and year the degree was earned. The author's major field of study should be lower-cased.

    %     The second paragraph uses the pronoun of the person (he or she) and not the author's last name. It lists military and work experience, including summer and fellowship jobs. Job titles are capitalized. The current job must have a  location; previous positions may be listed without one. Information concerning previous publications may be included. Try not to list more than three books or published articles. The format for listing publishers of a book within the biography is: title of book (publisher name, year) similar to a reference. Current and previous research interests end the paragraph. The third paragraph begins with the author's title and last name (e.g., Dr.\ Smith, Prof.\ Jones, Mr.\ Kajor, Ms.\ Hunter). List any memberships in professional societies other than the IEEE. Finally, list any awards and work for IEEE committees and publications. If a photograph is provided, it should be of good quality, and professional-looking. Following are two examples of an author's biography.
    % \end{IEEEbiography}

    % \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a2.png}}]
    %     {Second B. Author} was born in Greenwich Village, New York, NY, USA in 1977. He received the B.S. and M.S. degrees in aerospace engineering from the University of Virginia, Charlottesville, in 2001 and the Ph.D. degree in mechanical engineering from Drexel University, Philadelphia, PA, in 2008.

    %     From 2001 to 2004, he was a Research Assistant with the Princeton Plasma Physics Laboratory. Since 2009, he has been an Assistant Professor with the Mechanical Engineering Department, Texas A{\&}M University, College Station. He is the author of three books, more than 150 articles, and more than 70 inventions. His research interests include high-pressure and high-density nonthermal plasma discharge processes and applications, microscale plasma discharges, discharges in liquids, spectroscopic diagnostics, plasma propulsion, and innovation plasma applications. He is an Associate Editor of the journal \emph{Earth, Moon, Planets}, and holds two patents.

    %     Dr. Author was a recipient of the International Association of Geomagnetism and Aeronomy Young Scientist Award for Excellence in 2008, and the IEEE Electromagnetic Compatibility Society Best Symposium Paper Award in 2011. 
    % \end{IEEEbiography}

    % \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{a3.png}}]
    %     {Third C. Author, Jr.} (M'87) received the B.S. degree in mechanical engineering from National Chung Cheng University, Chiayi, Taiwan, in 2004 and the M.S. degree in mechanical engineering from National Tsing Hua University, Hsinchu, Taiwan, in 2006. He is currently pursuing the Ph.D. degree in mechanical engineering at Texas A{\&}M University, College Station, TX, USA.

    %     From 2008 to 2009, he was a Research Assistant with the Institute of Physics, Academia Sinica, Tapei, Taiwan. His research interest includes the development of surface processing and biological/medical treatment techniques using nonthermal atmospheric pressure plasmas, fundamental study of plasma sources, and fabrication of micro- or nanostructured surfaces.

    %     Mr. Author's awards and honors include the Frew Fellowship (Australian Academy of Science), the I. I. Rabi Prize (APS), the European Frequency and Time Forum Award, the Carl Zeiss Research Award, the William F. Meggers Award and the Adolph Lomb Medal (OSA).
    % \end{IEEEbiography}

\end{document}

% Figure example.
\begin{figure}[!t]
    \centerline{\includegraphics[width=\columnwidth]{fig1.png}}
    \caption{Magnetization as a function of applied field. It is good practice to explain the significance of the figure in the caption.}
    \label{example}
\end{figure}

% Table example.
\begin{table}
    \caption{Units for Magnetic Properties}
    \label{table}
    \setlength{\tabcolsep}{3pt}
    \begin{tabular}{|p{25pt}|p{75pt}|p{115pt}|}
        \hline
        Symbol& Quantity& Conversion from Gaussian and \par CGS EMU to SI $^{\mathrm{a}}$ \\\hline
        $\Phi $& magnetic flux& 1 Mx $\to  10^{-8}$ Wb $= 10^{-8}$ V$\cdot $s \\
        $B$& magnetic flux density, \par magnetic induction& 1 G $\to  10^{-4}$ T $= 10^{-4}$ Wb/m$^{2}$ \\
        $H$& magnetic field strength& 1 Oe $\to  10^{3}/(4\pi )$ A/m \\
        $m$& magnetic moment& 1 erg/G $=$ 1 emu \par $\to 10^{-3}$ A$\cdot $m$^{2} = 10^{-3}$ J/T \\
        $M$& magnetization& 1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 10^{3}$ A/m \\
        4$\pi M$& magnetization& 1 G $\to  10^{3}/(4\pi )$ A/m \\
        $\sigma $& specific magnetization& 1 erg/(G$\cdot $g) $=$ 1 emu/g $\to $ 1 A$\cdot $m$^{2}$/kg \\
        $j$& magnetic dipole \par moment& 1 erg/G $=$ 1 emu \par $\to 4\pi \times  10^{-10}$ Wb$\cdot $m \\
        $J$& magnetic polarization& 1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 4\pi \times  10^{-4}$ T \\
        $\chi , \kappa $& susceptibility& 1 $\to  4\pi $ \\
        $\chi_{\rho }$& mass susceptibility& 1 cm$^{3}$/g $\to  4\pi \times  10^{-3}$ m$^{3}$/kg \\
        $\mu $& permeability& 1 $\to  4\pi \times  10^{-7}$ H/m \par $= 4\pi \times  10^{-7}$ Wb/(A$\cdot $m) \\
        $\mu_{r}$& relative permeability& $\mu \to \mu_{r}$ \\
        $w, W$& energy density& 1 erg/cm$^{3} \to  10^{-1}$ J/m$^{3}$ \\
        $N, D$& demagnetizing factor& 1 $\to  1/(4\pi )$ \\\hline
        \multicolumn{3}{p{251pt}}{Vertical lines are optional in tables. Statements that serve as captions for the entire table do not need footnote letters. }\\
        \multicolumn{3}{p{251pt}}{$^{\mathrm{a}}$Gaussian units are the same as cg emu for magnetostatics; Mx $=$ maxwell, G $=$ gauss, Oe $=$ oersted; Wb $=$ weber, V $=$ volt, s $=$ second, T $=$ tesla, m $=$ meter, A $=$ ampere, J $=$ joule, kg $=$ kilogram, H $=$ henry.}
    \end{tabular}
    \label{tab1}
\end{table}

### 2024-07-23 main.tex
Teste do uso do git para a escrita do artigo
Pequenos polimentos na seção 3

@@
 
-		Once the reconstruction result of the contrast function is obtained by a given algorithm for the problem, the error in recovering the shape and location of the objects can be measured by comparing it with the original images.
+		Once the result of the contrast function reconstruction is obtained by a given algorithm, the error in recovering the shape and location of the objects can be measured by comparing it with the original images.
 This means that the application of these metrics is relevant in studies where the exact response is known.
 Although in many real-world scenarios the imaged scatterer is unknown, applying these metrics to known cases can be valuable for comparing the performance of different algorithms and for estimating a confidence interval for the average performance of an algorithm in a given configuration.
-Therefore, these metrics are relevant tools that can contribute to the investigation and evaluation of algorithms for this problem.
+Therefore, these metrics are relevant tools that can contribute to the investigation and evaluation of algorithms for the problem.
 
@@
 
-			The contrast function reconstructed by many algorithms -- such as BIM, DBIM, CSI, SOM, among others -- is commonly a continuous surface.
-Therefore, even if the original image contains only objects with well-defined boundaries and homogeneous contrast, the image of these objects obtained by the algorithms has smooth edges, i.e., the contrast value gradually varies between the background medium and the object's value.
+			The contrast function reconstructed by many algorithms -- such as BIM, DBIM, CSI, SOM, among others -- is commonly a discretized approximation of a continuous surface.
+Therefore, even if the original image contains only objects with well-defined boundaries and homogeneous contrast, the image of these objects obtained by the algorithms will have frequently smooth edges, i.e., the contrast value gradually varies between the background medium and the object's value.
 Consequently, identifying a contour in the resulting image is heuristic because it requires selecting a criterion to define the contrast value at which a pixel can be considered as belonging to the object.
@@
 In fact, a single scatterer is the most objective way to test an algorithm's potential in recovering geometry, since the presence of multiple scatterers can degrade the algorithm's performance due to the influence of the induced currents in each scatterer on the scattering of the other.
-Furthermore, it poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods.
+Furthermore, this approach poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods.
 Moreover, instead of using the values from the original image, it is more beneficial to use only the values from the reconstructed image, both to isolate the influence of error in the contrast estimate and to apply the metric to qualitative methods that do not estimate contrast.

### 2024-07-23 main.tex
Explicando o final do indicador de forma

@@
 
+            The sum of false negatives and false positives can be easily obtained by applying the XOR operation between the two images.
+Then, we can compute the shape error as the ratio between the number of incorrectly classified pixels and the total number of pixels that are part of the scatterers in the original image.
+Additionally, if we consider the shape error in percentage values, we can then define the indicator $\zeta_S$ as
+
+            \begin{equation}
+                \zeta_S = \frac{\text{FP} + \text{FN}}{\text{TP}} \times 100\%, \label{eq:shapeerror}
+            \end{equation}
+
+            \noindent where $\text{FP}$ and $\text{FN}$ are the numbers of false-positive and false-negative pixels, respectively, and $\text{TP}$ is the total number of pixels that are part of the scatterers in the original image.
+Therefore, the indicator assumes values greater than or equal to zero.
+Note that values greater than 100\% are also possible, indicating that the reconstructed image has more incorrectly classified pixels than the total number of pixels that make up the scatterers in the original image.
+This can occur more frequently when the number of pixels of the scatterer in the original image is small.
+
 		\subsection{Position Error}\label{sec:indicators:positionerror}

### 2024-07-26 main.tex
Escrevi sobre o indicador de posição

@@
 \usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithm}
 \usepackage{algorithmic}
@@
 
+            % A metodologia para o cálculo do erro de detecção de posição possui similaridades.
+Da mesma forma como no cálculo de erro de forma, o cálculo do erro de posição também considera o valor absoluto do contraste das imagens e a mesma operação de limiarização.
+As razões para aplicar a mesma abordagem são as mesmas.
+
+            The methodology for calculating the position detection error shares similarities with that of shape error calculation.
+As it is done when computing the shape error, the position error calculation also uses the absolute value of the image contrasts and applies the same thresholding operation.
+The reasons for this approach are the same.
+
+            % A diferença é que o cálculo do erro de posição se baseia na comparação do ponto médio de pixeis classificados como objetos pelo operador de limiarização aplicado em cada imagem.
+Ou seja, para cada coordenada na imagem, é calculado a média dos valores de coordenada onde os objetos estão.
+Para isso, não é necessário aplicar o cálculo de contornos, uma vez que, mesmo tendo resoluções diferentes, os pontos das coordenadas estão dentro dos mesmos limites.
+
+            The key difference lies in the method of position error calculation, which is based on comparing the centroid of pixels classified as objects by the thresholding operation in each image.
+Specifically, the centroid for each image is determined by averaging the coordinates of the pixels that constitute the objects.
+This method does not require contour detection, as the coordinate points are within the same boundaries for both images, even when resolutions differ.
+
+            % Com base nos pontos médios em cada imagem, o indicador é definido como a distância euclidiana entre o par de pontos.
+Vale à pena destacar que os pontos são calculados em um intervalo de 0 a 1, onde 0 representa a origem da imagem e 1 representa o final da imagem.
+Desta forma, se multiplicarmos a distância por 100, podemos interpretar a distância como um erro percentual em relação ao tamanho da imagem.
+Em outra palavras, o indicador significa o quanto o algoritmo errou na localização dos objetos em relação ao tamanho da imagem.
+Isso permite também que o indicador seja usado em um conjunto de testes que tenham diferentes tamanhos de domínio.
+
+            The position error indicator is then defined as the Euclidean distance between the centroids in the two images.
+It is important to note that these centroids are normalized within a range of 0 to 1, where 0 represents the image's origin and 1 represents its end.
+By multiplying this distance by 100, the error can be interpreted as a percentage relative to the image size.
+Thus, the indicator quantifies the error in object localization relative to the image size, allowing its application across test sets with varying domain sizes.
+Therefore, the position error indicator $\zeta_P$ is defined as:
+            \begin{equation}
+                \zeta_P = \sqrt{(x_c^R - x_c^O)^2 + (y_c^R-y_c^O)^2} \times 100\%, \label{eq:positionerror}
+            \end{equation}
+
+            \noindent where $(x_c^R, y_c^R)$ and $(x_c^O, y_c^O)$ are the centroids of the reconstructed and original images, respectively.
+
+            % De fato, erros na recuperação da geometrias dos objetos podem influenciar diretamente no cálculo no erro de posição.
+Por exemplo, se um objeto no formato de uma estrela de cinco pontas fosse reconstruído com uma de suas pontas entortada, isso afetaria o ponto médio do objeto e, consequentemente, o erro de posição.
+No entanto, isso é esperado, uma vez que qualquer critério para considerar a posição de um objeto leva em conta os píxeis que o descrevem, assim como sua geometria.
+Por outro lado, o indicador proposto, além de ser simples, pode ser aplicado também em imagens com múltiplos objetos.
+
+            It should be noted that inaccuracies in the reconstructed geometry of objects can significantly influence the position error calculation.
+For example, if a star-shaped object with five points is reconstructed with one point distorted, this distortion will affect the object's centroid, thereby impacting the position error.
+However, this effect is expected, as any criterion for determining an object's position inherently considers the pixels defining it, as it is for its geometry.
+Furthermore, the proposed indicator is straightforward and versatile, applicable even in scenarios involving images with multiple objects.
+
 	\section{Computational Experiments}\label{sec:results}

### 2024-07-29 main.tex
Escrevi primeiros parágrafos da seção de resultados

@@
 
-		% Destacar aqui tudo que for comum a todos experimentos. Por exemplo, a biblioteca.
+		% Os experimentos descritos neste artigo tem por objetivo ilustrar a aplicação dos indicadores propostos.
+Por isso, os experimentos foram desenhados para reforçar as possibilidades que existem com a introdução destes indicadores, e não necessariamente para obter resultados que representem novidades significativas na literatura.
+No entanto, as conclusões tiradas dos experimentos podem servir como base para outras investigações pela comunidade.
+
+        The experiments presented in this article are intended to illustrate the application of the proposed indicators.
+The design of these experiments focuses on demonstrating the potential utility of these indicators, rather than achieving pioneering results in the field.
+Nevertheless, the findings from these experiments can still provide a foundation for further research by the scientific community.
+
+        % Os experimentos foram realizados por meio da biblioteca de código-aberto EISPY2D \cite{batista2022eispy2d}, a qual foi construída especificamente para desenhar e medir o desempenho de algoritmos para o problema inverso de espalhamento eletromagnético.
+Ambos indicadores serão abordados e, para cada abordagem, foram realizados dois estudos de caso (um básico e outro explorando alguma particularidade) e um estudo de benchmarking.
+Os estudos de caso tem por objetivo medir o desempenho em situações específicas, enquanto o estudo de benchmarking permite uma maior generalização dos resultados.
+
+        The experiments were conducted using the open-source library EISPY2D \cite{batista2022eispy2d}, specifically developed to design and evaluate algorithms for the inverse electromagnetic scattering problem.
+Both indicators will be analyzed, with each approach featuring two case studies (one fundamental and the other exploring a particular aspect) as well as a benchmarking study.
+The case studies aim to assess performance in specific scenarios, while the benchmarking study facilitates broader generalization of the results.
 
@@
 
-			\subsection{Average performance}\label{sec:results:shape:average}
+			\subsubsection{Average performance}\label{sec:results:shape:average}
 

### 2024-08-02 main.tex
Escrevendo resultados

@@
 
+        Para todos os experimentos, o $\lambda_b$ foi definido em 1 [m].
+O ruído acrescentado nos dados sempre foi de 5\%.
+A permissividade relativa do meio de fundo sempre foi fixada em 1.
+A amplitude da onda incidente sempre foi fixada em 1 [V/m].
+
 		\subsection{Shape Recovering Study}\label{sec:results:shape}
 
-			% Destacar aqui tudo o que for comum a esse tipo de estudo.
+			Para estudar o erro de forma, dois estudos de caso foram realizados.
+O primeiro estudo de caso consiste em um único espalhador com contraste homogêneo.
+O segundo estudo de caso envolve um espalhador com contraste variável.
+Ambos estudos de caso foram escolhidos para ilustrar a aplicação do indicador proposto em cenários comuns em problemas de espalhamento eletromagnético.
+O estudo de benchmarking foi realizado para medir o desempenho médio dos algoritmos em situações mais gerais.
+
+            Em todos os casos, as dimensões do DoI foram ajustadas para $2\lambda_b\times2\lambda_b$. O raio de distância dos pontos de medição $R_O$ foi fixado em 4$\lambda_b$.
 
 			\subsubsection{Single scatter}\label{sec:results:shape:star}
+
+                O primeiro estudo de caso foi formulado com objetivo de verificar a aplicabilidade do indicador em um cenário simples, onde diferentes algoritmos pudessem ser aplicados.
+O estudo considera um espelhador com formato de uma estrela de cinco pontas posicionada no centro da imagem.
+Esta escolha foi feita com o objetivo de escolher uma geometria que, ao mesmo tempo que é simétrica e bem definida, possui um número maior de vértices que geometria mais comuns, como quadrados ou triângulos.
+O contraste foi fixado em 0.25 e o raio do centro do espalhador até os vértices mais distantes foi fixado em 0.9$\lambda_b$.
+Foram considerados 80 pontos de medição ($N_M$) e 80 ângulos de incidência ($N_S$).
+
+                % The first case study involves a single scatterer with homogeneous contrast.
+Fig.
+\ref{fig:star} illustrates the geometry of the problem.
+The scatterer is a five-point star with a radius of 0.1 m and a contrast of 0.5.
+The original image was discretized into a 100x100 pixel grid.
+Fig.
+\ref{fig:star} also shows the image reconstructed by an imaging algorithm.
+Table \ref{tab:star} presents the results obtained for shape and position errors.
+The results demonstrate that the algorithm successfully recovered the scatterer's shape with a shape error of 0.5\% and a position error of 0.1\%.
+These findings indicate that the algorithm accurately recovered the scatterer's shape and position.
+
+                % \begin{figure}[!t]
+                %     \centering
+                %     \includegraphics[width=.8\columnwidth]{./figs/star}
+                %     \caption{Single scatterer geometry.}
+                %     \label{fig:star}
+                % \end{figure}
+
+                % \begin{table}[!t]
+                %     \centering
+                %     \caption{Results for the single scatterer case study.}
+                %     \label{tab:star}
+                %     \begin{tabular}{|c|c|c|}
+                %         \hline
+                %         Indicator & Value & Unit \\
+                %         \hline
+                %         $\zeta_S$ & 0.5 & \% \\
+                %         $\zeta_P$ & 0.1 & \% \\
+                %         \hline
+                %     \end{tabular}   
+                % \end{table}
 

### 2024-08-06 main.tex
Escrevendo resultados da estrela

@@
 A amplitude da onda incidente sempre foi fixada em 1 [V/m].
+A sintetização dos dados foi feita através do algoritmo MoM-CG-FFT \cite{su1987calculation} com 5000 iterações.
 
@@
 
-			Para estudar o erro de forma, dois estudos de caso foram realizados.
+			% Para estudar o erro de forma, dois estudos de caso foram realizados.
 O primeiro estudo de caso consiste em um único espalhador com contraste homogêneo.
@@
 
-            Em todos os casos, as dimensões do DoI foram ajustadas para $2\lambda_b\times2\lambda_b$. O raio de distância dos pontos de medição $R_O$ foi fixado em 4$\lambda_b$.
+            To evaluate shape error, two case studies were conducted.
+The first case study involves a single scatterer with homogeneous contrast, while the second case study involves a scatterer with variable contrast.
+These case studies were selected to demonstrate the application of the proposed indicator in typical scenarios encountered in electromagnetic scattering problems.
+Additionally, a benchmarking study was performed to assess the average performance of algorithms in more general situations.
+
+            % Em todos os casos, as dimensões do DoI foram ajustadas para $2\lambda_b\times2\lambda_b$. O raio de distância dos pontos de medição $R_O$ foi fixado em 4$\lambda_b$.
+
+            In all instances, the dimensions of the DoI were set to $2\lambda_b\times2\lambda_b$, and the measurement points' distance radius $R_O$ was fixed at $4\lambda_b$.
 
@@
 
-                O primeiro estudo de caso foi formulado com objetivo de verificar a aplicabilidade do indicador em um cenário simples, onde diferentes algoritmos pudessem ser aplicados.
+                % O primeiro estudo de caso foi formulado com objetivo de verificar a aplicabilidade do indicador em um cenário simples, onde diferentes algoritmos pudessem ser aplicados.
 O estudo considera um espelhador com formato de uma estrela de cinco pontas posicionada no centro da imagem.
@@
 Foram considerados 80 pontos de medição ($N_M$) e 80 ângulos de incidência ($N_S$).
+Nessas condições, o Grau de Não Linearidade (DNL) do teste vale 0.12, o qual é significativamente menor que o limiar em que a Aproximação de Born deixa de ser aplicável, i.e., 1 \cite{bucci2001degree}.
+O campo espalhado foi sintetizado com base numa discretização de 120$\times$120 pixels da imagem original e todas as reconstruções foram feitas com base numa discretização de 40$\times$40 pixels.
+
+                The first case study was designed to evaluate the applicability of the proposed indicator in a straightforward scenario where various algorithms could be applied.
+This case study features a scatterer shaped like a five-pointed star, centrally positioned within the image.
+This choice was made to select a geometry that, while symmetric and well-defined, has more vertices compared to more common shapes such as squares or triangles.
+The contrast was set to 0.25, and the radius from the center of the scatterer to the farthest vertices was set to 0.9$\lambda_b$.
+A total of 80 measurement points ($N_M$) and 80 incidence angles ($N_S$) were used.
+Under these conditions, the Degree of Nonlinearity (DNL) for the test is 0.12, which is significantly lower than the threshold beyond which the Born Approximation becomes inapplicable, i.e., 1 \cite{bucci2001degree}.
+The scattered field was synthesized using a discretization of 120$\times$120 pixels for the original image, and all reconstructions were performed using a discretization of 40$\times$40 pixels.
+
+                % Os seguintes algoritmos e suas repectivas configurações foram considerados neste estudo:
+                % \begin{itemize}
+                %     \item Linear Sampling Method (LSM):
+                %     \begin{itemize}
+                %         \item Limiar: 0.7;
+                %         \item Método de Regularização: Gradiente Conjugado com 300 iterações.
+                %     \end{itemize}
+                %     \item Orthogonality Sampling Method (OSM):
+                %     \begin{itemize}
+                %         \item Limiar: 0.35;
+                %     \end{itemize}
+                %     \item Born Iterative Method (BIM):
+                %     \begin{itemize}
+                %         \item Método de Regularização: Gradiente Conjugado com 300 iterações.
+                %         \item Critério de Parada: 30 iterações.
+                %     \end{itemize}
+                %     \item Contrast Source Inversion (CSI):
+                %     \begin{itemize}
+                %         \item Critério de Parada: 300 iterações.
+                %     \end{itemize}
+                %     \item Subspace Optimization Method (SOM):
+                %     \begin{itemize}
+                %         \item Critério de Parada: 30 iterações.
+                %         \item Índice de corte de autovalores: 5.
+                %     \end{itemize}
+                % \end{itemize}
+
+                The following algorithms and their configurations were considered for this study:
+                \begin{itemize}
+                    \item Linear Sampling Method (LSM):
+                    \begin{itemize}
+                        \item Threshold: 0.7;
+                        \item Regularization Method: Conjugate Gradient with 300 iterations.
+                    \end{itemize}
+                    \item Orthogonality Sampling Method (OSM):
+                    \begin{itemize}
+                        \item Threshold: 0.35;
+                    \end{itemize}
+                    \item Born Iterative Method (BIM):
+                    \begin{itemize}
+                        \item Regularization Method: Conjugate Gradient with 300 iterations.
+                        \item Stopping Criterion: 30 iterations.
+                    \end{itemize}
+                    \item Contrast Source Inversion (CSI):
+                    \begin{itemize}
+                        \item Stopping Criterion: 300 iterations.
+                    \end{itemize}
+                    \item Subspace Optimization Method (SOM):
+                    \begin{itemize}
+                        \item Stopping Criterion: 30 iterations.
+                        \item Eigenvalue Cutoff Index: 5.
+                    \end{itemize}
+                \end{itemize}
 

### 2024-08-21 main.tex
Inserção das imagens reconstruídas do primeiro estudo de caso dos experimentos sobre o indicador de forma

@@
 
-			\subsubsection{Single scatter}\label{sec:results:shape:star}
+			\subsubsection{Single scatterer}\label{sec:results:shape:star}
 
@@
 
-                The following algorithms and their configurations were considered for this study:
+                For this experiment, the following algorithms were considered: LSM, OSM, BIM, CSI, and SOM.
+Their parameters were chosen after empirical tests that aimed to achieve their best performance.
+The configurations for each algorithm are as follows:
                 \begin{itemize}
@@
                 \end{itemize}
+
+                The images reconstructed by each algorithm are shown in Fig. \ref{fig:shape:single:recons}.
+
+                \begin{figure*}
+                    \subfigure[Ground-Truth]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/0}}
+                    \subfigure[LSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/1}}
+                    \subfigure[OSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/2}} \\
+                    \subfigure[BIM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/3}}
+                    \subfigure[CSI]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/4}}
+                    \subfigure[SOM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/5}}
+                    \caption{Shape recovering study, single scatterer: ground-truth and reconstructed images by each algorithm.}
+                    \label{fig:shape:single:recons}
+                \end{figure*}
 

### 2025-07-15 main.tex
Não consegui padronizar todas as colobars da fig do primeiro resultado
Inclusão dos códigos

@@
 \usepackage{subfigure}
+\usepackage{xcolor}
 
@@
 
-        Para todos os experimentos, o $\lambda_b$ foi definido em 1 [m].
-O ruído acrescentado nos dados sempre foi de 5\%.
-A permissividade relativa do meio de fundo sempre foi fixada em 1.
-A amplitude da onda incidente sempre foi fixada em 1 [V/m].
-A sintetização dos dados foi feita através do algoritmo MoM-CG-FFT \cite{su1987calculation} com 5000 iterações.
+        For all experiments, the following common parameters were used: $\lambda_b$ = 1 m, noise level = 5\%, relative permittivity of the background medium $\epsilon_{rb}$ = 1, and incident wave amplitude = 1 V/m.
+Data synthesis was performed using the MoM-CG-FFT algorithm \cite{su1987calculation} with 5000 iterations.
 

### 2025-07-15 eispy2d/library/analytical.py

@@ -1,0 +1,451 @@
+r"""Method of Moments - Conjugate-Gradient FFT Method.
+
+This module provides the implementation of Method of Moments (MoM) with
+the Conjugated-Gradient FFT formulation. It solves the forward problem
+following the Forward Solver abstract class.
+
+References
+----------
+.. [1] P. Zwamborn and P. M. van den Berg, "The three dimensional weak
+   form of the conjugate gradient FFT method for solving scattering
+   problems," in IEEE Transactions on Microwave Theory and Techniques,
+   vol. 40, no. 9, pp. 1757-1766, Sept. 1992, doi: 10.1109/22.156602.
+
+.. [2] Chen, Xudong. "Computational methods for electromagnetic inverse
+   scattering". John Wiley & Sons, 2018.
+"""
+
+import pickle
+import numpy as np
+from numpy import pi
+from scipy.constants import epsilon_0, mu_0
+from scipy.special import jv, jvp, hankel2, h2vp
+import forward as fwr
+import inputdata as ipt
+import configuration as cfg
+import error
+from matplotlib import pyplot as plt
+from joblib import Parallel, delayed
+
+
+PERFECT_DIELECTRIC_PROBLEM = 'perfect_dieletric'
+PERFECT_CONDUCTOR_PROBLEM = 'perfect_conductor'
+
+
+class Analytical(fwr.ForwardSolver):
+    """Method of Moments - Conjugated-Gradient FFT Method.
+
+    This class implements the Method of Moments following the
+    Conjugated-Gradient FFT formulation.
+
+    Attributes
+    ----------
+        MAX_IT : int
+            Maximum number of iterations.
+        TOL : float
+            Tolerance level of error.
+    """
+
+    def __init__(self, contrast=None, radius=None, position=[0, 0]):
+        """Create the object.
+
+        Parameters
+        ----------
+            configuration : string or :class:`Configuration`:Configuration
+                Either a configuration object or a string with the name
+                of file in which the configuration is saved. In this
+                case, the file path may also be provided.
+
+            configuration_filepath : string, optional
+                A string with the path to the configuration file (when
+                the file name is provided).
+
+            tolerance : float, default: 1e-6
+                Minimum error tolerance.
+
+            maximum_iteration : int, default: 10000
+                Maximum number of iterations.
+        """
+        super().__init__()
+        self.name = "Analytical Solution to Cylinder Scattering"
+        self.contrast = contrast
+        self.radius = radius
+        self.position = position
+
[…]

### 2025-07-15 eispy2d/library/bornapprox.py

@@ -1,0 +1,102 @@
+# Standard libraries
+import sys
+import pickle
+import time as tm
+from numpy import pi
+
+# Developed libraries
+import deterministic as dtm
+import mom_cg_fft as mom
+import configuration as cfg
+import result as rst
+
+REGULARIZATION = 'regularization'
+FORWARD = 'forward'
+
+class FirstOrderBornApproximation(dtm.Deterministic):
+    def __init__(self, regularization, forward=mom.MoM_CG_FFT(), alias='ba',
+                 import_filename=None, import_filepath=''):
+        if import_filename is not None:
+            self.importdata(import_filename, import_filepath)
+        else:
+            super().__init__(alias=alias, parallelization=False)
+            self.name = 'First-Order Born Approximation'
+            self.regularization = regularization
+            self.forward = forward
+
+    def solve(self, inputdata, discretization, print_info=True,
+              print_file=sys.stdout):
+        result = super().solve(inputdata, discretization,
+                               print_info=print_info, print_file=print_file)
+
+        incident_field = self.forward.incident_field(discretization.elements,
+                                                     inputdata.configuration)
+        
+        tic = tm.time()
+        contrast = discretization.solve(scattered_field=inputdata.scattered_field,
+                                        total_field=incident_field,
+                                        linear_solver=self.regularization)
+        execution_time = tm.time()-tic
+
+
+        scattered_field = discretization.scattered_field(contrast=contrast,
+                                                         total_field=incident_field)
+        total_field = self.forward.incident_field(inputdata.resolution,
+                                                  inputdata.configuration)
+        contrast = discretization.contrast_image(contrast,
+                                                 inputdata.resolution)
+
+        result.update_error(inputdata, scattered_field=scattered_field,
+                            total_field=total_field, contrast=contrast)
+        result.scattered_field = scattered_field
+        result.total_field = incident_field
+
+        if not inputdata.configuration.good_conductor:
+            result.rel_permittivity = cfg.get_relative_permittivity(
+                contrast, inputdata.configuration.epsilon_rb
+            )
+        if not inputdata.configuration.perfect_dielectric:
+            result.conductivity = cfg.get_conductivity(
+                contrast, 2*pi*inputdata.configuration.f,
+                inputdata.configuration.epsilon_rb,
+                inputdata.configuration.sigma_b
+            )
+        if rst.EXECUTION_TIME in inputdata.indicators:
[…]

### 2025-07-15 eispy2d/library/casestudy.py

@@ -1,0 +1,1368 @@
+import sys
+import numpy as np
+from joblib import Parallel, delayed
+import pickle
+import multiprocessing
+from matplotlib import pyplot as plt
+from matplotlib import colors
+
+import inputdata as ipt
+import result as rst
+import experiment as exp
+import deterministic as dtm
+import stochastic as stc
+import statistics as sts
+import error
+
+TEST = 'test'
+STOCHASTIC_RUNS = 's_nexec'
+SAVE_STOCHASTIC_RUNS = 's_save'
+
+PARALLELIZE_METHOD = 'method'
+PARALLELIZE_EXECUTIONS = 'executions'
+PERMITTIVITY = 'epsilon_r'
+CONDUCTIVITY = 'sigma'
+BOTH_PROPERTIES = 'both'
+CONTRAST = 'contrast'
+ALL_EXECUTIONS = 'all'
+BEST_EXECUTION = 'best'
+
+class CaseStudy(exp.Experiment):
+
+    @property
+    def test(self):
+        return self._test
+
+    @test.setter
+    def test(self, new):
+        if new is None:
+            self._test = None
+            self._test_available = False
+        elif type(new) is ipt.InputData:
+            self._test = new.copy()
+            self._test_available = True
+        elif type(new) is str:
+            self._test = new
+            self._test_available = False
+        else:
+            raise error.WrongTypeInput('CaseStudy.test', 'new object',
+                                       'None or InputData or str',
+                                       str(type(new)))
+
+    def __init__(self, name=None, method=None, discretization=None, test=None,
+                 stochastic_runs=30, save_stochastic_runs=False,
+                 import_filename=None, import_filepath=''):
+        if import_filename is not None:
+            self.importdata(import_filename, import_filepath)
+        else:
+            super().__init__(name, method, discretization)
+            self.test = test
+            self.s_nexec = stochastic_runs
+            self.s_save = save_stochastic_runs
+    
+    def importdata(self, file_name, file_path=''):
+        data = super().importdata(file_name, file_path)
+        self.test = data[TEST]
+        self.s_nexec = data[STOCHASTIC_RUNS]
+        self.s_save = data[SAVE_STOCHASTIC_RUNS]
+
+    def save(self, file_path='', save_test=False):
+        data = super().save(file_path)
+
+        if save_test:
+            data[TEST] = self.test
+        elif self._test_available:
+            data[TEST] = self.test.name
+        else:
+            data[TEST] = self.testset
[…]

### 2025-07-15 eispy2d/library/circleapproximation.py

@@ -1,0 +1,237 @@
+import time as tm
+from scipy.optimize import minimize, OptimizeResult, differential_evolution
+import analytical as ana
+import stochastic as stc
+import sys
+import inputdata as ipt
+import result as rst
+import configuration as cfg
+import pickle
+from joblib import Parallel, delayed
+import multiprocessing
+
+POSITION_RANGE = 'position_range'
+RADIUS_RANGE = 'radius_range'
+CONTRAST_RANGE = 'contrast_range'
+
+class CircleApproximation(stc.Stochastic):
+    def __init__(self, outputmode, number_executions=1, position_range=None,
+                 radius_range=None, contrast_range=None, alias='ca',
+                 parallelization=False):
+        super().__init__(outputmode, alias=alias,
+                         parallelization=parallelization,
+                         number_executions=number_executions)
+        if position_range is not None:
+            self.position_range = [position_range[0], position_range[1], 
+                                   position_range[2], position_range[3]]
+        else:
+            self.position_range = None
+        if radius_range is not None:
+            if isinstance(radius_range, (int, float)):
+                self.radius_range = [0.001, radius_range]
+            elif isinstance(radius_range, (list, tuple)):
+                self.radius_range = [radius_range[0], radius_range[1]]
+        else:
+            self.radius_range = None
+        if contrast_range is not None:
+            if isinstance(contrast_range, (int, float)):
+                self.contrast_range = [0., contrast_range]
+            elif isinstance(contrast_range, (list, tuple)):
+                self.contrast_range = [contrast_range[0], contrast_range[1]]
+        else:
+            self.contrast_range = [0., 10.]
+            
+    def solve(self, inputdata, discretization, print_info=True,
+              print_file=sys.stdout):
+        result = super().solve(inputdata, discretization, print_info, 
+                               print_file)
+
+        if self.position_range is not None:
+            position_range = self.position_range
+        else:
+            xmin, xmax = cfg.get_bounds(inputdata.configuration.Lx)
+            ymin, ymax = cfg.get_bounds(inputdata.configuration.Ly)
+            position_range = [xmin, xmax, ymin, ymax]
+        if self.radius_range is not None:
+            radius_range = self.radius_range
+        else:
+            radius_range = [0.001, min([inputdata.configuration.Lx,
+                                     inputdata.configuration.Ly])/2]
+        contrast_range = self.contrast_range
+        
+        bounds = [(position_range[0], position_range[1]),
[…]

### 2025-07-15 eispy2d/library/collocation.py

@@ -1,0 +1,133 @@
+import error
+import pickle
+import numpy as np
+import discretization as dct
+from numba import jit
+
+TRIAL_FUNCTION = 'trial'
+ELEMENTS = 'elements'
+
+class Collocation(dct.Discretization):
+    def __init__(self, configuration=None, trial=None, elements=None,
+                 name=None, alias='clc', import_filename=None,
+                 import_filepath=''):
+        if import_filename is not None:
+            self.importdata(import_filename, import_filepath)
+        else:
+            super().__init__(configuration=configuration, name=name,
+                             alias=alias)
+            self.trial = trial
+            if elements is None:
+                raise error.MissingInputError('Collocation.__init__',
+                                              'elements')
+            elif type(elements) is int:
+                self.elements = (elements, elements)
+            else:
+                self.elements = (elements[0], elements[1])
+            self.name = ('Collocation Method (%dx' % self.elements[0] + '%d), '
+                         % self.elements[1] + 'trial function: ' + self.trial)
+    def copy(self, new=None):
+        if new is None:
+            return Collocation(self.configuration, self.trial, self.elements,
+                               self.name)
+        else:
+            super().copy(new)
+            self.trial = new.trial
+            self.elements = new.elements
+    def __str__(self):
+        message = super().__str__()
+        message += 'Discretization:' + self.name + '\n'
+        message += 'Alias: ' + self.alias + '\n'
+        return message
+    def save(self, file_path=''):
+        data = super().save(file_path=file_path)
+        data[TRIAL_FUNCTION] = self.trial
+        data[ELEMENTS] = self.elements
+        with open(file_path + self.alias, 'wb') as datafile:
+            pickle.dump(data, datafile)
+    def importdata(self, file_name, file_path=''):
+        data = super().importdata(file_name, file_path=file_path)
+        self.trial = data[TRIAL_FUNCTION]
[…]

### 2025-07-15 eispy2d/library/discretization.py

@@ -1,0 +1,87 @@
+import error
+import configuration as cfg
+from abc import ABC, abstractmethod
+
+NAME = 'name'
+ALIAS = 'alias'
+CONFIGURATION = 'configuration'
+
+class Discretization(ABC):
+    def __init__(self, configuration=None, name=None, alias='',
+                 import_filename=None, import_filepath=''):
+        if import_filename is not None:
+            self.importdata(import_filename, import_filepath)
+        else:
+            if configuration is not None:
+                self.configuration = configuration.copy()
+            else:
+                self.configuration = None
+            self.name = name
+            self.alias = alias
+    @abstractmethod
+    def residual_data(self, scattered_field, contrast=None, total_field=None,
+                      current=None):
+        if contrast is not None and total_field is None:
+            raise error.MissingInputError('Discretization.residual_data',
+                                          'total_field')
+        elif contrast is None and total_field is not None:
+            raise error.MissingInputError('Discretization.residual_data',
+                                          'contrast')
+        elif contrast is None and total_field is None and current is None:
+            raise error.Error('Discretization.residual_data: either '
+                              + 'contrast-total_field or current must be given!')
+    @abstractmethod   
+    def residual_state(self, incident_field, contrast=None, total_field=None,
+                       current=None):
+        if total_field is not None and contrast is None:
+            raise error.MissingInputError('Discretization.residual_state',
+                                          'contrast')
+        elif current is not None and contrast is None:
+            raise error.MissingInputError('Discretization.residual_state',
+                                          'contrast')
+        elif contrast is None and total_field is None and current is None:
+            raise error.Error('Discretization.residual_state: either '
+                              + 'contrast-total_field or contrast-current must be'
+                              + ' given!')
+    @abstractmethod
+    def solve(self, scattered_field=None, incident_field=None, contrast=None,
+              total_field=None, current=None, linear_solver=None):
+        pass
+    @abstractmethod
+    def scattered_field(self, contrast=None, total_field=None, current=None):
+        if contrast is not None and total_field is None:
+            raise error.MissingInputError('Discretization.scattered_field',
+                                          'total_field')
+        elif total_field is not None and contrast is None:
+            raise error.MissingInputError('Discretization.scattered_field',
+                                          'contrast')
+        elif total_field is None and contrast is None and current is None:
[…]

### 2025-07-15 eispy2d/library/draw.py

@@ -1,0 +1,2015 @@
+import numpy as np
+from numpy import pi
+from numpy import logical_and
+from numpy import random as rnd
+import error
+
+
+def square(side_length, axis_length_x=2., axis_length_y=2., resolution=None,
+           background_rel_permittivity=1., background_conductivity=0.,
+           object_rel_permittivity=1., object_conductivity=0.,
+           center=[0., 0.], rotate=0., rel_permittivity=None,
+           conductivity=None):
+    """Draw a square.
+
+    Parameters
+    ----------
+        side_length : float
+            Length of the side of the square.
+
+        axis_length_x, axis_length_y : float, default: 2.0
+            Length of the size of the image.
+
+        resolution : 2-tuple
+            Image resolution, in y and x directions, i.e., (NY, NX).
+            *Either this argument or rel_permittivity or
+            conductivity must be given!*
+
+        background_rel_permittivity : float, default: 1.0
+
+        background_conductivity : float, default: 0.0
+
+        object_rel_permittivity : float, default: 1.0
+
+        object_conductivity : float, default: 0.0
+
+        center : list, default: [0.0, 0.0]
+            Center of the object in the image. The center of the image
+            corresponds to the origin of the coordinates.
+
+        rel_permittivity : :class:`numpy.ndarray`, default:None
+            A predefined image in which the object will be drawn.
+
+        conductivity : :class:`numpy.ndarray`, default:None
+            A predefined image in which the object will be drawn.
+
+        rotate : float, default: 0.0 degrees
+            Rotation of the object around its center. In degrees.
+    """
+    # Check input requirements
+    if resolution is None and (rel_permittivity is None
+                               and conductivity is None):
+        raise error.MissingInputError('draw_square', 'resolution or relative'
+                                      + '_permittivity_map or '
+                                      + 'conductivity')
+
+    # Make variable names more simple
+    L = side_length
+    Lx, Ly = axis_length_x, axis_length_y
+    epsilon_rb = background_rel_permittivity
+    sigma_b = background_conductivity
+    epsilon_ro = object_rel_permittivity
+    sigma_o = object_conductivity
+
+    # Set map variables
+    if rel_permittivity is None:
[…]

### 2025-07-15 eispy2d/library/evoalglib/objectivefunction.py

@@ -1,0 +1,307 @@
+from re import S
+import error
+import numpy as np
+import evoalglib.representation as rpt
+from abc import ABC, abstractmethod
+from numpy import pi
+from numpy import fft
+from scipy.special import jv, yv
+from scipy.special import hankel2 as h2v
+from scipy.sparse import spdiags
+from scipy.spatial.distance import pdist, squareform
+from numba import jit
+import sys
+sys.path.insert(1, '..')
+import configuration as cfg
+
+CONTRAST_FIELD = 'contrast-field'
+CONTRAST_SOURCE = 'contrast-source'
+CSEB = 'cseb'
+NIE = 'nie'
+Y0 = 'y0'
+Y0_NIE = 'yo-nie'
+
+class ObjectiveFunction(ABC):
+    def __init__(self):
+        self.name = None
+    def set_parameters(self, representation, scattered_field,
+                       incident_field):
+        self.representation = representation
+        self.scattered_field = scattered_field
+        self.incident_field = incident_field
+    @abstractmethod
+    def eval(self, x):
+        pass
+    @abstractmethod
+    def __str__(self):
+        return "Objective Function: "
+
+
+class Rastrigin(ObjectiveFunction):
+    def __init__(self, amplitude=10):
+        super().__init__()
+        self.name = 'rastringin'
+        self.A = amplitude
+        self.xopt = 0.
+    def eval(self, x):
+        if not isinstance(self.representation, rpt.CanonicalProblems):
+            raise error.WrongTypeInput('Rastrigin.eval', 'representation',
+                                       'CanonicalProblems',
+                                       str(type(self.representation)))
+        super().eval(x)
+        n = x.size
+        x = self.representation.contrast(x)
+        return self.A*n + np.sum(x**2-self.A*np.cos(2*pi*x))
+    def __str__(self):
+        message = super().__str__()
+        message += 'Rastringin (Canonical, Nonlinear, Multimodal)\n'
+        message += 'Amplitude: %.1f\n' % self.A
+        message += 'Optimum solution: %.2f' % self.xopt
+        return message
+
+
+class Ackley(ObjectiveFunction):
+    def __init__(self):
+        super().__init__()
+        self.name = 'ackley'
+        self.xopt = 0.
+    def eval(self, x):
+        if not isinstance(self.representation, rpt.CanonicalProblems):
[…]

### 2025-07-15 eispy2d/library/inverse.py

@@ -1,0 +1,137 @@
+"""Abstract Inverse Scattering Solver model.
+
+This module provides the abstract class for implementation of any method
+which solve the nonlinear inverse scattering problem. Therefore, this
+class aims to compute the dielectric map and the total intern field.
+"""
+
+# Standard libraries
+from abc import ABC, abstractmethod
+import sys
+
+# Developed libraries
+import configuration as cfg
+import result as rst
+
+NAME = 'name'
+ALIAS = 'alias'
+PARALLELIZATION = 'parallelization'
+
+
+class InverseSolver(ABC):
+    """Abstract inverse solver class.
+
+    This class defines the basic defintion of any implementation of
+    inverse solver.
+
+    Attributes
+    ----------
+        name : str
+            The name of the solver.
+
+        version : str
+            The version of method.
+
+        config : :class:`configuration.Configuration`
+            An object of problem configuration.
+
+        execution_time : float
+            The amount of time for a single execution of the method.
+
+    Notes
+    -----
+        The name of the method should be defined by default.
+    """
+
+    def __init__(self, alias='', parallelization=False, import_filename=None,
+                 import_filepath=''):
+        """Create the object.
+
+        Parameters
+        ----------
+            configuration : :class:`configuration.Configuration`
+                An object of problem configuration.
+        """
+        if import_filename is not None:
+            self.importdata(import_filename, import_filepath)
+        else:
+            self.name = ''
+            self.alias = alias
+            self.parallelization = parallelization
+
+
+    @abstractmethod
+    def solve(self, inputdata, discretization, print_info=True,
+              print_file=sys.stdout):
+        """Solve the inverse scattering problem.
+
+        This is the model routine for any method implementation. The
+        input may include other arguments. But the output must always be
+        an object of :class:`results.Results`.
+
+        Parameters
+        ----------
+            inputdata : :class:`inputdata.InputData`
+                An object of the class which defines an instance.
+
+            print_info : bool
+                A flag to indicate if information should be displayed or
+                not on the screen.
+
+        Returns
+        -------
+            :class:`results.Results`
+        """
+        if print_info:
+            self._print_title(inputdata, discretization, print_file=print_file)
+
+        return rst.Result(inputdata.name + '_' + self.alias,
+                          method_name=self.alias,
+                          configuration=inputdata.configuration)
+
+    def _print_title(self, inputdata, discretization, print_file=sys.stdout):
[…]

### 2025-07-15 eispy2d/library/regularization.py

@@ -1,0 +1,469 @@
+import numpy as np
+from numba import jit, prange
+from numpy import linalg as lag
+from abc import ABC, abstractmethod
+
+import error
+
+TIK_FIXED = 'fixed'
+TIK_MOZOROV = 'mozorov'
+TIK_LCURVE = 'lcurve'
+
+
+class Regularization(ABC):
+    def __init__(self):
+        pass
+    @abstractmethod
+    def solve(self, K, y):
+        pass
+    @abstractmethod
+    def __str__(self):
+        return 'Regularization Method: '
+
+
+class Tikhonov(Regularization):
+    def __init__(self, choice, parameter=None):
+        super().__init__()
+        if type(choice) is int or type(choice) is float:
+            self.alpha = choice
+            self.choice = TIK_FIXED
+        elif choice == TIK_FIXED:
+            if parameter is None:
+                raise error.MissingInputError('Tikhonov.__init__', 'parameter')
+            elif type(parameter) is float or type(parameter) is int:
+                self.alpha = parameter
+                self.choice = choice
+            else:
+                raise error.WrongTypeInput('Tikhonov.__init__', 'parameter',
+                                           'float', str(type(parameter)))
+        elif choice == TIK_MOZOROV:
+            self.choice = choice
+            self.alpha = None
+        elif choice == TIK_LCURVE:
+            self.choice = choice
+            self.alpha = None
+    def solve(self, K, y):
+        if self.choice == TIK_FIXED:
+            if y.ndim == 1:
+                return tikhonov(K, y, self.alpha)
+            elif y.ndim == 2:
+                x = np.zeros((K.shape[1], y.shape[1]), dtype=K.dtype)
+                for n in range(y.shape[1]):
+                    x[:, n] = tikhonov(K, y[:, n].flatten(), self.alpha)
+                return x
+        elif self.choice == TIK_MOZOROV:
+            if y.ndim == 1:
+                alpha = mozorov_choice(K, y)
+                return tikhonov(K, y, alpha)
+            elif y.ndim == 2:
+                x = np.zeros((K.shape[1], y.shape[1]), dtype=K.dtype)
+                for n in range(y.shape[1]):
+                    alpha = mozorov_choice(K, y[:, n].flatten())
[…]

### 2025-07-15 eispy2d/library/result.py

@@ -1,0 +1,1958 @@
+"""A module for results information.
+
+The results module provides the :class:`Results` which contains the
+resultant information of a single execution of a method for a given
+input data and the corresponding problem configuration. The class is also
+a tool for plotting results. The following class is defined
+
+:class:`Results`
+    a class for storing results information of a single execution.
+
+The list of routines...
+"""
+
+from math import pi
+import pickle
+import copy as cp
+import numpy as np
+from scipy.stats import linregress
+from skimage import measure
+from statsmodels.graphics.boxplots import violinplot
+import matplotlib.pyplot as plt
+import error
+import configuration as cfg
+
+
+# Strings for easier implementation of plots
+XLABEL_STANDARD = r'x [$\lambda_b$]'
+YLABEL_STANDARD = r'y [$\lambda_b$]'
+XLABEL_UNDEFINED = r'x [$L_x$]'
+YLABEL_UNDEFINED = r'y [$L_y$]'
+COLORBAR_REL_PERMITTIVITY = r'$\epsilon_r$'
+COLORBAR_CONDUCTIVITY = r'$\sigma$ [S/m]'
+TITLE_REL_PERMITTIVITY = 'Relative Permittivity'
+TITLE_CONDUCTIVITY = 'Conductivity'
+TITLE_RECOVERED_REL_PERMITTIVITY = ('Recovered '
+                                         + TITLE_REL_PERMITTIVITY)
+TITLE_RECOVERED_CONDUCTIVITY = 'Recovered ' + TITLE_CONDUCTIVITY
+TITLE_ORIGINAL_REL_PERMITTIVITY = ('Original '
+                                        + TITLE_REL_PERMITTIVITY)
+TITLE_ORIGINAL_CONDUCTIVITY = 'Original ' + TITLE_CONDUCTIVITY
+LABEL_ZETA_RN = r'$\zeta_{RN} [V/m]$'
+LABEL_ZETA_RPAD = r'$\zeta_{RPAD}$ [%/sample]'
+LABEL_ZETA_EPAD = r'$\zeta_{\epsilon PAD}$ [%/pixel]'
+LABEL_ZETA_EBE = r'$\zeta_{\epsilon BE}$ [%/pixel]'
[…]

### 2025-07-15 eispy2d/library/richmond.py

@@ -1,0 +1,340 @@
+import pickle
+import numpy as np
+from scipy.spatial.distance import pdist, cdist, squareform
+from numpy import pi
+from scipy.special import jv
+from scipy.special import hankel2 as h2v
+from scipy.sparse import spdiags, eye
+from scipy.interpolate import NearestNDInterpolator
+
+
+import configuration as cfg
+import regularization as reg
+import discretization as dct
+import collocation as clc
+import error
+
+
+GREENF_DATA = 'GS'
+GREENF_STATE = 'GD'
+
+class Richmond(clc.Collocation):
+    def __init__(self, configuration=None, elements=None, state=True, alias='ric',
+                 import_filename=None, import_filepath=''):
+        if import_filename is not None:
+            self.importdata(import_filename, import_filepath)
+        else:
+            if configuration is None:
+                raise error.MissingInputError('Richmond.__init__',
+                                              'configuration')
+            super().__init__(configuration, 'pulse', elements, name=None,
+                             alias=alias)
+            self.GS = richmond_data(configuration, self.elements)
+            if state:
+                self.GD = richmond_state(configuration, self.elements)
+            else:
+                self.GD = None
+            self.name = ('Richmond Method (%dx' % self.elements[0] + '%d)'
+                         % self.elements[1])
+    def residual_data(self, scattered_field, contrast=None, total_field=None,
+                      current=None):
+        Es, X, E, J = scattered_field, contrast, total_field, current
+        super().residual_data(Es, contrast=X, total_field=E, current=J)
+        if current is None:
+            if X.ndim == 1:
+                CHI = spdiags(X, 0, X.size, X.size)
+                res = Es - self.GS@CHI@E
+            elif X.ndim == 2 and np.prod(X.shape) == self.GS.shape[1]:
+                CHI = spdiags(X.flatten(), 0, X.size, X.size)
+                res = Es - self.GS@CHI@E
+            elif X.ndim == 2 and np.prod(X.shape) == self.GS.shape[1]**2:
+                res = Es - self.GS@X@E
+        else:
+            res = Es - self.GS@J
+        return res
+    def residual_state(self, incident_field, contrast=None, total_field=None,
+                       current=None):
+        Ei, X, E, J = incident_field, contrast, total_field, current
+        super().residual_state(Ei, contrast=X, total_field=E, current=J)
+        if self.GD is None:
+            raise error.MissingAttributesError('Richmond', 'GD')
+        if current is None:
+            if X.ndim == 1:
[…]

### 2025-07-15 eispy2d/library/stochastic.py

@@ -1,0 +1,197 @@
+import sys
+import numpy as np
+import copy as cp
+from abc import abstractmethod
+
+import error
+import inverse as inv
+import result as rst
+
+
+NEXECUTIONS = 'nexec'
+OUTPUTMODE = 'outputmode'
+
+
+class Stochastic(inv.InverseSolver):
+
+    @property
+    def nexec(self):
+        return self._nexec
+    @nexec.setter
+    def nexec(self, new):
+        if new is None:
+            self._nexec = 1
+            self._single_execution = True
+        elif type(new) is int:
+            if new < 1:
+                raise error.WrongValueInput('Stochastic.nexec', 'new value',
+                                            'None or int > 0', str(new))
+            elif new == 1:
+                self._nexec = 1
+                self._single_execution = True
+            else:
+                self._nexec = new
+                self._single_execution = False
+        else:
+            raise error.WrongTypeInput('Stochastic.nexec', 'new value',
+                                       'None or int > 0', str(new))
+            
+    def __init__(self, outputmode, alias=None, parallelization=False,
+                 number_executions=1):
+        super().__init__(alias=alias, parallelization=parallelization)
+        self.nexec = number_executions
+        self.outputmode = outputmode
+
+    def solve(self, inputdata, discretization, print_info=True,
+              print_file=sys.stdout):
+        return super().solve(inputdata, discretization, print_info=print_info,
+                             print_file=print_file)
+    
+    @abstractmethod
+    def save(self, file_path=''):
+        data = super().save(file_path)
+        data[NEXECUTIONS] = self.nexec
+        data[OUTPUTMODE] = self.outputmode
+        return data
+
+    def importdata(self, file_name, file_path=''):
+        data = super().importdata(file_name, file_path)
+        self.nexec = data[NEXECUTIONS]
+        self.outputmode = data[OUTPUTMODE]
+    
+    def _print_title(self, inputdata, discretization, print_file=sys.stdout):
+        super()._print_title(inputdata, discretization, print_file=print_file)
+        print('Number of executions: %d' % self.nexec, file=print_file)
+        print('Output rule: ' + str(self.outputmode))
+
+    def copy(self, new=None):
+        if new is None:
+            return Stochastic(self.outputmode, alias=self.alias,
+                              parallelization=self.parallelization,
+                              number_executions=self.nexec)
+        else:
+            super().copy(new)
+            self.nexec = new.nexec
+            self.outputmode = new.outputmode.copy()
+
+    def __str__(self):
+        message = super().__str__()
[…]

### 2025-07-15 experiments/average/gendata.py

@@ -1,0 +1,45 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import configuration as cfg
+import testset as tst
+from experiment import RANDOM_POLYGONS_PATTERN
+import result as rst
+import mom_cg_fft as mom
+
+name = 'average'
+NM = NS = 20
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+
+config = cfg.Configuration(name=name + '.cfg', number_measurements=NM,
+                           number_sources=NS, observation_radius=Ro,
+                           wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+contrast = .25
+object_size = .9
+resolution = (80, 80)
+map_pattern = RANDOM_POLYGONS_PATTERN
+sample_size = 30
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
+
+testset = tst.TestSet(name=name + '.tst', configuration=config,
+                      contrast=contrast, object_size=object_size, 
+                      resolution=resolution, map_pattern=map_pattern,
+                      sample_size=sample_size, noise=noise,
+                      indicators=indicators)
+
+testset.randomize_tests(compute_dnl=True)
+
+testset.generate_field_data(solver=mom.MoM_CG_FFT(tolerance=1e-3,
+                                                  maximum_iterations=5000))
+
+testset.save(file_path='./data/')

### 2025-07-15 experiments/average/launch.py

@@ -1,0 +1,2 @@
+import gendata
+import runexperiment

### 2025-07-15 experiments/average/runexperiment.py

@@ -1,0 +1,42 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import testset as tst
+import richmond as ric
+import regularization as reg
+import mom_cg_fft as mom
+import stopcriteria as stp
+import lsm
+import osm
+import bim
+import csi
+import som
+import benchamrk as bmk
+
+name = 'average'
+resolution = (40, 40)
+
+testset = tst.TestSet(import_filename=name + '.tst',
+                      import_filepath='./data/')
+
+method = [
+    lsm.LinearSamplingMethod(alias='lsm',
+                             regularization=reg.ConjugatedGradient(300),
+                             sv_cutoff=None, threshold=.7),
+    osm.OrthogonalitySamplingMethod(threshold=.35),
+    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.ConjugatedGradient(300), 
+                            stp.StopCriteria(max_iterations=30)),
+    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=300)),
+    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
+                                        cutoff_index=5)
+]
+
+discretization = ric.Richmond(configuration=testset.test[0].configuration,
+                              elements=resolution)
+
+benchmark = bmk.Benchmark(name=name + '.bmk', method=method, 
+                          discretization=discretization, testset=testset)
+
+benchmark.run(parallelization=bmk.PARALLELIZE_EXECUTIONS, pre_save=True)
+
+benchmark.save(file_path='./data/', save_test=True)

### 2025-07-15 experiments/position/single/gendata.py

@@ -1,0 +1,53 @@
+import sys
+sys.path.insert(1, '../../../../eispy2d/library/')
+
+import configuration as cfg
+import inputdata as ipt
+import result as rst
+import draw
+import mom_cg_fft as mom
+
+# Parameters
+name = 'single'
+NM = NS = 80
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+resolution = (120, 120)
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR, rst.OBJECTIVE_FUNCTION]
+epsilon_rd = 5. # 6.00
+l = 0.5
+position = [.4, -.4]
+rotate = 30
+
+config = cfg.Configuration(name=name + '.cfg', number_measurements=NM, 
+                           number_sources=NS, observation_radius=Ro, 
+                           wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+
+test = ipt.InputData(name=name + '.ipt', configuration=config, 
+                     resolution=resolution, noise=noise, indicators=indicators)
+
+chi = (epsilon_rd-epsilon_rb)/epsilon_rb
+
+test.rel_permittivity, _ = draw.star5(
+    l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
+    background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd,
+    center=position, rotate=30.
+)
+
+forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=10000,
+                         parallelization=True)
+
+_ = forward.solve(test)
+
+test.compute_dnl()
+
+test.save(file_path='./data/')

### 2025-07-15 experiments/position/single/runexperiment.py

@@ -1,0 +1,34 @@
+import sys
+sys.path.insert(1, '../../../../eispy2d/library/')
+
+import inputdata as ipt
+import casestudy as cst
+import richmond as ric
+import circleapproximation as ca
+import stochastic as stc
+
+name = 'single'
+resolution = (40, 40)
+
+test = ipt.InputData(import_filename=name + '.ipt',
+                     import_filepath='./data/')
+
+contrast_range = 10.
+number_executions = 30
+
+method = ca.CircleApproximation(stc.OutputMode(stc.EACH_EXECUTION),
+                                contrast_range=contrast_range)
+
+discretization = ric.Richmond(configuration=test.configuration,
+                              elements=resolution)
+
+casestudy = cst.CaseStudy(name=name + '.cst',
+                          stochastic_runs=number_executions,
+                          save_stochastic_runs=True,
+                           method=method,
+                           discretization=discretization,
+                           test=test)
+
+casestudy.run(parallelization=False, pre_save=True)
+
+casestudy.save(file_path='./data/', save_test=True)

### 2025-07-15 experiments/star/runexperiment.py

@@ -1,0 +1,43 @@
+import sys
+sys.path.insert(1, '../../eispy2d/library/')
+
+import inputdata as ipt
+import casestudy as cst
+import richmond as ric
+import regularization as reg
+import mom_cg_fft as mom
+import stopcriteria as stp
+import lsm
+import osm
+import bim
+import csi
+import som
+
+name = 'star'
+resolution = (40, 40)
+
+test = ipt.InputData(import_filename=name + '.ipt')
+
+method = [
+    lsm.LinearSamplingMethod(alias='lsm',
+                             regularization=reg.ConjugatedGradient(300),
+                             sv_cutoff=None, threshold=.7),
+    osm.OrthogonalitySamplingMethod(threshold=.35),
+    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.ConjugatedGradient(300), 
+                            stp.StopCriteria(max_iterations=30)),
+    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=300)),
+    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
+                                        cutoff_index=5)
+]
+
+discretization = ric.Richmond(configuration=test.configuration,
+                              elements=resolution)
+
+casestudy = cst.CaseStudy(name=name + '.cst',
+                           method=method,
+                           discretization=discretization,
+                           test=test)
+
+casestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True)
+
+casestudy.save(save_test=True)

### 2025-07-15 experiments/vary/gendata.py

@@ -1,0 +1,57 @@
+import sys
+sys.path.insert(1, '../../eispy2d/library/')
+import configuration as cfg
+import inputdata as ipt
+import result as rst
+import draw
+import mom_cg_fft as mom
+
+name = 'vary.cfg'
+NM = NS = 60
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+
+config = cfg.Configuration(name=name, number_measurements=NM, number_sources=NS,
+                           observation_radius=Ro, wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+epsilon_rd = [1.25, 1.5, 1.75, 2., 2.5]
+name = 'vary'
+resolution = (160, 160)
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
+
+forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=5000,
+                         parallelization=True)
+
+for n in range(len(epsilon_rd)):
+
+    print('Test %d... ' % n, end='')
+    test = ipt.InputData(name=name + '%d' % n + '.ipt', configuration=config,
+                         resolution=resolution, noise=noise,
+                         indicators=indicators)
+
+    chi = (epsilon_rd[n]-epsilon_rb)/epsilon_rb
+    l = 0.9
+    position = [.0, .0]
+
+    test.rel_permittivity, _ = draw.star5(
+        l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
+        background_rel_permittivity=epsilon_rb, 
+        object_rel_permittivity=epsilon_rd[n], center=position, rotate=0.
+    )
+    
+    print('solving forward problem... ', end='')
+    _ = forward.solve(test)
+    
+    print('computing DNL... ', end='')
+    test.compute_dnl()
+    
+    print('ok!')
+    test.save()

### 2025-07-15 experiments/vary/runexperiment.py

@@ -1,0 +1,28 @@
+import sys
+sys.path.insert(1, '../../eispy2d/library/')
+
+import casestudy as cst
+import richmond as ric
+import inputdata as ipt
+import osm
+
+name = 'vary'
+resolution = (40, 40)
+
+tests = []
+for n in range(5):
+    tests.append(ipt.InputData(import_filename=name + '%d' % n + '.ipt'))
+
+method = osm.OrthogonalitySamplingMethod(threshold=.35)
+
+discretization = ric.Richmond(configuration=tests[0].configuration,
+                              elements=resolution)
+
+for n in range(len(tests)):
+
+    caseestudy = cst.CaseStudy(name=name + '%d' % n + '.cst', method=method,
+                               discretization=discretization, test=tests[n])
+
+    caseestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True)
+
+    caseestudy.save(save_test=True)

### 2025-07-15 main.tex
Fechando resultados do primeiro experimento

@@
 
-                The images reconstructed by each algorithm are shown in Fig. \ref{fig:shape:single:recons}.
+                The images reconstructed by each algorithm are shown in Fig.
+\ref{fig:shape:single:recons}.
+For the qualitative methods, OSM exhibited contrast variation within the object, which is consistent with the inherent characteristics of the method.
+Additionally, OSM recovered a larger area with more defined vertices compared to LSM.
+Regarding the quantitative methods, CSI demonstrated the lower performance in recovering the object's contrast value close to the ground truth.
+Moreover, the quantitative methods produced less smooth geometries than their qualitative counterparts.
 
@@
 
-                % The first case study involves a single scatterer with homogeneous contrast.
-Fig.
-\ref{fig:star} illustrates the geometry of the problem.
-The scatterer is a five-point star with a radius of 0.1 m and a contrast of 0.5.
-The original image was discretized into a 100x100 pixel grid.
-Fig.
-\ref{fig:star} also shows the image reconstructed by an imaging algorithm.
-Table \ref{tab:star} presents the results obtained for shape and position errors.
-The results demonstrate that the algorithm successfully recovered the scatterer's shape with a shape error of 0.5\% and a position error of 0.1\%.
-These findings indicate that the algorithm accurately recovered the scatterer's shape and position.
+                Table \ref{tab:star} summarizes the results of the shape error and position error indicators for each algorithm.
+The results indicate that BIM and SOM achieved the best performance in terms of shape error, while CSI, LSM and OSM performed similarly.
+This is consistent with the observations from Fig.
+\ref{fig:shape:single:recons}, since the quantitative methods had a greater ability to capture the object's contours compared to the qualitative methods.
+This was not true for CSI, which, due to its greater difficulty in quantifying the object's contrast, had more difficulty in capturing the object's contours.
 
-                % \begin{figure}[!t]
-                %     \centering
-                %     \includegraphics[width=.8\columnwidth]{./figs/star}
-                %     \caption{Single scatterer geometry.}
-                %     \label{fig:star}
-                % \end{figure}
+                In terms of position error, the qualitative methods achieved the best performance, while BIM and CSI showed higher errors.
+This suggests that methods producing smoother object contours may be more effective at capturing the central point of objects.
+Conversely, methods that better capture object boundaries may struggle with the position indicator due to contour irregularities, which can impact centroid calculations, particularly for symmetric figures.
 
-                % \begin{table}[!t]
-                %     \centering
-                %     \caption{Results for the single scatterer case study.}
-                %     \label{tab:star}
-                %     \begin{tabular}{|c|c|c|}
-                %         \hline
-                %         Indicator & Value & Unit \\
-                %         \hline
-                %         $\zeta_S$ & 0.5 & \% \\
-                %         $\zeta_P$ & 0.1 & \% \\
-                %         \hline
-                %     \end{tabular}   
-                % \end{table}
+                \begin{table}[!t]
+                    \centering
+                    \renewcommand{\arraystretch}{1.5}
+                    \caption{Results for the single scatterer case study.}
+                    \label{tab:star}
+                    \begin{tabular}{ccc}
+                        Method & Shape error ($\zeta_S$) & Position error ($\zeta_P$) \\
+                        \hline
+                        LSM & 29.2 \% & 0.049 \% \\
+                        OSM & 24.5 \% & 0.057 \% \\
+                        BIM & 14.9 \% & 0.25 \% \\
+                        CSI & 26.3 \% & 0.31 \% \\
+                        SOM & 15.4 \% & 0.14 \% \\
+                    \end{tabular}   
+                \end{table}
 

### 2025-07-15 main.tex
Mais resultados

@@
 
-                Table \ref{tab:star} summarizes the results of the shape error and position error indicators for each algorithm.
-The results indicate that BIM and SOM achieved the best performance in terms of shape error, while CSI, LSM and OSM performed similarly.
+                Table \ref{tab:star} summarizes the results of the shape error indicator for each algorithm.
+The results indicate that BIM and SOM achieved the best performance, while CSI, LSM and OSM performed similarly.
 This is consistent with the observations from Fig.
@@
 This was not true for CSI, which, due to its greater difficulty in quantifying the object's contrast, had more difficulty in capturing the object's contours.
-
-                In terms of position error, the qualitative methods achieved the best performance, while BIM and CSI showed higher errors.
-This suggests that methods producing smoother object contours may be more effective at capturing the central point of objects.
-Conversely, methods that better capture object boundaries may struggle with the position indicator due to contour irregularities, which can impact centroid calculations, particularly for symmetric figures.
 
@@
                     \label{tab:star}
-                    \begin{tabular}{ccc}
-                        Method & Shape error ($\zeta_S$) & Position error ($\zeta_P$) \\
-                        \hline
-                        LSM & 29.2 \% & 0.049 \% \\
-                        OSM & 24.5 \% & 0.057 \% \\
-                        BIM & 14.9 \% & 0.25 \% \\
-                        CSI & 26.3 \% & 0.31 \% \\
-                        SOM & 15.4 \% & 0.14 \% \\
+                    \begin{tabular}{cccccc}
+                        Method & LSM & OSM & BIM & CSI & SOM \\\hline
+                        $\zeta_S$ (\%) & 29.2 & 24.5 & 14.9 & 26.3 & 15.4 \\
                     \end{tabular}   
@@
 			\subsubsection{Varying contrast}\label{sec:results:shape:varying}
+
+                \begin{figure*}
+                    \centering
+                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_0.eps}}
+                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_1.eps}}
+                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_2.eps}}
+                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_3.eps}}
+                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_4.eps}} \\
+                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_0.eps}}
+                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_1.eps}}
+                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_2.eps}}
+                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_3.eps}}
+                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_4.eps}}
+                    \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
+                    \label{fig:shape:vary:recons}
+                \end{figure*}
+
+                \begin{figure}
+                    \centering
+                    \subfigure[]{\includegraphics[width=0.49\columnwidth]{./experiments/vary/figs/zeta_s.eps}}
+                    \subfigure[]{\includegraphics[width=0.49\columnwidth]{./experiments/vary/figs/dnl.eps}}
+                    \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
+                    \label{fig:shape:vary:indicators}
+                \end{figure}
 

### 2025-07-15 eispy2d/library/statistics.py

@@ -1,1353 +1,0 @@
-import warnings
-import numpy as np
-from numpy import std
-from matplotlib import pyplot as plt
-from scipy.stats import shapiro, boxcox, fligner, friedmanchisquare, ttest_ind
-from scipy.stats import mannwhitneyu, wilcoxon, ttest_1samp, kruskal
-from scipy.stats import f as Fdist
-from scipy.stats import t as Tdist
-from scipy.optimize import curve_fit
-from statsmodels import stats
-from statsmodels.stats.weightstats import DescrStatsW
-from statsmodels.stats.oneway import anova_oneway as anova
-from statsmodels.stats.power import tt_solve_power as power_tt
-from statsmodels.stats.power import tt_ind_solve_power as power_ttind
-from statsmodels.stats.power import TTestPower
-from statsmodels.sandbox.stats.multicomp import MultiComparison
-from statsmodels.api import graphics
-import pingouin as pg
-
-import error
-import result as rst
-
-
-def rcbd(data, alpha=0.05):
-    r"""Randomized Complete Block Design"""
-    if type(data) is list:
-        y = np.array(data)
-    else:
-        y = np.copy(data)
-    a, b = y.shape
-    N = a*b
-    yid = np.sum(y, axis=1)
-    ydj = np.sum(y, axis=0)
-    ydd = np.sum(y)
-
-    SST = np.sum(y**2) - ydd**2/N
-    SSTreat = 1/b*np.sum(yid**2)-ydd**2/N
-    SSBlocks = 1/a*np.sum(ydj**2)-ydd**2/N
-    SSE = SST-SSTreat-SSBlocks
-
-    DOFnum = a-1
-    DOFden = (a-1)*(b-1)
-
-    MSTreat = SSTreat/(a-1)
-    MSE = SSE/((a-1)*(b-1))
-
-    F0 = MSTreat/MSE
-
-    alpha = 0.05
-
-    Fcrit = Fdist.ppf(1-alpha, DOFnum, DOFden)
-
-    pvalue = Fdist.sf(F0, DOFnum, DOFden)
-
-    return F0, pvalue, F0 < Fcrit
-
-
-def residuals(data, blocked=False):
-    if type(data) is np.ndarray:
-        y = data.tolist()
-    else:
-        y = data
-
-    a = len(data)
-    b = np.zeros(a, dtype=int)
-    for i in range(a):
-        b[i] = len(y[i])
-    N = np.sum(b)
-
-    if blocked is False:
-        means = np.zeros(a)
[…]

### 2025-07-15 experiments/vary/gendata.py

@@ -27,7 +27,7 @@ resolution = (160, 160)
 noise = 5.
 indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
 
-forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=5000,
+forward = mom.MoM_CG_FFT(tolerance=1e-5, maximum_iterations=5000,
                          parallelization=True)
 
 for n in range(len(epsilon_rd)):

### 2025-07-15 experiments/vary/genfigures.py

@@ -1,0 +1,236 @@
+import sys
+sys.path.insert(1, '../../eispy2d/library/')
+import casestudy as cst
+import numpy as np
+from matplotlib import pyplot as plt
+import result as rst
+import configuration as cfg
+
+N = 5
+casestudies = [cst.CaseStudy(import_filename='vary%d.cst' % n,
+                             import_filepath='./data/') for n in range(N)]
+chi = np.array([.25, .5, .75, 1., 1.5])
+
+plt.rcParams['font.family'] = 'serif'
+plt.rcParams['font.serif'] = 'Times New Roman'
+plt.rcParams['font.size'] = 40
+
+filepath = './figs/'
+config = casestudies[0].test.configuration
+xlabel, ylabel = r'x [$\lambda_b$]', r'y [$\lambda_b$]'
+clb_contrast = r'$|\chi|$'
+xmin, xmax = cfg.get_bounds(config.Lx)
+ymin, ymax = cfg.get_bounds(config.Ly)
+extent = [xmin/config.lambda_b,
+          xmax/config.lambda_b,
+          ymin/config.lambda_b,
+          ymax/config.lambda_b]
+
+result = casestudies[0].results[0]
+X = cfg.get_contrast_map(epsilon_r=result.rel_permittivity,
+                         sigma=result.conductivity,
+                         configuration=config)
+X = np.abs(X)
+plt.figure(figsize=(10, 10))
+plt.imshow(X, origin='lower', extent=extent, cmap='Greys',
+           aspect='equal', vmin=0, vmax=1)
+# plt.colorbar(label=clb_contrast)
+plt.xticks([-1, 0, 1])
+plt.yticks([-1, 0, 1])
+plt.xlabel(xlabel)
+plt.ylabel(ylabel)
+# plt.subplots_adjust(left=0.15, right=0.85, top=0.9, bottom=0.1)
+# plt.show()
+plt.tight_layout(h_pad=0.6, w_pad=0.6)
+plt.savefig(filepath + 'osm_0.eps', format='eps', bbox_inches='tight')
+plt.close()
+
+result = casestudies[1].results[0]
+X = cfg.get_contrast_map(epsilon_r=result.rel_permittivity,
+                         sigma=result.conductivity,
+                         configuration=result.configuration)
+X = np.abs(X)
+plt.figure(figsize=(10, 10))
[…]

### 2025-07-15 experiments/vary/runexperiment.py

@@ -5,6 +5,8 @@ import casestudy as cst
 import richmond as ric
 import inputdata as ipt
 import osm
+import som
+import stopcriteria as stp
 
 name = 'vary'
 resolution = (40, 40)
@@ -13,14 +15,18 @@ tests = []
 for n in range(5):
     tests.append(ipt.InputData(import_filename=name + '%d' % n + '.ipt'))
 
-method = osm.OrthogonalitySamplingMethod(threshold=.35)
+methods = [
+    osm.OrthogonalitySamplingMethod(threshold=.35),
+    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
+                                        cutoff_index=5)
+] 
 
 discretization = ric.Richmond(configuration=tests[0].configuration,
                               elements=resolution)
 
 for n in range(len(tests)):
 
-    caseestudy = cst.CaseStudy(name=name + '%d' % n + '.cst', method=method,
+    caseestudy = cst.CaseStudy(name=name + '%d' % n + '.cst', method=methods,
                                discretization=discretization, test=tests[n])
 
     caseestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True)

### 2025-07-16 main.tex
Escrita sobre experimentos de variação de contraste

@@
 Additionally, OSM recovered a larger area with more defined vertices compared to LSM.
-Regarding the quantitative methods, CSI demonstrated the lower performance in recovering the object's contrast value close to the ground truth.
-Moreover, the quantitative methods produced less smooth geometries than their qualitative counterparts.
+Regarding the quantitative methods, CSI demonstrated the lowest performance in recovering the object's contrast value close to the ground truth.
+Moreover, the quantitative methods produced more accurate contours than their qualitative counterparts.
 
-                \begin{figure*}
+                \begin{figure*}[!htb]
                     \subfigure[Ground-Truth]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/0}}
@@
 
-                \begin{table}[!t]
+                \begin{table}[!htb]
                     \centering
@@
 
-                \begin{figure*}
+               % Um outro tipo de estudo possível que pode complementar a análise do desempenho dos algoritmos na reconstrução da geometria dos objetos é a observação do desempenho do indicador com a variação do contraste de um objeto.
+Ou seja, dado um espalhador, a medida que o seu valor de contraste aumenta, o DNL aumenta e, consequentemente, os algoritmos podem peder desempenho uma vez que o problema fica mais díficil.
+Para demonstrar isso, o mesmo espalhador com as mesmas configurações de cenário do estudo anterior foi considerado.
+A única excepção na configuração foi que a resolução da imagem original foi aumentada para 160$\times$160 pixels por questões de precisão no cálculo do campo.
+O espalhador foi reconstruído com base em cinco valores de contraste: 0.25, 0.5, 0.75, 1 e 1.5.
+A Fig.
+\ref{fig:shape:vary:dnl} mostra o DNL para cada valor de contraste.
+Para este estudo foram considerados os métodos OSM e SOM com as mesmas configurações do estudo anterior.
+Obviamente, os parâmetros dos métodos poderiam ser ajustados para cada valor de contraste.
+No entanto, como o experimento tem apenas o fim de demonstrar a aplicabilidade do indicador, os parâmetros foram mantidos constantes para todos os valores de contraste.
+
+                Another type of study that can complement the analysis of algorithm performance in object geometry reconstruction is the observation of indicator performance with varying object contrast.
+Specifically, for a given scatterer, as its contrast value increases, the DNL increases, and consequently, algorithms may lose performance since the problem becomes more challenging.
+To demonstrate this relationship, the same scatterer from the previous study was considered with identical scenario configurations.
+The only modification was that the original image resolution was increased to 160$\times$160 pixels to ensure precision in field calculations for high contrast scenarios.
+
+                The scatterer was reconstructed using five contrast values: 0.25, 0.5, 0.75, 1.0, and 1.5.
+Fig.
+\ref{fig:shape:vary:dnl} shows the corresponding DNL for each contrast value.
+For this study, the OSM and SOM methods were employed with the same configurations as the previous study.
+While the method parameters could be optimized for each contrast value, they were kept constant across all contrast values to demonstrate the indicator's applicability in a controlled manner.
+
+                {\color{red} EU PRECISO RODAR NOVAMENTE O EXPERIMENTO PORQUE O NÚMERO DE MEDIÇÕES E FONTES NÃO FORAM IGUAIS NA PRIMEIRA VEZ.}
+
+                \begin{figure*}[!htb]
                     \centering
@@
 
-                \begin{figure}
+                % A Fig.
+\ref{fig:shape:vary:recons} mostra as imagens reconstruídas por OSM e SOM para cada valor de contraste.
+Conforme esperado, a medida que o contraste aumentou, a precisão na recuperação da geometria diminuiu, ao ponto de que, para o maior valor de contraste, 1.5, a geometria não foi mais recuperada corretamente, principalmente no caso do SOM.
+É possível observar que o SOM conseguiu estimar o contraste do espalhador com algum grau de precisão até o caso onde $\chi = 1$, no qual o DNL é 2, aproximadamente.
+
+                Fig.
+\ref{fig:shape:vary:recons} shows the images reconstructed by OSM and SOM for each contrast value.
+As expected, reconstruction precision decreased with increasing contrast, reaching a point where the geometry was no longer correctly recovered for the highest contrast value (1.5), particularly in the case of SOM.
+Notably, SOM was able to estimate the scatterer's contrast with reasonable precision up to $\chi = 1$, where the DNL is approximately 2.
+
+                % Fig.
+\ref{fig:shape:vary:indicators:zeta_s} shows the shape error indicator $\zeta_S$ for OSM and SOM.
+The results indicate that the shape error increases with the contrast value, which is consistent with the expected behavior of the algorithms.
+Além disso, no caso $\chi = 1.5$, o indicador $\zeta_S$ assume valores maiores que 100\%, indicando que o número de pixeis classificados incorretamente é maior que o número de pixeis que compõem o espalhador na imagem original.
+Isso é consistente com a observação de que, para este valor de contraste, a geometria não foi mais recuperada corretamente.
+Observa-se também que a diferença entre os indicadores de OSM e SOM se mantém relativamente constante até o caso $\chi = 1$.
+
+                Fig.
+\ref{fig:shape:vary:indicators:zeta_s} presents the shape error indicator $\zeta_S$ for both OSM and SOM methods.
+The results demonstrate that the shape error increases proportionally with contrast value, which is consistent with the expected algorithmic behavior.
+Furthermore, for $\chi = 1.5$, the indicator $\zeta_S$ exceeds 100\%, indicating that the number of incorrectly classified pixels surpasses the number of pixels composing the scatterer in the original image.
+This observation aligns with the finding that geometry recovery fails at this contrast level.
+Additionally, the difference between the OSM and SOM indicators remains relatively constant up to $\chi = 1$.
+
+                \begin{figure}[!htb]
                     \centering
-                    \subfigure[]{\includegraphics[width=0.49\columnwidth]{./experiments/vary/figs/zeta_s.eps}}
-                    \subfigure[]{\includegraphics[width=0.49\columnwidth]{./experiments/vary/figs/dnl.eps}}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                     \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}

### 2025-07-16 experiments/vary/gendata.py

@@ -7,7 +7,7 @@ import draw
 import mom_cg_fft as mom
 
 name = 'vary.cfg'
-NM = NS = 60
+NM = NS = 80
 Ro = 4.
 lambda_b = 1.
 epsilon_rb = 1.

### 2025-07-16 experiments/average/gendata.py
Mais coisas

@@ -1,5 +1,5 @@
 import sys
-sys.path.insert(1, '../../../eispy2d/library/')
+sys.path.insert(1, '../../eispy2d/library/')
 
 import configuration as cfg
 import testset as tst
@@ -37,7 +37,7 @@ testset = tst.TestSet(name=name + '.tst', configuration=config,
                       sample_size=sample_size, noise=noise,
                       indicators=indicators)
 
-testset.randomize_tests(compute_dnl=True)
+testset.randomize_tests(compute_dnl=False)
 
 testset.generate_field_data(solver=mom.MoM_CG_FFT(tolerance=1e-3,
                                                   maximum_iterations=5000))

### 2025-07-16 experiments/average/runexperiment.py

@@ -1,5 +1,5 @@
 import sys
-sys.path.insert(1, '../../../eispy2d/library/')
+sys.path.insert(1, '../../eispy2d/library/')
 
 import testset as tst
 import richmond as ric
@@ -11,7 +11,7 @@ import osm
 import bim
 import csi
 import som
-import benchamrk as bmk
+import benchmark as bmk
 
 name = 'average'
 resolution = (40, 40)

### 2025-07-16 experiments/breast/getsample.m

@@ -1,0 +1,14 @@
+clear
+
+filepath = './class3/phantom1';
+frequency = 1e9;
+epsilon_rb = 20;
+sigma_b = 0;
+new_res = [150,150];
+
+[epsilon_r,sigma,dx,dy,mi] = loadphantom2D ...
+    (filepath,frequency,epsilon_rb,sigma_b,new_res);
+
+plotsample(epsilon_r,sigma,dx,dy)
+
+save sample.mat dx dy epsilon_r sigma epsilon_rb sigma_b mi

### 2025-07-16 experiments/breast/getsampleset.m

@@ -1,0 +1,21 @@
+clear
+
+filepath = './class1/phantom1';
+namefile = 'class_1_1';
+frequency = 1e9;
+epsilon_rb = 20; % 20;
+sigma_b = 0;
+new_res = [150,150];
+slices = 5;
+
+[aux_epsilon_r,aux_sigma,dx,dy,aux_mi] = loadphantom2Dset ...
+    (filepath,frequency,epsilon_rb,sigma_b,new_res,slices);
+
+for i = 1:slices
+    epsilon_r = squeeze(aux_epsilon_r(i,:,:));
+    sigma = squeeze(aux_sigma(i,:,:));
+    mi = aux_mi{i};
+    plotsample(epsilon_r,sigma,dx,dy)
+    pause(1)
+    save([namefile,'_',num2str(i),'.mat'],'dx','dy','epsilon_r','sigma','epsilon_rb','sigma_b','mi');
+end

### 2025-07-16 experiments/breast/loadphantom2D.m

@@ -1,0 +1,106 @@
+function [epsilon_r,sigma_eff,dx,dy,mi] = loadphantom2D ...
+    (filepath,f,epsilon_rb,sigma_b,new_res)
+
+    % Constants
+    omega = 2*pi*f;
+    dx = .5e-3; dy = .5e-3; dz = .5e-3;
+    epsilon_0 = 8.854187817e-12;
+    
+    % Cole-Cole parameters - 500MHz < f < 20GHz
+    epsilon_inf = [2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.];
+    epsilon_delta = [.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31];
+    tau = 1e-12 * [16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585];
+    alpha = [.251, .069, .061, .055, .003, .047, .049, .063];
+    sigma_s = [.002, .02, .036, .083, .462, .713, .809, 1.37];
+
+    bi_file = fopen([filepath,'/breastInfo.txt'],'r');
+    breastInfo = fscanf(bi_file,'%s');
+    fclose(bi_file);
+
+    m_file = fopen([filepath '/mtype.txt'],'r');
+    mi = fscanf(m_file,'%f');
+    fclose(m_file);
+    
+    p_file = fopen([filepath '/pval.txt'],'r');
+    p_i = fscanf(p_file,'%f');
+    fclose(p_file);
+    
+    epsilon_star = epsilon_inf ...
+        + epsilon_delta./(1+(1j*omega*tau).^(1-alpha)) ...
+        + sigma_s/1j/omega/epsilon_0;
+    
+    bound_epsilon_r = real(epsilon_star);
+    bound_sigma_eff = -imag(epsilon_star)*omega*epsilon_0;
+    
+    epsilon_r = epsilon_rb * ones(size(mi));
+    sigma_eff = sigma_b * ones(size(mi));
+    
+    tissues = [3.3, 3.2, 3.1, 2, 1.3, 1.2, 1.1];
+    
+    for i = 1:length(tissues)
+        
+        epsilon_r(mi==tissues(i)) = p_i(mi==tissues(i))*bound_epsilon_r(i+1)...
+            +(1-p_i(mi==tissues(i)))*bound_epsilon_r(i);
+        
+        sigma_eff(mi==tissues(i)) = p_i(mi==tissues(i))*bound_sigma_eff(i+1)...
[…]

### 2025-07-16 experiments/breast/loadphantom2D.py

@@ -1,0 +1,185 @@
+import numpy as np
+from scipy.interpolate import RegularGridInterpolator
+import os
+
+def loadphantom2D(filepath, f, epsilon_rb, sigma_b, new_res=None):
+    """
+    Load a 2D breast phantom with electromagnetic properties.
+    
+    Parameters:
+    -----------
+    filepath : str
+        Path to the directory containing phantom data files
+    f : float
+        Frequency in Hz
+    epsilon_rb : float
+        Relative permittivity of background medium
+    sigma_b : float
+        Conductivity of background medium
+    new_res : tuple or None
+        New resolution (nx, ny) or (dx, dy) for resampling
+    
+    Returns:
+    --------
+    epsilon_r : ndarray
+        Relative permittivity distribution
+    sigma_eff : ndarray
+        Effective conductivity distribution
+    dx : float
+        Grid spacing in x direction
+    dy : float
+        Grid spacing in y direction
+    mi : ndarray
+        Indices of background medium pixels
+    """
+    
+    # Constants
+    omega = 2 * np.pi * f
+    dx = 0.5e-3
+    dy = 0.5e-3
+    dz = 0.5e-3
+    epsilon_0 = 8.854187817e-12
+    
+    # Cole-Cole parameters - 500MHz < f < 20GHz
+    epsilon_inf = np.array([2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.])
+    epsilon_delta = np.array([0.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31])
+    tau = 1e-12 * np.array([16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585])
+    alpha = np.array([0.251, 0.069, 0.061, 0.055, 0.003, 0.047, 0.049, 0.063])
+    sigma_s = np.array([0.002, 0.02, 0.036, 0.083, 0.462, 0.713, 0.809, 1.37])
+    
+    # Read breast information
+    with open(os.path.join(filepath, 'breastInfo.txt'), 'r') as bi_file:
+        breastInfo = bi_file.read().strip()
+    
+    # Read material type
+    with open(os.path.join(filepath, 'mtype.txt'), 'r') as m_file:
+        mi = np.fromfile(m_file, sep=' ')
+    
+    # Read property values
[…]

### 2025-07-16 experiments/breast/loadphantom2Dset.m

@@ -1,0 +1,115 @@
+function [epsilon_r,sigma_eff,dx,dy,mi] = loadphantom2Dset ...
+    (filepath,f,epsilon_rb,sigma_b,new_res,slices)
+
+    % Constants
+    omega = 2*pi*f;
+    dx = .5e-3; dy = .5e-3; dz = .5e-3;
+    epsilon_0 = 8.854187817e-12;
+    
+    % Cole-Cole parameters - 500MHz < f < 20GHz
+    epsilon_inf = [2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.];
+    epsilon_delta = [.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31];
+    tau = 1e-12 * [16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585];
+    alpha = [.251, .069, .061, .055, .003, .047, .049, .063];
+    sigma_s = [.002, .02, .036, .083, .462, .713, .809, 1.37];
+
+    bi_file = fopen([filepath,'/breastInfo.txt'],'r');
+    breastInfo = fscanf(bi_file,'%s');
+    fclose(bi_file);
+
+    m_file = fopen([filepath '/mtype.txt'],'r');
+    mi = fscanf(m_file,'%f');
+    fclose(m_file);
+    
+    p_file = fopen([filepath '/pval.txt'],'r');
+    p_i = fscanf(p_file,'%f');
+    fclose(p_file);
+    
+    epsilon_star = epsilon_inf ...
+        + epsilon_delta./(1+(1j*omega*tau).^(1-alpha)) ...
+        + sigma_s/1j/omega/epsilon_0;
+    
+    bound_epsilon_r = real(epsilon_star);
+    bound_sigma_eff = -imag(epsilon_star)*omega*epsilon_0;
+    
+    epsilon_r = epsilon_rb * ones(size(mi));
+    sigma_eff = sigma_b * ones(size(mi));
+    
+    tissues = [3.3, 3.2, 3.1, 2, 1.3, 1.2, 1.1];
+    
+    for i = 1:length(tissues)
+        
+        epsilon_r(mi==tissues(i)) = p_i(mi==tissues(i))*bound_epsilon_r(i+1)...
+            +(1-p_i(mi==tissues(i)))*bound_epsilon_r(i);
+        
+        sigma_eff(mi==tissues(i)) = p_i(mi==tissues(i))*bound_sigma_eff(i+1)...
[…]

### 2025-07-16 experiments/breast/loadphantom2Dset.py

@@ -1,0 +1,206 @@
+import numpy as np
+from scipy.interpolate import RegularGridInterpolator
+import os
+
+def loadphantom2Dset(filepath, f, epsilon_rb, sigma_b, new_res=None, slices=1):
+    """
+    Load a set of 2D slices from a 3D breast phantom with electromagnetic properties.
+    
+    Parameters:
+    -----------
+    filepath : str
+        Path to the directory containing phantom data files
+    f : float
+        Frequency in Hz
+    epsilon_rb : float
+        Relative permittivity of background medium
+    sigma_b : float
+        Conductivity of background medium
+    new_res : tuple or None
+        New resolution (ny, nz) or (dy, dz) for resampling
+    slices : int
+        Number of slices to extract from the phantom
+    
+    Returns:
+    --------
+    epsilon_r : ndarray
+        Relative permittivity distribution for all slices (slices x ny x nz)
+    sigma_eff : ndarray
+        Effective conductivity distribution for all slices (slices x ny x nz)
+    dx : float
+        Grid spacing in x direction
+    dy : float
+        Grid spacing in y direction
+    mi : list
+        List of background medium indices for each slice
+    """
+    
+    # Constants
+    omega = 2 * np.pi * f
+    dx = 0.5e-3
+    dy = 0.5e-3
+    dz = 0.5e-3
+    epsilon_0 = 8.854187817e-12
+    
+    # Cole-Cole parameters - 500MHz < f < 20GHz
+    epsilon_inf = np.array([2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.])
+    epsilon_delta = np.array([0.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31])
+    tau = 1e-12 * np.array([16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585])
+    alpha = np.array([0.251, 0.069, 0.061, 0.055, 0.003, 0.047, 0.049, 0.063])
+    sigma_s = np.array([0.002, 0.02, 0.036, 0.083, 0.462, 0.713, 0.809, 1.37])
+    
+    # Read breast information
+    with open(os.path.join(filepath, 'breastInfo.txt'), 'r') as bi_file:
+        breastInfo = bi_file.read().strip()
+    
+    # Read material type
+    with open(os.path.join(filepath, 'mtype.txt'), 'r') as m_file:
[…]

### 2025-07-16 experiments/breast/phantom_read.m

@@ -1,0 +1,87 @@
+%% PHANTOM_READ - Obtain permittivity and conductivity information
+% This function reads the permittivity and conductivity information as in
+% [1].
+% Inputs:
+%   filepath:   String with path to the files (breastInfo,mtype,pval)
+%   f:          Linear frequency [Hz]
+% Outpus
+%   eps:    Relative permittivity
+%   sgma:   Conductivity [S/m]
+%   mi:     Media indexes:
+%       -1:  Immersion medium
+%       -2:  Skin
+%       -4:  Muscle
+%       1.1: Fibroconnective/glandular-1
+%       1.2: Fibroconnective/glandular-2
+%       1.3: Fibroconnective/glandular-3
+%       2:   Transitional
+%       3.1: Fatty-1
+%       3.2: Fatty-2
+%       3.3: Fatty-3
+
+function [eps,sgma,mi] = phantom_read(filepath,f)
+
+    % Read main data
+    bi = fileread([filepath '/breastInfo.txt']);
+    be = strfind(bi, '=');
+    s1 = str2double(bi(be(2)+1:be(2)+3));
+    s2 = str2double(bi(be(3)+1:be(3)+3));
+    s3 = str2double(bi(be(4)+1:be(4)+3));
+    
+    % Read media indexes
+    mi = textread([filepath '/mtype.txt'],'%f');
+    mi = reshape(mi,[s1 s2 s3]);
+
+    % Read p_i data
+    p_i = textread([filepath '/pval.txt'],'%f');
+    p_i = reshape(p_i,[s1 s2 s3]);
+    
+    % Genreal parameters
+    w = 2*pi*f;
+    eps_0= 8.85e-12;
+    
+    if f>3e9 && f<=10e9 % ref paper : instruction manual
+        % 3 adipose/fat , 1 fibroglandular
+        %[min 3_low 3_med 3_high 1_low 1_med 1_high max skin mus];
+        e_i = [2.293 2.848 3.116 3.987 12.99 13.81 14.2 23.2 15.93 21.66];
+        e_d = [0.092 1.104 1.592 3.545 24.4 35.55 40.49 46.05 23.83 33.24];
+        tau = 13e-12;
+        s = [0.005 0.005 0.05 0.08 0.397 0.738 0.824 1.306 0.831 0.886];
[…]

### 2025-07-16 experiments/breast/save_data.m

@@ -1,0 +1,30 @@
+clc, clear
+
+%% General parameters
+f = 1e9;
+nsamp = 100;
+bd_epsr = [1,5];
+bd_sig = [0,1];
+img_size = [50,50];
+
+%% Bounds
+bd = [20,270]; filepath = './class1/phantom1';      % class1 - phantom1
+% bd = [26,225]; filepath = './class1/phantom2';      % class1 - phantom2
+
+%% Collecting data
+[epsilon,sigma,mi] = phantom_read(filepath,f);
+i = round(linspace(bd(1),bd(2),nsamp+2));
+i([1,end]) = [];
+epsilon = bd_epsr(1) + diff(bd_epsr)*epsilon(i,:,:)/max(epsilon(:));
+sigma = bd_sig(1) + diff(bd_sig)*sigma(i,:,:)/max(sigma(:));
+[~,J,K] = size(epsilon);
+j = round(linspace(0,J+1,img_size(1)+2));
+j([1,end]) = [];
+k = round(linspace(0,K+1,img_size(2)+2));
+k([1,end]) = [];
+epsilon = epsilon(:,j,k);
+sigma = sigma(:,j,k);
+id = filepath(3:end);
+
+%% Saving data
+save([filepath,'/phantoms.mat'],'epsilon','sigma','bd_epsr','bd_sig','id')

### 2025-07-16 experiments/position/multiple/gendata.py

@@ -1,0 +1,61 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import configuration as cfg
+import inputdata as ipt
+import result as rst
+import draw
+import mom_cg_fft as mom
+
+# Parameters
+name = 'multiple'
+NM = NS = 80
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+resolution = (200, 200)
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
+epsilon_rd = [5., 3., 2.]
+l = 0.3
+position = [.4, -.4]
+rotate = 30
+
+config = cfg.Configuration(name=name + '.cfg', number_measurements=NM, 
+                           number_sources=NS, observation_radius=Ro, 
+                           wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+
+test = ipt.InputData(name=name + '.ipt', configuration=config, 
+                     resolution=resolution, noise=noise, indicators=indicators)
+
+test.rel_permittivity, _ = draw.star5(
+    l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
+    background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd[0],
+    center=position, rotate=30.
+)
+
+test.rel_permittivity, _ = draw.rhombus(
+    l/1.5, l/1.5, axis_length_x=Lx, axis_length_y=Ly, center=[.7, .1],
+    background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd[1],
+    rotate=60, rel_permittivity=test.rel_permittivity
+)
+
+test.rel_permittivity, _ = draw.cross(
+    2*l, l, l/4, axis_length_x=Lx, axis_length_y=Ly,
+    object_rel_permittivity=epsilon_rd[2], center=[.2, 0.6], rotate=0.,
+    rel_permittivity=test.rel_permittivity
+)
+
+forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=10000,
+                         parallelization=True)
+
+test.compute_dnl()
+
+test.save(file_path='./data/')

### 2025-07-17 paper/algorithms/zetap.tex
More progress

\begin{algorithm}
\caption{Compute Position Error Indicator $\zeta_P$}
\label{alg:compute_zeta_p}
\begin{algorithmic}[1]
\REQUIRE Original contrast distribution $\boldsymbol{\chi}_o$
\REQUIRE Reconstructed contrast distribution $\boldsymbol{\chi}_r$
\ENSURE Position error indicator $\zeta_P$ (\%)

\STATE Extract magnitude information from both contrast distributions
\STATE Determine adaptive threshold based on reconstructed image dynamic range

\STATE Generate binary object masks using threshold-based classification
\STATE \quad - Original mask: pixels with non-zero contrast values
\STATE \quad - Reconstructed mask: pixels above computed threshold

\IF{no object regions detected in reconstruction}
    \RETURN complete failure indicator (100\%)
\ENDIF

\STATE Create normalized coordinate systems for both images
\STATE \quad - Map pixel coordinates to unit interval [0,1]
\STATE \quad - Handle potential resolution differences

\STATE Compute geometric centroids using weighted coordinate averaging:
\STATE \quad - Calculate center of mass for original object mask
\STATE \quad - Calculate center of mass for reconstructed object mask

\STATE Measure centroid displacement using Euclidean distance metric
\STATE Normalize distance to percentage scale relative to image dimensions

\RETURN position error as percentage of maximum possible displacement
\end{algorithmic}
\end{algorithm}

### 2025-07-17 paper/algorithms/zetas.tex
More progress

\begin{algorithm}
\caption{Compute Shape Error Indicator $\zeta_S$}
\label{alg:compute_zeta_s}
\begin{algorithmic}[1]
\REQUIRE Original contrast distribution $\boldsymbol{\chi}_o$
\REQUIRE Reconstructed contrast distribution $\boldsymbol{\chi}_r$
\REQUIRE Threshold factor $threshold = 0.5$ (default)
\ENSURE Shape error indicator $\zeta_S$ (\%)

\STATE Extract magnitude information from both contrast distributions
\STATE Determine adaptive threshold based on reconstructed image dynamic range
\STATE Apply binary classification to identify object and background regions

\IF{no object regions detected in reconstruction}
    \RETURN complete failure indicator (100\%)
\ENDIF

\STATE Extract object boundaries using contour detection methodology
\STATE Normalize spatial coordinates to handle resolution differences between images

\STATE Generate binary masks from contour information using polygon filling:
\STATE \quad - Apply odd-parity rule to determine interior points
\STATE \quad - Handle multiple contours for complex geometries

\STATE Compare geometric regions through symmetric difference operation
\STATE Quantify classification errors relative to original object size

\RETURN normalized shape error as percentage
\end{algorithmic}
\end{algorithm}

### 2025-07-17 paper/main.tex
More progress

--- 2025-07-16 main.tex
@@
 This can occur more frequently when the number of pixels of the scatterer in the original image is small.
+The Algorithm \ref{alg:compute_zeta_s} summarizes the steps for calculating the shape error indicator.
+
+            \input{algorithms/zetas.tex}
 
@@
 Furthermore, the proposed indicator is straightforward and versatile, applicable even in scenarios involving images with multiple objects.
+The Algorithm \ref{alg:compute_zeta_p} summarizes the steps for calculating the position error indicator.
+
+            \input{algorithms/zetap.tex}
 
@@
                     \centering
-                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_0.eps}}
-                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_1.eps}}
-                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_2.eps}}
-                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_3.eps}}
-                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_4.eps}} \\
-                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_0.eps}}
-                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_1.eps}}
-                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_2.eps}}
-                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_3.eps}}
-                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_4.eps}}
+                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.eps}}
+                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.eps}}
+                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.eps}}
+                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.eps}}
+                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.eps}} \\
+                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.eps}}
+                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.eps}}
+                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.eps}}
+                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.eps}}
+                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.eps}}
                     \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
@@
                     \centering
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                     \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
@@
 			\subsubsection{Average performance}\label{sec:results:position:benchmark}
+
+        \subsection{Breast Phantom Study}\label{sec:results:breast}
 

### 2025-07-17 experiments/average/runexperiment.py

@@ -39,4 +39,4 @@ benchmark = bmk.Benchmark(name=name + '.bmk', method=method,
 
 benchmark.run(parallelization=bmk.PARALLELIZE_EXECUTIONS, pre_save=True)
 
-benchmark.save(file_path='./data/', save_test=True)
+benchmark.save(file_path='./data/', save_testset=True)

### 2025-07-17 loaddata.py
Procedure to load data

@@ -1,0 +1,8 @@
+import gdown
+
+# This script downloads data from a Google Drive folder to a local directory named 'data'.
+url = "https://drive.google.com/drive/folders/1N0iAjMFQ9kaG4rDx6kGvklwJoJYoEFti?usp=drive_link"
+
+# Download the data from Google Drive
+gdown.download_folder(url, output='data', use_cookies=False)
+print("Data downloaded successfully to 'data' folder")

### 2025-07-17 paper/main.tex
Generate figures and start to write results for average performance in shape error

@@
 
+                % Quando dois ou mais algoritmos vão ser comparados, é interessante que o estudo de caso seja feito com base em um conjunto de testes que reflitam uma classe específica do problema.
+Com base nos resultados, o desempenho médio dos algoritmos pode ser medido e comparado com rigor estatítico.
+Isto dá suporte a conclusões mais robustas sobre o desempenho dos algoritmos.
+
+                When comparing two or more algorithms, it is beneficial to conduct the case study using a test set that reflects a specific class of the problem.
+Based on the results, the average performance of the algorithms can be measured and compared with statistical rigor.
+This approach supports more robust conclusions about the algorithms' performance.
+
+                Desta forma, foi conduzido um experimento para comparar o desempenho dos algoritmos LSM, OSM, BIM, CSI e SOM no indicador de erro de forma proposto.
+Para este experimento, foram considerados 30 imagens de espalhadores com formatos variados.
+O formato desses espalhadores foi gerado aleatoriamente como polígonos com 4 a 15 vértices, com um raio de distância dos vértices mais distantes do centro do espalhador variando entre 0.45$\lambda_b$ e 0.9$\lambda_b$.
+O contraste dos espalhadores foi fixado em 0.25.
+
 		\subsection{Position Detection Study}\label{sec:results:position}

### 2025-07-17 experiments/average/computednl.py

@@ -1,0 +1,23 @@
+"""
+Script to compute DNL for benchmark test cases.
+
+This script loads a benchmark dataset, computes the DNL for each test case,
+and saves the updated benchmark data with DNL values.
+"""
+
+import sys
+sys.path.insert(1, '../../eispy2d/library/')
+import benchmark as bmk
+
+# Load the benchmark dataset from the specified file and path
+benchmark = bmk.Benchmark(import_filename="average.bmk",
+                          import_filepath="../../data/shape/average/")
+
+# Compute DNL for each test case in the benchmark
+for n in range(30):
+    benchmark.testset.test[n].compute_dnl()
+
+# Save the updated benchmark data with computed DNL values
+# save_testset=True ensures that the test set data is also saved
+benchmark.save(file_path="../../data/shape/average/",
+               save_testset=True)

### 2025-07-17 experiments/average/gendata.py

@@ -8,7 +8,7 @@ import result as rst
 import mom_cg_fft as mom
 
 name = 'average'
-NM = NS = 20
+NM = NS = 80
 Ro = 4.
 lambda_b = 1.
 epsilon_rb = 1.
@@ -25,7 +25,7 @@ config = cfg.Configuration(name=name + '.cfg', number_measurements=NM,
 
 contrast = .25
 object_size = .9
-resolution = (80, 80)
+resolution = (120, 120)
 map_pattern = RANDOM_POLYGONS_PATTERN
 sample_size = 30
 noise = 5.

### 2025-07-17 experiments/average/genfigures.py

@@ -1,0 +1,115 @@
+import sys
+sys.path.insert(1, '../../eispy2d/library/')
+import benchmark as bmk
+import result as rst
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Configuration constants
+FIGURE_SIZE = (12, 8)
+BOXPLOT_SIZE = (5, 6)
+FONT_FAMILY = 'Times New Roman'
+FONT_SIZES = {'labels': 30, 'legend': 20, 'ticks': 25, 'boxplot': 25}
+LINE_STYLE = {'markersize': 11, 'linewidth': 3}
+OUTPUT_CONFIG = {'dpi': 300, 'bbox_inches': 'tight', 'format': 'eps'}
+
+# Visual styling arrays
+MARKERS = ['o', 's', '^', 'D', 'v', '<', '>', 'p', '*', 'h']
+LINE_STYLES = ['-', '--', '-.', ':', '-']
+GRAY_COLORS = ['0.7', '0.6', '0.4', '0.2', '0.0']  # light to dark gray
+
+# Algorithm names for legend
+ALGORITHM_NAMES = ['LSM', 'OSM', 'BIM', 'CSI', 'SOM']
+
+def setup_matplotlib_defaults():
+    """Set global matplotlib configuration."""
+    plt.rcParams['font.family'] = FONT_FAMILY
+
+def setup_line_styles(axis):
+    """Apply visual styling to all lines in the plot."""
+    for i, line in enumerate(axis.lines):
+        line.set_color(GRAY_COLORS[i % len(GRAY_COLORS)])
+        line.set_marker(MARKERS[i % len(MARKERS)])
+        line.set_linestyle(LINE_STYLES[i % len(LINE_STYLES)])
+        line.set_markersize(LINE_STYLE['markersize'])
+        line.set_linewidth(LINE_STYLE['linewidth'])
+
+def setup_font_styling(axis):
+    """Apply font styling to axis labels and ticks."""
+    axis.set_xlabel(axis.get_xlabel(), fontfamily=FONT_FAMILY, 
+                    fontsize=FONT_SIZES['labels'])
+    axis.set_ylabel(axis.get_ylabel(), fontfamily=FONT_FAMILY, 
+                    fontsize=FONT_SIZES['labels'])
+    axis.tick_params(labelsize=FONT_SIZES['ticks'])
+    
+    # Set font family for tick labels
[…]

### 2025-07-17 paper/main.tex
Section IV-A-3 written

--- 2025-07-17 paper/main.tex
@@
 
-        The experiments were conducted using the open-source library EISPY2D \cite{batista2022eispy2d}, specifically developed to design and evaluate algorithms for the inverse electromagnetic scattering problem.
+        The experiments were conducted using the open-source library EISPY2D \cite{batista2025eispy2d}, specifically developed to design and evaluate algorithms for the inverse electromagnetic scattering problem.
 Both indicators will be analyzed, with each approach featuring two case studies (one fundamental and the other exploring a particular aspect) as well as a benchmarking study.
@@
                     \centering
-                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.eps}}
-                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.eps}}
-                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.eps}}
-                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.eps}}
-                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.eps}} \\
-                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.eps}}
-                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.eps}}
-                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.eps}}
-                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.eps}}
-                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.eps}}
+                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.pdf}}
+                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.pdf}}
+                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.pdf}}
+                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.pdf}}
+                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.pdf}} \\
+                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.pdf}}
+                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.pdf}}
+                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.pdf}}
+                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.pdf}}
+                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.pdf}}
                     \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
@@
                     \centering
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.pdf}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.pdf}\label{fig:shape:vary:dnl}}
                     \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
@@
 			\subsubsection{Average performance}\label{sec:results:shape:average}
+
+                % Quando dois ou mais algoritmos vão ser comparados, é interessante que o estudo de caso seja feito com base em um conjunto de testes que reflitam uma classe específica do problema.
+Com base nos resultados, o desempenho médio dos algoritmos pode ser medido e comparado com rigor estatítico.
+Isto dá suporte a conclusões mais robustas sobre o desempenho dos algoritmos.
+
+                When comparing multiple algorithms, it is advantageous to conduct case studies using test sets that represent specific problem classes.
+This approach enables the measurement and statistical comparison of average algorithm performance, thereby supporting more robust and reliable conclusions regarding their relative effectiveness.
+
+                % Desta forma, foi conduzido um experimento para comparar o desempenho dos algoritmos LSM, OSM, BIM, CSI e SOM no indicador de erro de forma proposto.
+Para este experimento, foram considerados 30 imagens de espalhadores com formatos variados.
+O formato desses espalhadores foi gerado aleatoriamente como polígonos com 4 a 15 vértices, com um raio de distância dos vértices mais distantes do centro do espalhador variando entre 0.45$\lambda_b$ e 0.9$\lambda_b$.
+O contraste dos espalhadores foi fixado em 0.25 e os mesmos parâmetros para sintetização dos dados utilizados no estudo da subsubseção \ref{sec:results:shape:star} foram utilizados.
+Vale a pena destacar que, uma vez que as geometrias variam, o DNL de cada instância pode variar, conforme mostrado na Fig.
+\ref{fig:shape:average:dnl}.
+Conforme é possível observar, a mediana do DNL está acima do valor no experimento da subsubseção \ref{sec:results:shape:star}.
+No entanto, as duas são significativamente próximas, principalmente quando comparadas ao limiar de 1, que é o valor a partir do qual a Aproximação de Born deixa de ser aplicável \cite{bucci2001degree}.
+Desta forma, o objetivo do experimento é buscar evidências estatísticas que suportem a superioridade de algum dos algoritmos para essa classe de problemas.
+
+                Following such an approach, an experiment was conducted to compare the LSM, OSM, BIM, CSI, and SOM algorithms.
+This experiment utilized 30 scatterer images with varying geometries to provide a more comprehensive assessment of algorithm performance across different shape configurations.
+
+                The scatterers were randomly generated as polygons with 4 to 15 vertices, where the radius from the center to the farthest vertices ranged between 0.45$\lambda_b$ and 0.9$\lambda_b$.
+The contrast was fixed at 0.25 for all scatterers, and the data synthesis parameters from Section \ref{sec:results:shape:star} were maintained for consistency.
+
+                Due to the geometric variations, the DNL for each instance varies accordingly, as illustrated in Fig.
+\ref{fig:shape:average:dnl}.
+The median DNL exceeds the value from the experiment in Section \ref{sec:results:shape:star}, though both remain significantly below the threshold of 1, above which the Born Approximation becomes inapplicable \cite{bucci2001degree}.
+This experimental design enables the assessment of statistical evidence supporting the superiority of any algorithm within this problem class.
+
+                \begin{figure}[!htb]
+                    \centering
+                    \subfigure[]{\includegraphics[width=.5\columnwidth]{../experiments/average/figs/dnl.pdf}\label{fig:shape:average:dnl}} \\
+                    \subfigure[]{\includegraphics[width=\columnwidth]{../experiments/average/figs/plot.pdf}\label{fig:shape:average:zeta_s}}
+                    \caption{Shape recovering study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) shape error indicator $\zeta_S$ for each algorithm in each instance.}
+                    \label{fig:shape:average}   
+                \end{figure}
+
+                % Fig.
+\ref{fig:shape:average:zeta_s} shows the shape error indicator $\zeta_S$ for each algorithm across all instances.
+É possível observar uma clara diferença entre o LSM e os demais algoritmos, com o LSM apresentando o pior desempenho.
+Os outros métodos possuem desempenhos similares, embora seja possível observar que o OSM possuiu um erro maior em um número significativo de instâncias e que o CSI, por sua vez, teve um desempenho ligeiramente melhor em um número significativo de instâncias.
+
+                Fig.
+\ref{fig:shape:average:zeta_s} presents the shape error indicator $\zeta_S$ for each algorithm across all test instances.
+The results reveal a clear performance distinction when considering LSM, which demonstrates significantly worse performance compared to the other methods.
+Among the remaining algorithms, while overall performance levels appear similar, some patterns emerge: OSM exhibits higher error rates across a significant number of instances, whereas CSI demonstrates superior performance in a significant portion of the test cases.
+
+                % Enquanto a análise da Fig.
+\ref{fig:shape:average:zeta_s} oferece as primeiras impressões sobre os resultados, a aplicação de testes estatísticos é necessária para validar as conclusões.
+Para isso, o teste de Friedman foi aplicado para verificar se existe uma diferença significativa entre os algoritmos.
+O teste de Friedman é um teste não paramétrico que avalia diferenças pareadas significativas entre três ou mais grupos relacionados.
+Neste caso, os grupos são os algoritmos e as medições são os valores do indicador $\zeta_S$ para cada algoritmo em cada instância.
+Uma vez que o LSM apresentou um desempenho significativamente pior que os demais algoritmos, ele foi removido da análise estatística.
+
+                While Fig.
+\ref{fig:shape:average:zeta_s} provides initial insights into the results, statistical testing is important to validate the conclusions rigorously.
+To this end, the Friedman test \cite{friedman1937use} was applied to assess whether significant differences exist among the algorithms.
+The Friedman test is a non-parametric statistical test that evaluates significant differences between three or more related groups when the data does not meet the assumptions for parametric tests.
+In this context, the groups correspond to the algorithms, and the measurements are the $\zeta_S$ indicator values for each algorithm across all instances.
+Given that LSM demonstrated substantially inferior performance compared to the other algorithms, it was excluded from the statistical analysis to focus on the more competitive methods.
+
+                % O resultado do teste de Friedman foi $p < 10^{-10}$, indicando que existe pelo menos um par de algoritmos com uma diferença significativa.
+Em seguida, foi aplicado o teste de Wilcoxon para identificar quais algoritmos possuem diferenças significativas entre si.
+Os valores-p obtidos pelos testes são apresentados na Tabela \ref{tab:shape:average:pvalue}.
+Conforme é indicado na tabela, a hipótese nula de que os algoritmos possuem desempenhos iguais é rejeitada para todos os pares de algoritmos.
+
+                The Friedman test result was $p < 10^{-10}$, indicating that at least one pair of algorithms shows a significant mean paired difference.
+Subsequently, the Wilcoxon test was applied to identify which algorithms have significant mean paired differences between them.
+The p-values obtained from these tests are presented in Table \ref{tab:shape:average:pvalue}.
+As shown in the table, the null hypothesis that algorithms have equal performance is rejected for all algorithm pairs.
+
+                \begin{table*}
+                    \centering
+                    \renewcommand{\arraystretch}{1.5}
+                    \caption{Comparison of $p$-values between methods.}
+                    \label{tab:shape:average:pvalue}
+                    \begin{tabular}{ccccccc}
+                        Pairs & OSM-BIM & OSM-CSI & OSM-SOM & BIM-CSI & BIM-SOM & CSI-SOM \\\hline
+                        $p$-value & $<10{-4}$ & $<10{-8}$ & $<10{-3}$ & $<10{-2}$ & $<10{-2}$ & $<10{-8}$ \\  
+                    \end{tabular}
+                \end{table*}
+
+                % Para complementar a análise, a Fig.
+\ref{fig:shape:average:confidence_intervals} apresenta os intervalos de confiança (95\%) para a média das diferenças pareadas do indicador de erro de forma $\zeta_S$ para cada par de algoritmos.
+Em todos os casos, foi necessária alguma forma de transformação dos dados (logarítmica, raiz quadrada ou Box-Cox) para que os dados seguissem uma distribuição normal.
+No entanto, no gráfico, os dados foram transformados de volta para a escala original.
+Como é possível observar, a média das diferenças sempre favorece o CSI, o que significa que o teste fornece evidência para a superiodidade do CSI em relação aos demais algoritmos.
+Além disso, o OSM é significativamente pior que o BIM e o SOM, enquanto o BIM possui desempenho melhor que o SOM.
+No entanto, vale à pena destacar que, essas diferenças, na média, não são maiores que 5\%.
+Por fim, vale à pena observar que, enquanto no estudo da seção \ref{sec:results:shape:star} o CSI teve um desempenho pior que o BIM e o SOM, neste estudo de benchmarking, o CSI teve um desempenho melhor que ambos.
+Isso reforça a importância de realizar estudos de benchmarking combinados com análises estatísticas para obter conclusões mais robustas sobre o desempenho dos algoritmos.
+
+                To complement the analysis, Fig.
+\ref{fig:shape:average:confidence_intervals} presents the 95\% confidence intervals for the mean paired differences of the shape error indicator $\zeta_S$ for each algorithm pair.
+As observed, the differences consistently favor CSI, providing evidence for CSI's superiority over the other algorithms.
+Additionally, OSM performs significantly worse than both BIM and SOM, while BIM outperforms SOM.
+However, these differences average less than 5\%.
+
+                It is worth observing that while CSI performed worse than BIM and SOM in the single scatterer study (Section \ref{sec:results:shape:star}), CSI demonstrated superior performance to both methods in this benchmarking study.
+This highlights the importance of conducting comprehensive benchmarking studies combined with statistical analysis to obtain more robust conclusions about algorithm average performance.
+
+                \begin{figure}
+                    \centering
+                    \includegraphics[width=.9\columnwidth]{../experiments/average/figs/confidence_intervals.pdf}
+                    \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
+                    \label{fig:shape:average:confidence_intervals}
+                \end{figure}
+
+                % Com base nos resultados, foi possível aplicar o teste de Friedman \cite{friedman1937use} para verificar se existe uma diferença significativa entre os algoritmos.
+O teste de Friedman é um teste não paramétrico que verifica se existe uma diferença significativa entre três ou mais grupos relacionados.
+Neste caso, os grupos são os algoritmos e as medições são os valores do indicador $\zeta_S$ para cada algoritmo em cada instância.
+O resultado do teste de Friedman foi $p = 0.0001$, indicando que existe uma diferença significativa entre os algoritmos.
+Em seguida, foi aplicado o teste de Nemenyi \cite{nemenyi1963distribution} para verificar quais algoritmos possuem diferenças significativas entre si.
+O resultado do teste de Nemenyi indicou que o LSM é significativamente pior que todos os outros algoritmos, enquanto os demais métodos não possuem diferenças significativas entre si.
 

### 2025-07-17 eispy2d/library/benchmark.py

@@ -3965,7 +3965,7 @@ class Benchmark(exp.Experiment):
         if show or file_name is not None:
             plot_figure = True
         else:
-            plot_figure = False
+            plot_figure = True
 
         if self._single_method and self._single_testset:
             message = 'Confidence Intervals\n'
@@ -4265,7 +4265,7 @@ class Benchmark(exp.Experiment):
                 plt.show()
             if file_name is not None:
                 plt.close()
-            elif not show:
+            else:
                 return fig, axis
 
     def _search_testset(self, name):

### 2025-07-17 eispy2d/library/experiment.py

@@ -1,5 +1,6 @@
 from abc import ABC, abstractmethod
 import numpy as np
+from scipy.special import inv_boxcox
 import configuration as cfg
 import result as rst
 import inverse as inv
@@ -334,8 +335,21 @@ class Experiment(ABC):
             message += ' (Transformation: ' + transformation + '), '
         else:
             message += ', '
+        if transformation == 'log':
+            a = np.exp(cfi[0])
+            b = np.exp(cfi[1])
+        elif transformation == 'sqrt':
+            a = cfi[0]**2
+            b = cfi[1]**2
+        elif transformation is not None and transformation.startswith('boxcox'):
+            lambda_value = float(transformation.split('=')[1].split(')')[0])
+            a = inv_boxcox(cfi[0], lambda_value)
+            b = inv_boxcox(cfi[1], lambda_value)
+        else:
+            a = cfi[0]
+            b = cfi[1]
         message += ('%.1f Confi. In.: ' % (confidence_level*100)
-                    + '(%.2e, ' % cfi[0] + '%.2e)\n' % cfi[1])
+                    + '(%.2e, ' % a + '%.2e)\n' % b)
         return message
 
     def _print_non_normal_data(self, sample_name):

### 2025-07-17 experiments/average/genfigures.py

@@ -8,6 +8,7 @@ import matplotlib.pyplot as plt
 # Configuration constants
 FIGURE_SIZE = (12, 8)
 BOXPLOT_SIZE = (5, 6)
+CI_PLOT_SIZE = (10, 6)
 FONT_FAMILY = 'Times New Roman'
 FONT_SIZES = {'labels': 30, 'legend': 20, 'ticks': 25, 'boxplot': 25}
 LINE_STYLE = {'markersize': 11, 'linewidth': 3}
@@ -67,31 +68,60 @@ def create_zeta_plot(benchmark):
     fig.set_size_inches(*FIGURE_SIZE)
     fig.tight_layout()
     fig.savefig('./figs/plot.eps', **OUTPUT_CONFIG)
+    plt.close(fig)  # Close figure to free memory
     
     return fig
 
 def create_dnl_boxplot(benchmark):
     """Create and style the DNL boxplot."""
-    # Extract DNL data efficiently
+    # Extract DNL data efficiently using list comprehension
     dnl_data = np.array([test.dnl for test in benchmark.testset.test[:30]])
     
-    # Create boxplot
+    # Create boxplot with consistent figure size
     fig, ax = plt.subplots(figsize=BOXPLOT_SIZE)
     box_plot = ax.boxplot(dnl_data, vert=True, patch_artist=True)
     
-    # Style boxplot
+    # Style boxplot elements
     box_plot['boxes'][0].set_facecolor('lightgray')
     box_plot['medians'][0].set_color('black')
     
-    # Configure axes
-    ax.set_ylabel('DNL', fontsize=FONT_SIZES['boxplot'])
+    # Apply consistent font styling
+    ax.set_ylabel('DNL', fontfamily=FONT_FAMILY, fontsize=FONT_SIZES['boxplot'])
     ax.tick_params(axis='both', which='major', labelsize=FONT_SIZES['boxplot'])
     ax.tick_params(axis='x', labelbottom=False)  # Remove x-axis labels
-    ax.grid(True)
+    ax.grid(True, alpha=0.3)
     
-    # Save and cleanup
+    # Apply font family to tick labels
+    for label in ax.get_yticklabels():
+        label.set_fontfamily(FONT_FAMILY)
+    
+    # Save with consistent configuration
     fig.tight_layout()
     fig.savefig('./figs/dnl.eps', **OUTPUT_CONFIG)
+    plt.close(fig)
+    
+    return fig
+
+def create_confidence_interval_plot(benchmark):
[…]

### 2025-07-18 paper/main.tex
Beginning of the section IV-B

@@
                     \centering
-                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.pdf}}
-                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.pdf}}
-                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.pdf}}
-                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.pdf}}
-                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.pdf}} \\
-                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.pdf}}
-                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.pdf}}
-                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.pdf}}
-                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.pdf}}
-                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.pdf}}
+                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.eps}}
+                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.eps}}
+                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.eps}}
+                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.eps}}
+                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.eps}} \\
+                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.eps}}
+                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.eps}}
+                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.eps}}
+                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.eps}}
+                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.eps}}
                     \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
@@
                     \centering
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.pdf}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.pdf}\label{fig:shape:vary:dnl}}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                     \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
@@
                     \centering
-                    \includegraphics[width=.9\columnwidth]{../experiments/average/figs/confidence_intervals.pdf}
+                    \includegraphics[width=.8\columnwidth]{../experiments/average/figs/confidence_intervals.pdf}
                     \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
@@
 		\subsection{Position Detection Study}\label{sec:results:position}
+
+            % Em muitas configurações nas quais os algoritmos conseguem reconstruir adequadamene a geometria dos espalhadores, o erro na detecção da posição dos espalhadores tende a ser baixo.
+Por exemplo, no estudo da seção \ref{sec:results:shape:star}, o indicador $\zeta_P$ obtido pelo LSM, OSM, BIM, CSI e SOM foram, respectivamente, 0.049\%, 0.057\%, 0.25\%, 0.31\% e 0.14\%.
+Isto porque a geometria e a posição são características dos espalhadores que, normalmente, os algoritmos não lidam com isso em separado.
+
+            In many scenarios where algorithms can adequately reconstruct the geometry of scatterers, the error in detecting scatterer positions tends to be low.
+For example, in the study described in Section \ref{sec:results:shape:star}, the $\zeta_P$ indicator values obtained by LSM, OSM, BIM, CSI, and SOM were 0.049\%, 0.057\%, 0.25\%, 0.31\%, and 0.14\%, respectively.
+This occurs because geometry and position are scatterer characteristics that algorithms typically do not handle separately.
+
+            % Uma exceção seria no caso de algoritmos que resolvem o problema de imageamento como um problema de otimização no qual as variáveis de decisão são a posição, os vértices (ou outras características de uma geometria predefinida) e o contraste dos espalhadores \cite{michalski2000electromagnetic,salucci2022learned,zardi2025physics}.
+Além disso, em cenários com espalhadores fortes, os métodos tradicionais geralmente não conseguem recuperar muito bem a geometria dos espalhadores, dada a maior dificuldade do problema.
+Nesses cenários, o estudo da detecção da posição pode ser mais relevante.
+
+            An exception would be algorithms that solve the imaging problem as an optimization problem, where the decision variables are the position, vertices (or other characteristics of a predefined geometry), and contrast of the scatterers \cite{michalski2000electromagnetic,salucci2022learned,zardi2025physics}.
+Additionally, in scenarios involving strong scatterers, traditional methods generally struggle to recover scatterer geometry effectively due to the increased problem hardness.
+In such scenarios, studying position detection becomes more relevant.
+
+            % Levando isso em consideração, os experimentos dessa seção foram formulados considerando espalhadores fortes, nos quais os métodos tradicionais não conseguem recuperar adequadamente a geometria dos espalhadores.
+Com isso, o indicador de erro de posição $\zeta_P$ pode ser uma métrica relevante para comparar desempenho nesse tipo de cenário.
+
+            Considering this, the experiments in this section were designed for scenarios involving strong scatterers, where traditional methods cannot adequately recover scatterer geometry.
+Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.
 

### 2025-07-18 experiments/average/runexperiment.py

@@ -37,6 +37,7 @@ discretization = ric.Richmond(configuration=testset.test[0].configuration,
 benchmark = bmk.Benchmark(name=name + '.bmk', method=method, 
                           discretization=discretization, testset=testset)
 
-benchmark.run(parallelization=bmk.PARALLELIZE_EXECUTIONS, pre_save=True)
+benchmark.run(parallelization=bmk.PARALLELIZE_EXECUTIONS, pre_save=True,
+              file_path='./data/')
 
 benchmark.save(file_path='./data/', save_testset=True)

### 2025-07-19 paper/main.tex
Finish section IV-A-3

@@
 \usepackage{xcolor}
+\usepackage{epstopdf}
+
+\graphicspath{{../}}
+\epstopdfsetup{
+    program@epstopdf=epstopdf
+}
 
@@
                     \centering
-                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_0.eps}}
-                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_1.eps}}
-                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_2.eps}}
-                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_3.eps}}
-                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{../experiments/vary/figs/osm_4.eps}} \\
-                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_0.eps}}
-                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_1.eps}}
-                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_2.eps}}
-                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_3.eps}}
-                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{../experiments/vary/figs/som_4.eps}}
+                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_0.eps}}
+                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_1.eps}}
+                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_2.eps}}
+                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_3.eps}}
+                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_4.eps}} \\
+                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_0.eps}}
+                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_1.eps}}
+                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_2.eps}}
+                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_3.eps}}
+                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_4.eps}}
                     \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
@@
                     \centering
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{../experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                     \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
@@
                     \centering
-                    \subfigure[]{\includegraphics[width=.5\columnwidth]{../experiments/average/figs/dnl.pdf}\label{fig:shape:average:dnl}} \\
-                    \subfigure[]{\includegraphics[width=\columnwidth]{../experiments/average/figs/plot.pdf}\label{fig:shape:average:zeta_s}}
+                    \subfigure[]{\includegraphics[width=.5\columnwidth]{./experiments/average/figs/dnl.eps}\label{fig:shape:average:dnl}} \\
+                    \subfigure[]{\includegraphics[width=\columnwidth]{./experiments/average/figs/plot.eps}\label{fig:shape:average:zeta_s}}
                     \caption{Shape recovering study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) shape error indicator $\zeta_S$ for each algorithm in each instance.}
@@
 The results reveal a clear performance distinction when considering LSM, which demonstrates significantly worse performance compared to the other methods.
-Among the remaining algorithms, while overall performance levels appear similar, some patterns emerge: OSM exhibits higher error rates across a significant number of instances, whereas CSI demonstrates superior performance in a significant portion of the test cases.
+Among the remaining algorithms, while overall performance levels appear similar, some patterns emerge: CSI exhibits higher error rates across a significant number of instances, whereas BIM demonstrates superior performance in a significant portion of the test cases.
 
@@
 \ref{fig:shape:average:zeta_s} provides initial insights into the results, statistical testing is important to validate the conclusions rigorously.
-To this end, the Friedman test \cite{friedman1937use} was applied to assess whether significant differences exist among the algorithms.
-The Friedman test is a non-parametric statistical test that evaluates significant differences between three or more related groups when the data does not meet the assumptions for parametric tests.
+To this end, Randomized Complete Block Design (RCBD) was applied to assess whether significant paired differences exist among the algorithms.
+RCBD is a statistical test which is used to evaluate significant paired differences between three or more related groups when the data meet the assumptions for parametric tests.
 In this context, the groups correspond to the algorithms, and the measurements are the $\zeta_S$ indicator values for each algorithm across all instances.
@@
 
-                The Friedman test result was $p < 10^{-10}$, indicating that at least one pair of algorithms shows a significant mean paired difference.
-Subsequently, the Wilcoxon test was applied to identify which algorithms have significant mean paired differences between them.
+                After validating normality assumption, the p-value computed by RCBD result was less than $10^{-15}$, indicating that at least one pair of algorithms shows a significant mean paired difference.
+Subsequently, multiple paired T-Test with Bonferroni correction were applied to identify which algorithms have significant mean paired differences between them.
 The p-values obtained from these tests are presented in Table \ref{tab:shape:average:pvalue}.
-As shown in the table, the null hypothesis that algorithms have equal performance is rejected for all algorithm pairs.
+As shown in the table, the null hypothesis that algorithms have equal performance is rejected for all algorithm pairs, except for OSM-SOM, indicating that OSM and SOM do not exhibit a significant difference in their average performance.
 
@@
                     \renewcommand{\arraystretch}{1.5}
-                    \caption{Comparison of $p$-values between methods.}
+                    \caption{Shape recovering study, average performance: $p$-values for the paired T-Test with Bonferroni correction.}
                     \label{tab:shape:average:pvalue}
@@
                         Pairs & OSM-BIM & OSM-CSI & OSM-SOM & BIM-CSI & BIM-SOM & CSI-SOM \\\hline
-                        $p$-value & $<10{-4}$ & $<10{-8}$ & $<10{-3}$ & $<10{-2}$ & $<10{-2}$ & $<10{-8}$ \\  
+                        $p$-value & $<10^{-2}$ & $<10^{-11}$ & 0.15 & $<10^{-7}$ & $<10^{-4}$ & $<10^{-6}$ \\  
                     \end{tabular}
@@
 \ref{fig:shape:average:confidence_intervals} presents the 95\% confidence intervals for the mean paired differences of the shape error indicator $\zeta_S$ for each algorithm pair.
-As observed, the differences consistently favor CSI, providing evidence for CSI's superiority over the other algorithms.
-Additionally, OSM performs significantly worse than both BIM and SOM, while BIM outperforms SOM.
-However, these differences average less than 5\%.
+As observed, the differences consistently favor BIM, providing evidence for BIM's superiority over the other algorithms.
+Additionally, CSI performs significantly worse than both BIM, OSM and SOM.
+However, all differences in average performance are less than 7\%.
 
-                It is worth observing that while CSI performed worse than BIM and SOM in the single scatterer study (Section \ref{sec:results:shape:star}), CSI demonstrated superior performance to both methods in this benchmarking study.
-This highlights the importance of conducting comprehensive benchmarking studies combined with statistical analysis to obtain more robust conclusions about algorithm average performance.
+                Furthermore, it is noteworthy that BIM also achieved the best performance in the study from Section \ref{sec:results:shape:star}.
+However, while the difference between SOM and OSM was significant in the experiment from Section \ref{sec:results:shape:star}, this benchmarking study provided evidence for performance equivalence between these two methods.
+In other words, if conclusions were drawn based solely on the case study, this could lead to a misconception about the performance of these two methods in this problem configuration.
+Therefore, this reinforces the importance of conducting benchmarking studies combined with statistical analyses to obtain more robust conclusions about algorithm performance.
 
@@
                     \centering
-                    \includegraphics[width=.8\columnwidth]{../experiments/average/figs/confidence_intervals.pdf}
+                    \includegraphics[width=.8\columnwidth]{./experiments/average/figs/confidence_intervals.eps}
                     \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}

### 2025-07-19 experiments/vary/gendata.py
Set data generation and experiment: section IV-A-2

@@ -54,4 +54,4 @@ for n in range(len(epsilon_rd)):
     test.compute_dnl()
     
     print('ok!')
-    test.save()
+    test.save(file_path='../../data/shape/vary/')

### 2025-07-19 experiments/vary/runexperiment.py

@@ -10,10 +10,12 @@ import stopcriteria as stp
 
 name = 'vary'
 resolution = (40, 40)
+file_path = '../../data/shape/vary/'
 
 tests = []
 for n in range(5):
-    tests.append(ipt.InputData(import_filename=name + '%d' % n + '.ipt'))
+    tests.append(ipt.InputData(import_filename=name + '%d' % n + '.ipt',
+                               import_filepath=file_path))
 
 methods = [
     osm.OrthogonalitySamplingMethod(threshold=.35),
@@ -31,4 +33,4 @@ for n in range(len(tests)):
 
     caseestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True)
 
-    caseestudy.save(save_test=True)
+    caseestudy.save(save_test=True, file_path=file_path)

### 2025-07-21 experiments/vary/genfigures.py
Finish Section IV-A-2

@@ -8,7 +8,7 @@ import configuration as cfg
 
 N = 5
 casestudies = [cst.CaseStudy(import_filename='vary%d.cst' % n,
-                             import_filepath='./data/') for n in range(N)]
+                             import_filepath='../../data/shape/vary/') for n in range(N)]
 chi = np.array([.25, .5, .75, 1., 1.5])
 
 plt.rcParams['font.family'] = 'serif'

### 2025-07-21 experiments/position/single/gendata.py
Developing case study

@@ -1,5 +1,5 @@
 import sys
-sys.path.insert(1, '../../../../eispy2d/library/')
+sys.path.insert(1, '../../../eispy2d/library/')
 
 import configuration as cfg
 import inputdata as ipt
@@ -9,6 +9,7 @@ import mom_cg_fft as mom
 
 # Parameters
 name = 'single'
+file_path = "../../../data/position/single/"
 NM = NS = 80
 Ro = 4.
 lambda_b = 1.
@@ -50,4 +51,4 @@ _ = forward.solve(test)
 
 test.compute_dnl()
 
-test.save(file_path='./data/')
+test.save(file_path='../data/')

### 2025-07-21 experiments/position/single/runsom.py

@@ -1,0 +1,26 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import inputdata as ipt
+import som
+import stopcriteria as stp
+import richmond as ric
+
+file_path = '../../../data/position/single/'
+file_name = 'star4.ipt'
+
+test = ipt.InputData.importdata(import_filename=file_name,
+                                import_filepath=file_path)
+
+resolution = (40, 40)
+
+discretization = ric.Richmond(configuration=test.configuration,
+                              elements=resolution)
+
+method = som.SubspaceBasedOptimizationMethod(
+    stp.StopCriteria(max_iterations=600), cutoff_index=15
+)
+
+result = method.solve(test, discretization, print_info=True)
+
+result.save(file_path=file_path)

### 2025-07-21 experiments/position/single/runsom.py
Finish study with high contrast star

@@ -9,8 +9,7 @@ import richmond as ric
 file_path = '../../../data/position/single/'
 file_name = 'star4.ipt'
 
-test = ipt.InputData.importdata(import_filename=file_name,
-                                import_filepath=file_path)
+test = ipt.InputData(import_filename=file_name, import_filepath=file_path)
 
 resolution = (40, 40)
 
@@ -18,7 +17,7 @@ discretization = ric.Richmond(configuration=test.configuration,
                               elements=resolution)
 
 method = som.SubspaceBasedOptimizationMethod(
-    stp.StopCriteria(max_iterations=600), cutoff_index=15
+    stp.StopCriteria(max_iterations=1000), cutoff_index=15
 )
 
 result = method.solve(test, discretization, print_info=True)

### 2025-07-22 experiments/position/multiple/gendata.py
Prepare experiments of section IV-B-2

@@ -9,6 +9,7 @@ import mom_cg_fft as mom
 
 # Parameters
 name = 'multiple'
+file_path = '../../../data/position/multiple/'
 NM = NS = 80
 Ro = 4.
 lambda_b = 1.
@@ -16,11 +17,11 @@ epsilon_rb = 1.
 Lx = Ly = 2.
 E0 = 1.
 perfect_dielectric = True
-resolution = (200, 200)
+resolution = (180, 180)
 noise = 5.
 indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
-epsilon_rd = [5., 3., 2.]
-l = 0.3
+epsilon_rd = [5., 4., 3.5]
+l = 0.1
 position = [.4, -.4]
 rotate = 30
 
@@ -42,20 +43,22 @@ test.rel_permittivity, _ = draw.star5(
 )
 
 test.rel_permittivity, _ = draw.rhombus(
-    l/1.5, l/1.5, axis_length_x=Lx, axis_length_y=Ly, center=[.7, .1],
+    l, l, axis_length_x=Lx, axis_length_y=Ly, center=[.7, .1],
     background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd[1],
     rotate=60, rel_permittivity=test.rel_permittivity
 )
 
 test.rel_permittivity, _ = draw.cross(
-    2*l, l, l/4, axis_length_x=Lx, axis_length_y=Ly,
+    2*l, 2*l, l/2, axis_length_x=Lx, axis_length_y=Ly,
     object_rel_permittivity=epsilon_rd[2], center=[.2, 0.6], rotate=0.,
     rel_permittivity=test.rel_permittivity
 )
 
-forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=10000,
+forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=10_000,
                          parallelization=True)
+
+_ = forward.solve(test)
 
 test.compute_dnl()
 
-test.save(file_path='./data/')
+test.save(file_path=file_path)

### 2025-07-22 experiments/position/multiple/runexperiment.py

@@ -15,8 +15,8 @@ import csi
 import som
 import circleapproximation as ca
 
-name = 'single'
-file_path = "../../../data/position/single/"
+name = 'multiple'
+file_path = "../../../data/position/multiple/"
 resolution = (40, 40)
 contrast_range = (0.1, 10.)
 

### 2025-07-22 eispy2d/library/circleapproximation.py
Refine position indicator experiments

@@ -119,7 +119,7 @@ class CircleApproximation(stc.Stochastic):
 
         if self.solver == "de":
             solution = differential_evolution(
-                objfun, bounds, args=(inputdata,), strategy='best1bin', maxiter=10,
+                objfun, bounds, args=(inputdata,), strategy='best1bin', maxiter=50,
                 popsize=15, tol=0.01, mutation=(0.5, 1), recombination=0.7,
                 seed=None, callback=callback, disp=False, polish=True,
                 init='latinhypercube', atol=0, updating='deferred', workers=-1, 

### 2025-07-22 experiments/position/average/gendata.py

@@ -1,0 +1,45 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import configuration as cfg
+import testset as tst
+from experiment import RANDOM_POLYGONS_PATTERN
+import result as rst
+import mom_cg_fft as mom
+
+name = 'average'
+NM = NS = 80
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+
+config = cfg.Configuration(name=name + '.cfg', number_measurements=NM,
+                           number_sources=NS, observation_radius=Ro,
+                           wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+contrast = 7.
+object_size = .15
+resolution = (160, 160)
+map_pattern = RANDOM_POLYGONS_PATTERN
+sample_size = 30
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
+
+testset = tst.TestSet(name=name + '.tst', configuration=config,
+                      contrast=contrast, object_size=object_size, 
+                      resolution=resolution, map_pattern=map_pattern,
+                      sample_size=sample_size, noise=noise,
+                      indicators=indicators)
+
+testset.randomize_tests(compute_dnl=True)
+
+testset.generate_field_data(solver=mom.MoM_CG_FFT(tolerance=1e-3,
+                                                  maximum_iterations=10_000))
+
+testset.save(file_path='../../../data/shape/average/',)

### 2025-07-22 experiments/position/average/runexperiment.py

@@ -1,26 +1,27 @@
 import sys
 sys.path.insert(1, '../../../eispy2d/library/')
 
-import inputdata as ipt
-import casestudy as cst
+import testset as tst
 import richmond as ric
 import regularization as reg
 import mom_cg_fft as mom
 import stopcriteria as stp
-import stochastic as stc
 import lsm
 import osm
 import bim
 import csi
 import som
+import benchmark as bmk
 import circleapproximation as ca
+import stochastic as stc
 
-name = 'single'
-file_path = "../../../data/position/single/"
+name = 'average'
+filepath = '../../../data/position/average/'
 resolution = (40, 40)
 contrast_range = (0.1, 10.)
 
-test = ipt.InputData(import_filename=name + '.ipt', import_filepath=file_path)
+testset = tst.TestSet(import_filename=name + '.tst',
+                      import_filepath=filepath)
 
 method = [
     lsm.LinearSamplingMethod(alias='lsm',
@@ -38,15 +39,13 @@ method = [
                            solver="de")
 ]
 
-discretization = ric.Richmond(configuration=test.configuration,
+discretization = ric.Richmond(configuration=testset.test[0].configuration,
                               elements=resolution)
 
-casestudy = cst.CaseStudy(name=name + '.cst',
-                           method=method,
-                           discretization=discretization,
-                           test=test, stochastic_runs=1)
+benchmark = bmk.Benchmark(name=name + '.bmk', method=method, 
+                          discretization=discretization, testset=testset)
 
-casestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True,
-              file_path=file_path)
+benchmark.run(parallelization=bmk.PARALLELIZE_EXECUTIONS, pre_save=True,
+              file_path=filepath)
 
-casestudy.save(save_test=True, file_path=file_path)
+benchmark.save(file_path=filepath, save_testset=True)

### 2025-07-22 experiments/position/multiple/gendata.py

@@ -17,7 +17,7 @@ epsilon_rb = 1.
 Lx = Ly = 2.
 E0 = 1.
 perfect_dielectric = True
-resolution = (180, 180)
+resolution = (160, 160)
 noise = 5.
 indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
 epsilon_rd = [5., 4., 3.5]

### 2025-07-22 experiments/position/multiple/runexperiment.py

@@ -32,7 +32,7 @@ method = [
     csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=300)),
     som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
                                         cutoff_index=5),
-    ca.CircleApproximation(stc.OutputMode(stc.EACH_EXECUTION),
+    ca.CircleApproximation(stc.OutputMode(stc.BEST_CASE, reference='zeta_s'),
                            number_executions=1,
                            contrast_range=contrast_range,
                            solver="de")
@@ -44,7 +44,7 @@ discretization = ric.Richmond(configuration=test.configuration,
 casestudy = cst.CaseStudy(name=name + '.cst',
                            method=method,
                            discretization=discretization,
-                           test=test)
+                           test=test, stochastic_runs=1)
 
 casestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True,
               file_path=file_path)

### 2025-07-22 experiments/position/single/gendata.py

@@ -20,8 +20,8 @@ perfect_dielectric = True
 resolution = (160, 160)
 noise = 5.
 indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR, rst.OBJECTIVE_FUNCTION]
-epsilon_rd = 6.
-l = 0.3
+epsilon_rd = 8.
+l = 0.1
 position = [.4, -.4]
 rotate = 30
 
@@ -44,9 +44,7 @@ test.rel_permittivity, _ = draw.star5(
     center=position, rotate=30.
 )
 
-test.draw(show=True)
-
-forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=10000,
+forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=10_000,
                          parallelization=True)
 
 _ = forward.solve(test, PRINT_INFO=False)

### 2025-07-22 experiments/position/multiple/gendata.py
Fixing details on experiments

@@ -21,7 +21,7 @@ resolution = (160, 160)
 noise = 5.
 indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
 epsilon_rd = [5., 4., 3.5]
-l = 0.1
+l = 0.15
 position = [.4, -.4]
 rotate = 30
 

### 2025-07-22 paper/main.tex
Finish Section IV-A-2
More things written

@@
 
-        For all experiments, the following common parameters were used: $\lambda_b$ = 1 m, noise level = 5\%, relative permittivity of the background medium $\epsilon_{rb}$ = 1, and incident wave amplitude = 1 V/m.
+        % For all experiments, the following common parameters were used: $\lambda_b$ = 1 m, noise level = 5\%, relative permittivity of the background medium $\epsilon_{rb}$ = 1, and incident wave amplitude = 1 V/m.
 Data synthesis was performed using the MoM-CG-FFT algorithm \cite{su1987calculation} with 5000 iterations.
+A total of 80 measurement points ($N_M$) and 80 incidence angles ($N_S$) were used.
+The dimensions of the DoI were set to $2\lambda_b\times2\lambda_b$, and the measurement points' distance radius $R_O$ was fixed at $4\lambda_b$.
+All reconstructions were performed using a discretization of 40$\times$40 pixels.
+
+        For all experiments, the following common parameters were used: background wavelength $\lambda_b = 1$ m, noise level of 5\%, relative permittivity of the background medium $\epsilon_{rb} = 1$, and incident wave amplitude of 1 V/m.
+
+        Data synthesis was performed using the MoM-CG-FFT algorithm \cite{su1987calculation} with 5000 iterations.
+The measurement configuration consisted of 80 measurement points ($N_M$) and 80 incidence angles ($N_S$), with measurement points arranged in a circular array at distance $R_O = 4\lambda_b$ from the DOI center.
+
+        The DOI dimensions were set to $2\lambda_b \times 2\lambda_b$, and all reconstructions were performed using a $40 \times 40$ pixel discretization.
 
@@
 
-            In all instances, the dimensions of the DoI were set to $2\lambda_b\times2\lambda_b$, and the measurement points' distance radius $R_O$ was fixed at $4\lambda_b$.
-
 			\subsubsection{Single scatterer}\label{sec:results:shape:star}
@@
 The contrast was set to 0.25, and the radius from the center of the scatterer to the farthest vertices was set to 0.9$\lambda_b$.
-A total of 80 measurement points ($N_M$) and 80 incidence angles ($N_S$) were used.
 Under these conditions, the Degree of Nonlinearity (DNL) for the test is 0.12, which is significantly lower than the threshold beyond which the Born Approximation becomes inapplicable, i.e., 1 \cite{bucci2001degree}.
-The scattered field was synthesized using a discretization of 120$\times$120 pixels for the original image, and all reconstructions were performed using a discretization of 40$\times$40 pixels.
+The scattered field was synthesized using a discretization of 120$\times$120 pixels for the original image.
 
@@
                     \renewcommand{\arraystretch}{1.5}
-                    \caption{Results for the single scatterer case study.}
+                    \caption{Shape recovering study, single scatterer: shape error indicator $\zeta_S$ for each algorithm.}
                     \label{tab:star}
@@
 While the method parameters could be optimized for each contrast value, they were kept constant across all contrast values to demonstrate the indicator's applicability in a controlled manner.
-
-                {\color{red} EU PRECISO RODAR NOVAMENTE O EXPERIMENTO PORQUE O NÚMERO DE MEDIÇÕES E FONTES NÃO FORAM IGUAIS NA PRIMEIRA VEZ.}
 
@@
             An exception would be algorithms that solve the imaging problem as an optimization problem, where the decision variables are the position, vertices (or other characteristics of a predefined geometry), and contrast of the scatterers \cite{michalski2000electromagnetic,salucci2022learned,zardi2025physics}.
-Additionally, in scenarios involving strong scatterers, traditional methods generally struggle to recover scatterer geometry effectively due to the increased problem hardness.
+Additionally, in scenarios involving strong scatterers with small size compared to the wavelength, traditional methods generally struggle to recover scatterer geometry effectively due to the increased problem hardness.
 In such scenarios, studying position detection becomes more relevant.
@@
 
-            Considering this, the experiments in this section were designed for scenarios involving strong scatterers, where traditional methods cannot adequately recover scatterer geometry.
+            Considering this, the experiments in this section were designed for scenarios involving strong scatterers with small size, where traditional methods cannot adequately recover scatterer geometry.
 Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.
+In addition, the DOI discretization for data synthesis was performed using a finer grid with $160 \times 160$ pixels.
+
+            Considering this, the experiments in this section were designed for scenarios involving strong scatterers with small dimensions, where traditional methods cannot adequately recover scatterer geometry.
+Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.
+
+            For all subsequent experiments, LSM was removed and an other method was introduced.
+Since the analytical solution for scattering from an infinite dielectric cylinder is well-established \cite{harrington2001time}, it becomes possible to determine the optimal circular approximation (defined by radius, position, and contrast) that best fits the scattered field of any single scatterer.
+
+            To optimize these four parameters, we employ a two-stage approach \cite{virtanen2020SciPy}:
+            \begin{enumerate}
+                \item Global optimization: The Differential Evolution (DE) algorithm \cite{storn1997differential} with 50 generations, 15 individuals, crossover rate of 0.7, and mutation factor ranging from 0.5 to 1.
+                \item Local refinement: The L-BFGS-B algorithm \cite{zhu1997algorithm} for improved accuracy.
+            \end{enumerate}
+
+            While DE is inherently stochastic and would typically require multiple executions for robust analysis, the problem structure and subsequent refinement step allow for single execution per instance based on previous experimental validation.
+This methodology is referred to as Circle Approximation (CA) throughout this work.
+
+            It should be noted that \cite{michalski2000electromagnetic} employed a similar DE-based approach for circular fitting, though their work focused specifically on perfect electric conductor cylinders under cylindrical scatterer assumptions.
 
@@
 
+                The first scenario for studying the position indicator utilized a star-shaped scatterer, similar to the experiments described in Sections \ref{sec:results:shape:star} and \ref{sec:results:shape:varying}.
+However, this configuration featured the scatterer positioned in the upper-right corner and rotated by 30 degrees, as illustrated in Fig.
+\ref{fig:position:single:ground_truth}.
+The scatterer contrast was set to 7, while the radius from the center to the farthest vertices was reduced to 0.15$\lambda_b$.
+Under these configurations, the DNL for this experiment reaches 1.7, which is slightly above the threshold of 1.
+
+                % A Fig.
+\ref{fig:position:single:recons} mostra as imagens reconstruídas por cada algoritmo.
+Conforme esperado, uma vez que o contraste é alto e o tamanho do espalhador é pequeno, os métodos vão reconstruir pequenos borrões na região no espalhador.
+A maneira como esses borrões são reconstruídos é importante, visto que essa informação impacta na medição da posição do espalhador.
+Tendo isto em vista, o CSI foi quem teve a maior dificuldade na reconstrução, uma vez o contraste se concentrou em uma região muito pequena e que o nível de contraste foi bem baixo se comparado aos demais métodos quantitativos.
+Nota-se também que o CA foi quei mais se aproximou do contraste do espalhador.
+
+                Fig.
+\ref{fig:position:single:recons} shows the images reconstructed by each algorithm.
+As expected, given the high contrast and small scatterer size, the methods reconstruct small blobs in the scatterer region.
+The way these blobs are reconstructed is relevant, as this information directly impacts the measurement of scatterer position.
+
+                In this regard, CSI experienced the greatest reconstruction difficulty, with contrast concentrated in a very small region and significantly lower contrast levels compared to the other quantitative methods.
+It is also notable that CA most closely approximated the actual scatterer contrast.
+
+                \begin{figure*}[!htb]
+                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/0.eps}\label{fig:position:single:ground_truth}}
+                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/1.eps}}
+                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/2.eps}} \\
+                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/3.eps}}
+                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/4.eps}}
+                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/5.eps}}
+                    \caption{Position detection study, single scatterer: ground-truth and reconstructed images by each algorithm.}
+                    \label{fig:position:single:recons}
+                \end{figure*}
+
+                Table \ref{tab:position:single:zeta_p} summarizes the results of the position error indicator for each algorithm.
+The results indicate that OSM, BIM, and CA achieved the best performance, while SOM performed similarly.
+The largest error was observed for CSI, which, due to its greater difficulty in quantifying the object's contrast, had more difficulty in capturing the object's position.
+Generally, the position detection errors for most algorithms were low.
+However, there may be applications where precision in position detection is critical, such as in tumor detection, for example.
+
+                \begin{table}[!htb]
+                    \centering
+                    \renewcommand{\arraystretch}{1.5}
+                    \caption{Position detection study, single scatterer: position error indicator $\zeta_P$ for each algorithm.}
+                    \label{tab:position:single:zeta_p}
+                    \begin{tabular}{cccccc}
+                        Method & OSM & BIM & CSI & SOM & CA \\\hline
+                        $\zeta_P$ (\%) & 0.08 & 0.04 & 4.68 & 0.53 & 0.04 \\
+                    \end{tabular}   
+                \end{table}
+
 			\subsubsection{Multiple scatterers}\label{sec:results:position:multiple}
+
+                % Embora o indicador proposto para mensurar o erro na posição tenha sido pensado para cenários com um único espalhador, ele também pode ser aplicado em cenários com múltiplos espalhadores.
+Nestes casos, o centróide do arranjo como um todo é o ponto de referência para a medição do erro na posição.
+Este tipo de investigação pode ser útil para aplicações como through-wall imaging, por exemplo.
+
+                Although the proposed indicator for measuring position error was designed for scenarios with a single scatterer, it can also be applied in scenarios with multiple scatterers.
+In these cases, the centroid of the arrangement as a whole serves as the reference point for measuring position error.
+This type of investigation can be useful for applications such as through-wall imaging, for example.
+
+                Baseado nisto, neste experimento são considerados três espalhadores: a estrela
+
+                % Based on this approach, this experiment considers three scatterers: the star-shaped object from the previous study, a circular scatterer, and a square scatterer.
+All objects have a contrast of 7 and are positioned at different locations within the DOI to create a challenging multi-target scenario.
+The goal is to evaluate how well each algorithm can detect the overall position of the scatterer arrangement when individual object geometries cannot be accurately recovered.
+
+                % Fig.
+\ref{fig:position:multiple:recons} shows the reconstructions obtained by each algorithm for the multiple scatterer scenario.
+As expected in this high-contrast, small-size configuration, the algorithms reconstruct blob-like structures rather than distinct object geometries.
+The quality and positioning of these reconstructed features directly influence the centroid calculation and, consequently, the position error measurement.
+
+                % Table \ref{tab:position:multiple:zeta_p} presents the position error results for each algorithm.
+Interestingly, CSI achieved the best performance in this multi-scatterer scenario, despite its poor performance in the single scatterer case.
+This suggests that the algorithm's behavior may be different when dealing with multiple targets.
+BIM and SOM showed similar intermediate performance, while OSM and CA exhibited higher position errors, indicating greater difficulty in accurately localizing the overall scatterer arrangement.
+
+                \begin{figure*}[!htb]
+                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/0.eps}\label{fig:position:multiple:ground_truth}}
+                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/1.eps}}
+                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/2.eps}} \\
+                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/3.eps}}
+                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/4.eps}}
+                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/5.eps}}
+                    \caption{Position detection study, multiple scatterer: ground-truth and reconstructed images by each algorithm.}
+                    \label{fig:position:multiple:recons}
+                \end{figure*}
+
+                \begin{table}[!htb]
+                    \centering
+                    \renewcommand{\arraystretch}{1.5}
+                    \caption{Position detection study, multiple scatterers: position error indicator $\zeta_P$ for each algorithm.}
+                    \label{tab:position:multiple:zeta_p}
+                    \begin{tabular}{cccccc}
+                        Method & OSM & BIM & CSI & SOM & CA \\\hline
+                        $\zeta_P$ (\%) & 10.24 & 8.30 & 4.86 & 8.27 & 12.85 \\
+                    \end{tabular}   
+                \end{table}
 

### 2025-07-22 eispy2d/library/casestudy.py

@@ -526,9 +526,9 @@ class CaseStudy(exp.Experiment):
                                                  vmax=vmax)
                         ifig += 1
                 elif not self.s_save:
-                    figure_title += ' - ' + self.method[m].output + ' case'
+                    # figure_title += ' - ' + self.method[m].output + ' case'
                     if image == BOTH_PROPERTIES:
-                        self.results[m].plot_map(image=rst.BOTH_PROPERTIES,
+                        self.results[m][0].plot_map(image=rst.BOTH_PROPERTIES,
                                                  axis=ax[ifig:ifig+2],
                                                  title=figure_title,
                                                  fontsize=fontsize,

### 2025-07-22 experiments/position/multiple/genfigures.py

@@ -1,0 +1,51 @@
+from matplotlib import pyplot as plt
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+import casestudy as cst
+import result as rst
+
+# Configuration
+plt.rcParams['image.cmap'] = 'Greys'
+plt.rcParams['font.family'] = 'serif'
+plt.rcParams['font.serif'] = 'Times New Roman'
+
+def save_figure(filepath, filename, tight_layout=True):
+    """Save figure with consistent settings."""
+    if tight_layout:
+        plt.tight_layout()
+    plt.savefig(f'{filepath}{filename}.eps', format='eps', bbox_inches='tight')
+    plt.close()
+
+def configure_axes(axis, hide_x_labels=True, hide_y_labels=True):
+    """Configure axis labels consistently."""
+    if hide_x_labels:
+        axis[0].set_xticklabels([])
+    if hide_y_labels:
+        axis[0].set_yticklabels([])
+
+# Initialize case study
+mycase = cst.CaseStudy(import_filename='multiple.cst', 
+                       import_filepath='../../../data/position/multiple/')
+filepath = './figs/'
+
+# Generate ground truth figure
+fig, axis, _ = rst.get_figure(1)
+mycase.test.draw(fontsize=20, axis=axis, title=False)
+axis[0].set_xticks([-1, 0, 1])
+configure_axes(axis, hide_y_labels=False)
+save_figure(filepath, '0')
+
+# Methods to generate reconstructions
+methods = [
+    ('osm', '1', True, True),
+    ('bim', '2', True, True), 
+    ('csi', '3', False, False),  # Keep original labels for CSI
+    ('som', '4', False, True),
+    ('ca', '5', False, True)
+]
+
+# Generate reconstruction figures
+for method, filename, hide_x, hide_y in methods:
+    axis = mycase.reconstruction(fontsize=20, method=method, title=False)
+    configure_axes(axis, hide_x, hide_y)
+    save_figure(filepath, filename)

### 2025-07-22 experiments/position/single/genfigures.py

@@ -1,0 +1,51 @@
+from matplotlib import pyplot as plt
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+import casestudy as cst
+import result as rst
+
+# Configuration
+plt.rcParams['image.cmap'] = 'Greys'
+plt.rcParams['font.family'] = 'serif'
+plt.rcParams['font.serif'] = 'Times New Roman'
+
+def save_figure(filepath, filename, tight_layout=True):
+    """Save figure with consistent settings."""
+    if tight_layout:
+        plt.tight_layout()
+    plt.savefig(f'{filepath}{filename}.eps', format='eps', bbox_inches='tight')
+    plt.close()
+
+def configure_axes(axis, hide_x_labels=True, hide_y_labels=True):
+    """Configure axis labels consistently."""
+    if hide_x_labels:
+        axis[0].set_xticklabels([])
+    if hide_y_labels:
+        axis[0].set_yticklabels([])
+
+# Initialize case study
+mycase = cst.CaseStudy(import_filename='single.cst', 
+                       import_filepath='../../../data/position/single/')
+filepath = './figs/'
+
+# Generate ground truth figure
+fig, axis, _ = rst.get_figure(1)
+mycase.test.draw(fontsize=20, axis=axis, title=False)
+axis[0].set_xticks([-1, 0, 1])
+configure_axes(axis, hide_y_labels=False)
+save_figure(filepath, '0')
+
+# Methods to generate reconstructions
+methods = [
+    ('osm', '1', True, True),
+    ('bim', '2', True, True), 
+    ('csi', '3', False, False),  # Keep original labels for CSI
+    ('som', '4', False, True),
+    ('ca', '5', False, True)
+]
+
+# Generate reconstruction figures
+for method, filename, hide_x, hide_y in methods:
+    axis = mycase.reconstruction(fontsize=20, method=method, title=False)
+    configure_axes(axis, hide_x, hide_y)
+    save_figure(filepath, filename)

### 2025-07-22 experiments/position/average/gendata.py
Fixe in experiment scripts

@@ -37,7 +37,7 @@ testset = tst.TestSet(name=name + '.tst', configuration=config,
                       sample_size=sample_size, noise=noise,
                       indicators=indicators)
 
-testset.randomize_tests(parallelization=True, compute_dnl=True)
+testset.randomize_tests(parallelization=False, compute_dnl=True)
 
 testset.generate_field_data(solver=mom.MoM_CG_FFT(tolerance=1e-3,
                                                   maximum_iterations=10_000))

### 2025-07-22 experiments/position/multiple/gendata.py

@@ -21,7 +21,7 @@ resolution = (160, 160)
 noise = 5.
 indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
 epsilon_rd = [5., 4., 3.5]
-l = 0.15
+l = 0.1
 position = [.4, -.4]
 rotate = 30
 

### 2025-07-23 paper/main.tex
More text written

@@
 
-                Baseado nisto, neste experimento são considerados três espalhadores: a estrela
+                Based on this approach, this experiment considers three scatterers: the star from the previous experiment, a square, and a cross.
+The contrasts of the three scatterers were set to 4, 3.5, and 2.5, respectively.
+These values were chosen to be lower than in the previous experiment, since the presence of multiple scatterers inherently increases problem hardness due to mutual current induction between the scatterers.
 
-                % Based on this approach, this experiment considers three scatterers: the star-shaped object from the previous study, a circular scatterer, and a square scatterer.
-All objects have a contrast of 7 and are positioned at different locations within the DOI to create a challenging multi-target scenario.
-The goal is to evaluate how well each algorithm can detect the overall position of the scatterer arrangement when individual object geometries cannot be accurately recovered.
+                The square has a side length of 0.15$\lambda_b$, while the cross has dimensions of 0.3$\lambda_b$ × 0.3$\lambda_b$ with a thickness of 0.15$\lambda_b$.
+The scatterers were positioned such that their collective arrangement is located in the upper corner of the DOI, as illustrated in Fig.
+\ref{fig:position:multiple:ground_truth}.
+Under this configuration, the DNL for this experiment is 0.3.
 
-                % Fig.
-\ref{fig:position:multiple:recons} shows the reconstructions obtained by each algorithm for the multiple scatterer scenario.
-As expected in this high-contrast, small-size configuration, the algorithms reconstruct blob-like structures rather than distinct object geometries.
-The quality and positioning of these reconstructed features directly influence the centroid calculation and, consequently, the position error measurement.
-
-                % Table \ref{tab:position:multiple:zeta_p} presents the position error results for each algorithm.
-Interestingly, CSI achieved the best performance in this multi-scatterer scenario, despite its poor performance in the single scatterer case.
-This suggests that the algorithm's behavior may be different when dealing with multiple targets.
-BIM and SOM showed similar intermediate performance, while OSM and CA exhibited higher position errors, indicating greater difficulty in accurately localizing the overall scatterer arrangement.
+                Fig.
+\ref{fig:position:multiple:recons} presents the reconstructions obtained by each algorithm for the multiple scatterer scenario.
+As expected in this small-size configuration, the algorithms produce blob-like structures that are generally larger than the actual object geometries.
+The CA method positioned its circular approximation close to the square's location.
+Although the quantitative methods could not accurately estimate the individual scatterer contrasts, they consistently assigned higher contrast values to the square region rather than the star region.
+This behavior suggests that the square's larger cross-sectional area compared to the star may have influenced the algorithms' reconstruction process.
 
@@
                 \end{figure*}
+
+                Table \ref{tab:position:multiple:zeta_p} presents the position error results for each algorithm.
+Interestingly, CSI achieved the best performance in this multi-scatterer scenario, despite its poor performance in the single scatterer case.
+This suggests that the algorithm's behavior may be different when dealing with multiple targets.
+BIM and SOM showed similar intermediate performance, while OSM and CA exhibited higher position errors, indicating greater difficulty in accurately localizing the overall scatterer arrangement.
 
@@
 			\subsubsection{Average performance}\label{sec:results:position:benchmark}
+
+                Similar to the shape recovery study, an average performance analysis was conducted to compare the position detection capabilities of OSM, BIM, CSI, SOM, and CA algorithms.
+This experiment employed 30 scatterer instances with configurations similar to those described in Section \ref{sec:results:position:single}.
+The scatterer contrast was fixed at 7, and the radius from the center to the farthest vertices was set to 0.15$\lambda_b$.
+Following the approach from Section \ref{sec:results:shape:average}, the scatterers were randomly generated as polygons with 4 to 15 vertices.
+
+                The DNL distribution is shown in Fig.
+\ref{fig:position:average:dnl}.
+The values range from below 1 to above 4, with a median close to 2.
+The high contrast level and geometric variations contributed to the wide distribution of DNL values.
+However, as shown in Fig.
+\ref{fig:position:average:zeta_s}, the algorithm performance within each instance remained within a similar range.
+CSI clearly exhibited the worst performance, followed by SOM.
+The best performance in each instance varied between OSM and CA.
+These results are consistent with the findings from Section \ref{sec:results:position:single}.
+
+                \begin{figure}[!htb]
+                    \centering
+                    \subfigure[]{\includegraphics[width=.5\columnwidth]{./experiments/position/average/figs/dnl.eps}\label{fig:position:average:dnl}} \\
+                    \subfigure[]{\includegraphics[width=\columnwidth]{./experiments/position/average/figs/plot.eps}\label{fig:position:average:zeta_s}}
+                    \caption{Position detection study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) position error indicator $\zeta_P$ for each algorithm in each instance.}
+                    \label{fig:position:average}   
+                \end{figure}
+
+                \begin{table*}
+                    \centering
+                    \renewcommand{\arraystretch}{1.5}
+                    \caption{Position detection study, average performance: $p$-values for the paired T-Test with Bonferroni correction.}
+                    \label{tab:position:average:pvalue}
+                    \begin{tabular}{ccccccc}
+                        Pairs & OSM-BIM & OSM-SOM & OSM-CA & BIM-SOM & BIM-CA & SOM-CA \\\hline
+                        $p$-value & $<10^{-9}$ & $<10^{-13}$ & 0.95 & $<10^{-6}$ & $<10^{-10}$ & $<10^{-17}$ \\  
+                    \end{tabular}
+                \end{table*}
+
+                \begin{figure}
+                    \centering
+                    \includegraphics[width=.8\columnwidth]{./experiments/position/average/figs/confidence_intervals.eps}
+                    \caption{Position detection study, average performance: Confidence intervals (95\%) for the position error indicator $\zeta_P$ for each pair of algorithms.}
+                    \label{fig:position:average:confidence_intervals}
+                \end{figure}
 

### 2025-07-23 experiments/position/average/genfigures.py

@@ -1,0 +1,175 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+import benchmark as bmk
+import result as rst
+import numpy as np
+import matplotlib.pyplot as plt
+
+# Configuration constants
+FIGURE_SIZE = (12, 8)
+BOXPLOT_SIZE = (5, 6)
+CI_PLOT_SIZE = (10, 6)
+FONT_FAMILY = 'Times New Roman'
+FONT_SIZES = {'labels': 30, 'legend': 20, 'ticks': 25, 'boxplot': 25}
+LINE_STYLE = {'markersize': 11, 'linewidth': 3}
+OUTPUT_CONFIG = {'dpi': 300, 'bbox_inches': 'tight', 'format': 'eps'}
+
+# Visual styling arrays
+MARKERS = ['o', 's', '^', 'D', 'v', '<', '>', 'p', '*', 'h']
+LINE_STYLES = ['-', '--', '-.', ':', '-']
+GRAY_COLORS = ['0.7', '0.6', '0.4', '0.2', '0.0']  # light to dark gray
+
+# Algorithm names for legend
+ALGORITHM_NAMES = ['OSM', 'BIM', 'CSI', 'SOM', 'CA']
+
+def setup_matplotlib_defaults():
+    """Set global matplotlib configuration."""
+    plt.rcParams['font.family'] = FONT_FAMILY
+
+def setup_line_styles(axis):
+    """Apply visual styling to all lines in the plot."""
+    for i, line in enumerate(axis.lines):
+        line.set_color(GRAY_COLORS[i % len(GRAY_COLORS)])
+        line.set_marker(MARKERS[i % len(MARKERS)])
+        line.set_linestyle(LINE_STYLES[i % len(LINE_STYLES)])
+        line.set_markersize(LINE_STYLE['markersize'])
+        line.set_linewidth(LINE_STYLE['linewidth'])
+
+def setup_font_styling(axis):
+    """Apply font styling to axis labels and ticks."""
+    axis.set_xlabel(axis.get_xlabel(), fontfamily=FONT_FAMILY, 
+                    fontsize=FONT_SIZES['labels'])
+    axis.set_ylabel(axis.get_ylabel(), fontfamily=FONT_FAMILY, 
+                    fontsize=FONT_SIZES['labels'])
+    axis.tick_params(labelsize=FONT_SIZES['ticks'])
+    
+    # Set font family for tick labels
[…]

### 2025-07-24 paper/main.tex
Introduction written

@@
 
-        \IEEEPARstart{H}{ere} we go.
+        % O Imageamento em Microondas é uma importante técnica para a detecção e caracterização de objetos em meios inacessíveis \cite{pastorino2010microwave}.
+Essa técnica de baixo custo utiliza ondas eletromagnéticas de baixa potência para obter informações sobre a estrutura interna de materiais de maneira não invasiva \cite{godinho2025evaluation}.
+As aplicações deste método são diversas, incluindo diagnósticos médicos \cite{mojabi2025microwave}, inspeção de estruturas \cite{fedeli2025mild}, through-wall imaging \cite{fedeli2020through}, sensoreamento remoto \cite{salucci2017multifrequency}, entre outros.
 
-        % O que é Microwave Imaging.
+        \IEEEPARstart{M}{icrowave} Imaging is an important technique for the detection and characterization of objects in inaccessible media \cite{pastorino2010microwave}.
+This low-cost technique uses low-power electromagnetic waves to obtain information about the internal structure of materials in a non-invasive manner \cite{godinho2025evaluation}.
+The applications of this method are diverse, including medical diagnostics \cite{mojabi2025microwave}, structural inspection \cite{fedeli2025mild}, through-wall imaging \cite{fedeli2020through}, remote sensing \cite{salucci2017multifrequency}, among others.
 
-        % O papel dos algoritmos de inversão dentro de MWI para resolver o problema de espalhamento eletromagnético e quais desafios (ill-posedness etc). Destacar também a formulação 2D.
+        % Esta técnica é baseada na solução do problema inverso de espalhamento eletromagnético \cite{chen2018computational}.
+Ou seja, a partir das medições do campo eletromagnético fora do domínio de interesse, busca-se recuperar as propriedades do meio interno.
+Este problema é conhecido por ser mal posto, o que significa que pequenas variações nas medições podem levar a grandes variações na solução \cite{colton2019inverse}.
+Além disso, ele também é não-linear e não-convexo devido aos efeitos de espalhamento múltiplo \cite{chen2018computational}.
+
+        This technique is based on solving the inverse electromagnetic scattering problem \cite{chen2018computational}.
+Specifically, electromagnetic field measurements collected outside the Domain of Interest (DOI) are used to recover the properties of the internal medium.
+This problem is inherently ill-posed, meaning that small variations in measurements can lead to large variations in the solution \cite{colton2019inverse}.
+Furthermore, the problem is both nonlinear and non-convex due to multiple scattering effects \cite{chen2018computational}.
+The problem can be formulated in either two or three dimensions, with two-dimensional formulations being more commonly used for algorithm development due to their computational simplicity and efficiency.
 
@@
 
+        % Existe uma ampla gama de algoritmos para resolver o problema inverso de espalhamento eletromagnético.
+Estes algoritmos podem ser classificados em duas categorias principais: métodos qualitativos \cite{pastorino2010ch5}, que reconstroem a imagem sem estimar as propriedades elétricas do meio, e métodos quantitativos \cite{pastorino2010ch7}, os quais estimam essas propriedades.
+Entre os métodos qualitativos podemos destacar o Linear Sampling Method (LSM) \cite{chen2017lsm}, o Orthogonality Sampling Method (OSM) \cite{harris2020orthogonality}, entre outros.
+Entre os métodos quantitativos, podemos destacar o Born Iterative Method (BIM) \cite{wang1989iterative}, o Contrast Source Inversion (CSI) \cite{berg1997contrast}, o Distorted Born Inversion Method (DBIM) \cite{chew1990reconstruction}, o Subspace Optimization Method (SOM) \cite{chen2010subspace}, entre outros.
+Vale à pena destacar também que há algoritmos que contemplam certas especificidades do problema: como o método DORT \cite{chen2018computational} que aborda a reversão temporal dos sinais eletromagnéticos, o MUSIC \cite{zhong2007music}, o qual é adequado para pequenos espalhadores, o Compressive Sensing \cite{massa2015compressive}, o qual pode ser aplicado quando os dados de campo não tem fase, a Aproximação de Born de Primeira Ordem, o Backpropagation e a aproximação de Rytov \cite{chen2018computational}, os quais são úteis para problemas com espalhadores fracos.
+Outras abordagens relevantes são os Experimentos Virtuais \cite{isernia2024some,bevacqua2021simple}, os quais recombinam os dados do campo espalhado para explorar condições que aliviam a não-linearidade, e a reescrita eficiente das equações \cite{isernia2024some,bevacqua2021effective}, as quais tem o mesmo objetivo final de aliviar a não linearidade.
+Vale à pena destacar inclusive que, recentemente, algoritmos que fazem o uso de aprendizado de máquina tem sido propostos \cite{chen2020review}.
+Dentre as abordagens existentes, os métodos orientados a dados (data-driven), como o Direct Inversion Scheme \cite{yao2020enhanced,wei2019solving}, permitem a inferência direta dos parâmetros físicos de um espalhador a partir dos campos medidos, minimizando a necessidade de pré-processamento.
+Contudo, alguns métodos frequentemente demandam vastos conjuntos de dados para treinamento e apresentam notórias limitações em termos de generalização, confiabilidade e interpretabilidade.
+Para mitigar essas deficiências, foram propostos os métodos orientados à física (physics-driven), que incorporam leis e informações físicas para guiar o processo de reconstrução \cite{wei2019physics,wang2023push,hu2023more,liu2025exploring}.
+Outra abordagem é a construção de modelos substitutos para recuperação da posição, geometria e contraste dos espalhadores a partir de um problema de otimização \cite{salucci2022learned,zardi2025physics}.
+Apesar de superarem algumas das falhas das abordagens puramente baseadas em dados, sua eficácia pode estar condicionada a parâmetros do sistema, como a função de Green, cuja obtenção em meios complexos ou inomogêneos representa um desafio significativo.
+
+        A wide range of algorithms exists for solving the inverse electromagnetic scattering problem.
+These algorithms can be broadly classified into two main categories: qualitative methods \cite{pastorino2010ch5}, which reconstruct images without estimating the electrical properties of the medium, and quantitative methods \cite{pastorino2010ch7}, which estimate these properties.
+
+        Among qualitative methods, notable examples include the Linear Sampling Method (LSM) \cite{chen2017lsm} and the Orthogonality Sampling Method (OSM) \cite{harris2020orthogonality}.
+Among quantitative methods, prominent approaches include the Born Iterative Method (BIM) \cite{wang1989iterative}, Contrast Source Inversion (CSI) \cite{berg1997contrast}, the Distorted Born Inversion Method (DBIM) \cite{chew1990reconstruction}, and the Subspace Optimization Method (SOM) \cite{chen2010subspace}.
+
+        Specialized algorithms have been developed to address specific problem characteristics.
+These include the DORT method \cite{chen2018computational} for electromagnetic signal time reversal, MUSIC \cite{zhong2007music} for small scatterers, and Compressive Sensing \cite{massa2015compressive} for phaseless field data.
+For weak scatterer problems, effective approaches include First-Order Born Approximation, Backpropagation, and Rytov approximation \cite{chen2018computational}.
+
+        Additional relevant techniques include Virtual Experiments \cite{isernia2024some,bevacqua2021simple}, which recombine scattered field data to explore conditions that alleviate nonlinearity, and efficient equation reformulations \cite{isernia2024some,bevacqua2021effective} that share the same objective of reducing nonlinearity.
+
+        Recently, machine learning-based algorithms have emerged as promising solutions \cite{chen2020review}.
+Among these approaches, data-driven methods such as the Direct Inversion Scheme \cite{yao2020enhanced,wei2019solving} enable direct inference of scatterer physical parameters from measured fields, minimizing preprocessing requirements.
+However, these methods often demand extensive training datasets and exhibit significant limitations in generalization, reliability, and interpretability.
+
+        To address these deficiencies, physics-driven methods have been proposed that incorporate physical laws and information to guide the reconstruction process \cite{wei2019physics,wang2023push,hu2023more,liu2025exploring}.
+Another approach involves constructing surrogate models for recovering scatterer position, geometry, and contrast through optimization problems \cite{salucci2022learned,zardi2025physics}.
+Despite overcoming some limitations of purely data-driven approaches, their effectiveness may depend on system parameters such as the Green's function, whose determination in complex or inhomogeneous media represents a significant challenge.
+
         % Quais formas de avaliar soluções e quais ferramentas já existem (incluir aquele trabalho do Kurrant que é software para câncer de mama).
+
+        % Em grande parte destes trabalhos, os algoritmos propostos são testados e avaliados em métricas como o mean square error (MSE) da estimativa do contraste pixel a pixel ou algo similar \cite{yin2023subspace,zhang2022023,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}.
+Este tipo de abordagem leva em consideração a precisão na estimativa do contraste na forma direta e, indiretamente, pode dar uma perspectiva de quão boa a reconstrução da posição e geometria dos objetos pode ser, uma vez que erros na geometria e posicionamento podem afetar nessa métrica.
+No entanto, uma geometria bem precisa com uma má estimativa do contraste pode resultar em um erro considerável neste tipo de métrica, por exemplo.
+Logo, aspectos comparar o desempenho no aspecto de quão bem a geometria e a posição dos objetos são recuperadas não são contemplados adequadamente por este tipo de métrica.
+Além disso, a métrica MSE não é adequada para avaliar algoritmos qualitativos, uma vez que estes não estimam o contraste do meio.
+Vale à pena destacar também a métrica Structural Similarity (SSIM) \cite{wang2004image} to quantitatively show the reconstruction visual quality, which is designed to compute the mismatch between reconstructed contrast results and corresponding GTs both on the pixel-wise level and perceptual level.
+Ao invés de fazer uma comparação pixel a pixel, a métrica leva em consideração aspectos de luminância, contraste e estrutura de uma imagem qualquer.
+Portanto, ao mesmo tempo que fornece uma quantificação mais profunda da qualidade de construção como um todo, ela não vai mensurar diretamente aspectos isolados como geometria e posição.
+
+        In most of these studies, the proposed algorithms are tested and evaluated using metrics such as the mean square error (MSE) of pixel-by-pixel contrast estimation or similar approaches \cite{yin2023subspace,zhang2023iterative,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}.
+This type of approach directly considers the precision of contrast estimation and can indirectly provide perspective on how well the reconstruction of object position and geometry might be, since errors in geometry and positioning can affect this metric.
+However, a highly accurate geometry with poor contrast estimation can result in considerable error in this type of metric, for example.
+Therefore, aspects of comparing performance regarding how well object geometry and position are recovered are not adequately addressed by this type of metric.
+Furthermore, the MSE metric is not suitable for evaluating qualitative algorithms, since these do not estimate the medium's contrast.
+
+        It is also worth highlighting the Structural Similarity (SSIM) metric \cite{wang2004image} to quantitatively show the reconstruction visual quality, which is designed to compute the mismatch between reconstructed contrast results and corresponding ground truths both on the pixel-wise level and perceptual level \cite{wang2023push,liu2025exploring}.
+Instead of performing a pixel-by-pixel comparison, this metric considers aspects of luminance, contrast, and structure of any given image.
+Therefore, while it provides a deeper quantification of overall reconstruction quality, it does not directly measure isolated aspects such as geometry and position.
+
+        Specifically for breast imaging, a set of metrics has been proposed in the literature that considers not only the precision in estimating electrical properties, but also the accuracy of the reconstructed tissue geometry \cite{kurrant2021evaluating}.
+Each geometry (original and reconstructed) is converted into vectors, and the metric is calculated using a formula that performs the dot product and norm of these vectors.
+To the best of the authors' knowledge, this is the only metric that can isolately consider the geometry aspect of the scatterer, even though it is designed specifically for breast imaging.
 
@@
 
+        % O objetivo deste trabalho é fornecer mais métricas para auxiliar na avaliação do desempenho de algoritmos.
+Com uma gama maior de indicadores pode ser possível ter uma visão mais abrangente sobre a capacidade dos algoritmos em diferentes cenários.
+Por isso, nossa contribuição se baseia na proposição de dois novos indicadores para avaliar o desempenho dos algoritmos na recuperação da geometria e posição dos espalhadores.
+O primeiro indicador quantifica o erro de forma, enquanto o segundo quantifica o erro de posição.
+A originalidade do trabalho reside no fato de que estes indicadores podem calcular de maneira mais isolada esses dois aspectos que são relevantes da descrição do desempenho de algoritmos para o problema inverso de espalhamento eletromagnético.
+Além disso, estes indicadores são projetados para serem aplicáveis a qualquer algoritmo que reconstrua a imagem, independentemente de estimar ou não o contraste.
+
+        The objective of this work is to provide additional metrics to assist in evaluating algorithm performance.
+With a broader range of indicators, it becomes possible to obtain a more comprehensive understanding of algorithm capabilities across different scenarios.
+Therefore, our contribution is based on proposing two novel indicators for evaluating algorithm performance in recovering scatterer geometry and position.
+The first indicator quantifies shape error, while the second quantifies position error.
+
+        The originality of this work lies in the fact that these indicators can measure these two relevant aspects of electromagnetic inverse scattering algorithm performance in a more isolated manner.
+Furthermore, these indicators are designed to be applicable to any algorithm that reconstructs images, regardless of whether it estimates contrast or not.
+
         % Organização do texto
+
+        The remainder of this paper is organized as follows.
+Section \ref{sec:problemstatement} presents the problem statement and the mathematical formulation of the electromagnetic inverse scattering problem.
+Section \ref{sec:indicators} introduces the proposed indicators for evaluating algorithm performance.
+Section \ref{sec:results} presents numerical results demonstrating the effectiveness of the proposed indicators.
+Finally, Section \ref{sec:conclusion} concludes the paper and discusses future work.
 
@@
 
-		Let $D \in \mathbb{R}^2$ denote the Domain of Interest (DOI) embedded within a homogeneous, isotropic, nonmagnetic ($\mu = \mu_0 = 4\pi \times 10^{-7}$ H/m), and lossless ($\sigma = \sigma_0 = 0$ S/m) background medium with permittivity $\epsilon_b = \epsilon_{rb}\epsilon_0$, where $\epsilon_0 \approx 8.85 \times 10^{-12}$ F/m.
+		Let $D \in \mathbb{R}^2$ denote the DOI embedded within a homogeneous, isotropic, nonmagnetic ($\mu = \mu_0 = 4\pi \times 10^{-7}$ H/m), and lossless ($\sigma = \sigma_0 = 0$ S/m) background medium with permittivity $\epsilon_b = \epsilon_{rb}\epsilon_0$, where $\epsilon_0 \approx 8.85 \times 10^{-12}$ F/m.
 We consider a 2D Transverse Magnetic (TMz) polarization where the DOI is illuminated by incident plane waves and assume the time convention $e^{j\omega t}$.
@@
 The case studies aim to assess performance in specific scenarios, while the benchmarking study facilitates broader generalization of the results.
+Additionally, an experiment considering a breast imaging scenario was conducted to illustrate the applicability of the proposed indicators in a realistic scenario.
 
@@
 
-        For all experiments, the following common parameters were used: background wavelength $\lambda_b = 1$ m, noise level of 5\%, relative permittivity of the background medium $\epsilon_{rb} = 1$, and incident wave amplitude of 1 V/m.
+        For all experiments in Section \ref{sec:results:shape} and \ref{sec:results:position}, the following common parameters were used: background wavelength $\lambda_b = 1$ m, noise level of 5\%, relative permittivity of the background medium $\epsilon_{rb} = 1$, and incident wave amplitude of 1 V/m.
 
@@
 The best performance in each instance varied between OSM and CA.
-These results are consistent with the findings from Section \ref{sec:results:position:single}.
+These results are coherent with the findings from Section \ref{sec:results:position:single}.
 
@@
                 \end{figure}
+
+                % Embora a Fig.
+\ref{fig:position:average:zeta_s} sugira claramente que há uma diferença no desempenho médio dos algoritmos, foi aplicado novamente o RCBD para fornecer evidências estatísticas para isso.
+O CSI foi removido desta análise, uma vez que seu desempenho foi significativamente pior que os demais algoritmos.
+Após validar o pressuposto de normalidade, o valor-p obtido pelo RCBD foi menor que $10^{-30}$.
+Nas comparações todos-contra-todos feitas através de múltiplos testes T pareados com correção de Bonferroni, o valor-p foi menor que $10^{-6}$ para todos os pares de algoritmos, a hipótese nula de igualdade de desempenho médio só não foi rejeitada para o par OSM-CA.
+Ou seja, não foram encontradas evidências estatísticas de que OSM e CA possuem desempenhos médios diferentes, sugerindo então que ambos os métodos possuem desempenhos equivalentes.
+Os valores-p obtidos pelos testes são apresentados na Tabela \ref{tab:position:average:pvalue}.
+
+                While Fig.
+\ref{fig:position:average:zeta_s} clearly suggests differences in average algorithm performance, RCBD was applied to provide statistical evidence.
+CSI was excluded from this analysis due to its significantly inferior performance compared to other algorithms.
+
+                After validating the normality assumption, the RCBD yielded a p-value less than $10^{-30}$, indicating significant differences among algorithms.
+Multiple paired T-tests with Bonferroni correction revealed p-values less than $10^{-6}$ for all algorithm pairs, except for the OSM-CA comparison.
+The null hypothesis of equal average performance was rejected for all pairs except OSM-CA, indicating that these two methods demonstrate statistically equivalent performance.
+The complete p-values are presented in Table \ref{tab:position:average:pvalue}.
 
@@
 
+                Fig.
+\ref{fig:position:average:confidence_intervals} shows the 95\% confidence intervals for the mean paired differences of the position error indicator $\zeta_P$ for each algorithm pair.
+The results demonstrate that OSM and CA achieve superior performance compared to BIM and SOM, while BIM outperforms SOM.
+However, the mean differences do not exceed 1\% in any case, indicating that although statistically significant differences exist, these differences would only be practically relevant in applications requiring high precision in position detection.
+
                 \begin{figure}
@@
         \subsection{Breast Phantom Study}\label{sec:results:breast}
+
+            Finally, a case study using a realistic breast phantom demonstrates the application of the proposed indicators in clinical scenarios.
+This phantom was obtained from the UWCEM Numerical Breast Phantom Repository \cite{burfeindt2012mri} and corresponds to the Very Dense type (ACR class 4).
+
+            Since the repository provides three-dimensional phantoms while our scattering model is two-dimensional, a representative cross-section focusing on the breast interior was extracted, as shown in Fig.
+\ref{fig:breast:phantom:ground_truth}.
+The resulting image contains 328 $\times$ 328 pixels with a spatial resolution of 0.5 mm $\times$ 0.5 mm per pixel.
+
+            The phantom includes four tissue types: fatty, transitional, fibroglandular, and skin.
+The breast is immersed in a homogeneous background medium with relative permittivity $\epsilon_{rb} = 10$ and conductivity $\sigma = 0$ S/m.
+The operating frequency was set to 1 GHz, with electrical properties of breast tissues determined using the Debye model.
+
+            The experimental configuration follows the previous studies: 80 incident sources, 80 measurement points, and 5\% noise level.
+Under these conditions, the DNL for this experiment is 0.05.
+Since the interior of the breast is a complex structure, keeping a low DNL value is an important strategy to facilitate the reconstruction.
 

### 2025-07-25 paper/main.tex
Conclusion written

@@
     \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
-        \thanks{This work has been supported by the Brazilian agencies Coordination for the Improvement of Higher Education Personnel - Brazil (CAPES) through the Academic Excellence Program (PROEX) under Grant 88887.815891/2023-00, FAPEMIG (Research Support Foundation of the State of Minas Gerais), and CNPq (The National Council for Scientific and Technological Development).}
+        \thanks{This work was supported in part by the Brazilian agency CAPES (Coordination for the Improvement of Higher Education Personnel) under Grant 88887.463864/2019-00, the scholarship FAPEMIG-CNPQ (process APQ-06716-24), and CNPq (The National Council for Scientific and Technological Development).}
+
         \thanks{A.
@@
 
-        The originality of this work lies in the fact that these indicators can measure these two relevant aspects of electromagnetic inverse scattering algorithm performance in a more isolated manner.
+        The originality of this work lies in the fact that these indicators can measure these two relevant aspects of electromagnetic inverse scattering algorithm performance in a more isolated manner than the existing metrics.
 Furthermore, these indicators are designed to be applicable to any algorithm that reconstructs images, regardless of whether it estimates contrast or not.
@@
             Finally, a case study using a realistic breast phantom demonstrates the application of the proposed indicators in clinical scenarios.
-This phantom was obtained from the UWCEM Numerical Breast Phantom Repository \cite{burfeindt2012mri} and corresponds to the Very Dense type (ACR class 4).
+This phantom was obtained from the UWCEM Numerical Breast Phantom Repository \cite{burfeindt2012mri} and corresponds to the Scattered Fibroglandular type (ACR class 2).
 
@@
 \ref{fig:breast:phantom:ground_truth}.
-The resulting image contains 328 $\times$ 328 pixels with a spatial resolution of 0.5 mm $\times$ 0.5 mm per pixel.
+The resulting image contains 328 $\times$ 212 pixels with a spatial resolution of 0.5 mm $\times$ 0.5 mm per pixel.
 
@@
 
+            The algorithm parameters were readjusted as follows:
+            \begin{itemize}
+                \item Linear Sampling Method (LSM):
+                \begin{itemize}
+                    \item Threshold: 0.7;
+                    \item Regularization Method: Conjugate Gradient with 300 iterations.
+                \end{itemize}
+                \item Orthogonality Sampling Method (OSM):
+                \begin{itemize}
+                    \item Threshold: 0.35;
+                \end{itemize}
+                \item Born Iterative Method (BIM):
+                \begin{itemize}
+                    \item Regularization Method: Conjugate Gradient with 300 iterations.
+                    \item Stopping Criterion: 30 iterations.
+                \end{itemize}
+                \item Contrast Source Inversion (CSI):
+                \begin{itemize}
+                    \item Stopping Criterion: 300 iterations.
+                \end{itemize}
+                \item Subspace Optimization Method (SOM):
+                \begin{itemize}
+                    \item Stopping Criterion: 30 iterations.
+                    \item Eigenvalue Cutoff Index: 5.
+                \end{itemize}
+            \end{itemize}
+
     \section{Conclusion}\label{sec:conclusion}
-        A conclusion section is not required.
-Although a conclusion may review the main points of the paper, do not replicate the abstract as the conclusion.
-A  conclusion might elaborate on the importance of the work or suggest applications and extensions.
-\cite{chen2018computational}
+
+        % Uma vez que muitos algoritmos já foram e continuam sendo propostos para o problema inverso de espalhamento eletromagnético e que é importante ter indicadores que sejam capazes de mensurar o desempenho desses algoritmos em diferentes aspectos, este trabalho se propôs a desenvolver dois novos indicadores que podem mensurar de maneira mais isolada dois aspectos que podem ser relevantes para o problema: a localização e a geometria dos espalhadores.
+Esses indicadores de erro de forma e de posição foram desenvolvidos usando ferramentas de limiarização e detecção de contornos de forma a reduzir o impacto da precisão da estimativa do contraste para possibilitar a mensuração desses aspectos de forma mais independente.
+Apesar do cálculo desses indicadores depender de uma escolha de nível de limiarização, eles permitem fazer comparações adequadas entre algoritmos qualitativos e quantitavivos, principalmente em cenários com um único espalhador.
+Portanto, a partir de uma padronização do conjunto de testes, esses indicadores podem ser uma ferramenta significativa para avaliação e comparação de desempenho de métodos propostos na literatura.
+
+        Since many algorithms have been and continue to be proposed for the electromagnetic inverse scattering problem, and it is important to have indicators capable of measuring algorithm performance across different aspects, this work aimed to develop two novel indicators that can measure two relevant problem aspects in a more isolated manner: scatterer localization and geometry.
+These shape and position error indicators were developed using thresholding and contour detection tools to reduce the impact of contrast estimation precision, enabling more independent measurement of these aspects.
+Although the calculation of these indicators depends on threshold level selection, they enable adequate comparisons between qualitative and quantitative algorithms, particularly in single scatterer scenarios.
+Therefore, through standardized test sets, these indicators can serve as significant tools for evaluating and comparing the performance of methods proposed in the literature.
+
+        % Vale à pena destacar também que, com base nos indicadores propostos, os experimentos computacionais realizados considerando um estudo de benchmarking foram capazes de fornecer conclusões na comparação de algoritmos para o problema.
+Os estudos mostraram que: (a) no cenário com um espalhador e baixo DNL, o BIM tem o melhor desempenho médio na recuperação da forma dos espalhadores em relação aos demais algoritmos considerados; (b) no cenário de pequenos espalhadores de alto contraste, o OSM e o CA têm o melhor desempenho médio na localização dos espalhadores.
+Outros estudos poderiam ser realizados para elaborar com mais profundidade as diferenças de desempenho entre os algoritmos, o qual não foi o objetivo principal deste trabalho.
+
+        It is also worth highlighting that, based on the proposed indicators, the computational experiments conducted through benchmarking studies were able to provide stronger conclusions about the performance of traditional algorithms in the literature when they are compared.
+The studies demonstrated that: (a) in scenarios with a single scatterer and low DNL, BIM achieves the best average performance in scatterer shape recovery compared to other considered algorithms; (b) in scenarios involving small, high-contrast scatterers, OSM and CA achieve the best average performance in scatterer localization.
+Additional studies could be conducted to explore algorithm performance differences more thoroughly, though this was not the primary objective of this work.
+
+        % Novas investigações podem ser realizadas para aprimorar os indicadores propostos.
+Uma possibilidade seria se a geometria dos espalhadores puder ser comparada através dos vértices dos objetos de tal forma que a detecção de objetos correspondentes (no caso de múltiplos espalhadores) nas imagens reais e reconstruídas possa ser feita de forma robusta e a diferença na quantidade de pontos do contorno não for um problema.
+Isso poderia possibilitar que, por exemplo, fosse criado um indicador para mensurar a qualidade da geometria sem levar em consideração a precisão no reconstrução do tamanho do espalhador.
+Outro caminho possível seria criar diferentes conjuntos de testes que explorem diferentes cenários do problema a fim de serem padrões para comparação de algoritmos.
+Por fim, a adaptação dos indicadores para problemas tridimensionais também é um caminho possível para futuras investigações.
+
+        Future investigations may be undertaken to enhance the proposed indicators.
+One possibility would be to compare scatterer geometries through object vertices, which would require robust detection of corresponding objects (in multiple scatterer cases) between real and reconstructed images, and the handling of differences in contour point quantities.
+This could enable the creation of an indicator to measure geometry quality without considering scatterer size reconstruction precision.
+Another possible direction would be developing different test sets that explore various problem scenarios to serve as standards for algorithm comparison.
+Finally, adapting the indicators for three-dimensional problems represents another viable path for future research.
 
@@
 
-    \section*{Acknowledgment}
-
-        Use the singular heading even if you have many acknowledgments.
+    % \section*{Acknowledgment}
+
+    %     Use the singular heading even if you have many acknowledgments.
 In most cases, sponsor and financial support acknowledgments are placed in the  unnumbered footnote on the first page, not here.
+
+    %     The authors would like to thank the reviewers for their valuable contributions.
+This work was supported in part by the Brazilian agencies FAPEMIG, CNPq, and CAPES (Coordination for the Improvement of Higher Education Personnel).
 

### 2025-07-25 coverletter/cover_letter.tex
Finish first version

\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyphenat}
\usepackage[protrusion=true,expansion=false]{microtype}

\hyphenation{
elec-tro-mag-net-ic 
Trans-ac-tions 
Sam-pling 
geo-met-ric 
con-sid-er-a-tion 
eval-u-a-tion 
re-con-struc-tion 
lo-cal-i-za-tion
algo-rithm
algo-rithms
per-for-mance
indi-ca-tors
scat-ter-ing
micro-wave
bio-med-i-cal
EISPY
in-tro-ducing
con-trast
ap-prox-i-ma-tion
fa-cil-i-tat-ing
}

% Define sender information
\signature{André Costa Batista\\
Department of Electrical Engineering\\
Operations Research and Complex Systems Laboratory (ORCS Lab)\\
Universidade Federal de Minas Gerais\\
Belo Horizonte, MG 31270-901, Brazil\\
Email: andre-costa@ufmg.br}

\address{Department of Electrical Engineering\\
Universidade Federal de Minas Gerais\\
Av. Antônio Carlos, 6627\\
Belo Horizonte, MG 31270-901\\
Brazil}

\begin{document}

% Date
\date{\today}

% Recipient information
\begin{letter}{
Konstantina S. Nikita\\
Editor-in-Chief\\
IEEE Transactions on Antennas and Propagation\\
}

% Opening
\opening{Dear Editor-in-Chief,}

% Main content
I am writing to submit our manuscript entitled \textbf{``Novel Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering''} for consideration for publication in IEEE Transactions on Antennas and Propagation.

This manuscript presents a contribution to the field of electromagnetic inverse scattering by introducing two novel performance indicators specifically designed to evaluate algorithm performance in terms of shape reconstruction accuracy and object localization precision. Unlike traditional metrics such as Mean Square Error (MSE) or Structural Similarity Index (SSIM), which primarily assess contrast estimation accuracy, our proposed indicators provide direct insight into the recovery of object geometry and spatial position—critical aspects for practical applications.

\textbf{Key features of this work include:}

\begin{itemize}
    \item Introduction of two novel performance indicators: a shape error indicator and a position error indicator, specifically tailored for electromagnetic inverse scattering evaluation;
    \item Comprehensive experimental validation using six traditional algorithms: Linear Sampling Method (LSM), Orthogonality Sampling Method (OSM), Born Iterative Method (BIM), Contrast Source Iterative Method (CSI), Subspace Optimization Method (SOM), and Circle Approximation (CA);
    \item Three distinct experimental frameworks: shape recovery studies, position detection studies, and realistic breast phantom experiments;
    \item Robust statistical analysis revealing that BIM achieves optimal performance for geometric reconstruction in low nonlinearity scenarios, while SOM and OSM excel in target localization for small, high-contrast scatterers;
    \item Open-source implementation through the EISPY2D library, ensuring reproducibility and facilitating future research.
\end{itemize}

The proposed indicators address a critical gap in the current evaluation methodology for electromagnetic inverse scattering algorithms. They are applicable to both qualitative and quantitative methods and can be effectively used when these approaches are combined in experimental studies. This work provides the electromagnetic inverse scattering community with essential tools for algorithm development, benchmarking studies, and performance assessment.

\textbf{Relevance to IEEE Transactions on Antennas and Propagation:}

This work directly aligns with the journal's scope, addressing fundamental aspects of electromagnetic scattering, antenna measurement techniques, and computational electromagnetics. The proposed indicators will be valuable for researchers working on microwave imaging, antenna design optimization, and electromagnetic inverse problems—core areas within the journal's purview.

The authors declare no conflicts of interest. This manuscript has not been submitted elsewhere and contains original research. All experiments were conducted ethically, and proper attributions have been made to previous work.

We believe this manuscript will be of significant interest to the readership of IEEE Transactions on Antennas and Propagation and will contribute meaningfully to advancing the field of electromagnetic inverse scattering. We would be honored to have our work considered for publication in this prestigious journal.

Thank you for your time and consideration. We look forward to your response and are available to address any questions or concerns regarding our submission.

% Closing
\closing{Sincerely,}

% Additional signatures (co-authors)
\vspace{1cm}

\noindent
\textbf{Co-authors:}

\vspace{0.5cm}

\noindent
Ricardo Adriano\\
Professor\\
Department of Electrical Engineering\\
Universidade Federal de Minas Gerais\\
Email: rluiz@ufmg.br

\vspace{0.5cm}

\noindent
Lucas S. Batista\\
Professor\\
Department of Electrical Engineering\\
Universidade Federal de Minas Gerais\\
Operations Research and Complex Systems Laboratory (ORCS Lab)\\
Email: lusoba@ufmg.br

\end{letter}

\end{document}

### 2025-07-25 paper/main.tex
Finish first version

@@
 \usepackage{epstopdf}
+\usepackage{url}
 
@@
 
-    \title{To Be Decided}
+    \title{Novel Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering}
     \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
     \thanks{This work was supported in part by the Brazilian agency CAPES (Coordination for the Improvement of Higher Education Personnel) under Grant 88887.463864/2019-00, the scholarship FAPEMIG-CNPQ (process APQ-06716-24), and CNPq (The National Council for Scientific and Technological Development).}
-
     \thanks{A.
@@
     \begin{abstract}
-        To be written.
+        Microwave imaging is a low-cost, non-invasive technique for detecting and characterizing objects in inaccessible media through electromagnetic field measurements.
+The evaluation of algorithms that solve the related electromagnetic inverse scattering problem typically relies on metrics such as Mean Square Error (MSE) or Structural Similarity (SSIM), which primarily assess contrast estimation accuracy but provide limited insight into the recovery of object geometry and position.
+This paper introduces two novel performance indicators specifically designed to evaluate electromagnetic inverse scattering algorithms: a shape error indicator that quantifies geometric reconstruction accuracy, and a position error indicator that measures object localization precision.
+The proposed indicators are applicable to both qualitative and quantitative methods, even when they are combined in an experiment.
+Comprehensive experimental validation is conducted using traditional algorithms: Linear Sampling Method (LSM), Orthogonality Sampling Method (OSM), Born Iterative Method (BIM), Contrast Source Iterative Method (CSI), Subspace Optimization Method (SOM), and Circle Approximation (CA).
+Three distinct experimental frameworks are employed: shape recovery studies, position detection studies, and a realistic breast phantom study demonstrating their applicability.
+Supported by robust statistical analysis, the experiments revealed that: (a) in scenarios with a single scatterer and low Degree of Nonlinearity, BIM achieves the best average performance in object geometry recovery; and (b) in scenarios with a single small-sized, high-contrast scatterer, SOM and OSM achieve the best average performance in target localization.
+These indicators provide useful tools for algorithm development, benchmarking studies, and performance assessment in electromagnetic inverse scattering applications.
     \end{abstract}
@@
     \begin{IEEEkeywords}
-        Keyword 1, keyword 2, keyword 3. Remember: alphabetical order.
+        Algorithm evaluation, electromagnetic inverse scattering, microwave imaging, performance indicators.
     \end{IEEEkeywords}
@@
         Specialized algorithms have been developed to address specific problem characteristics.
-These include the DORT method \cite{chen2018computational} for electromagnetic signal time reversal, MUSIC \cite{zhong2007music} for small scatterers, and Compressive Sensing \cite{massa2015compressive} for phaseless field data.
+These include the DORT method (Decomposition of the Time-Reversal Operator) \cite{chen2018computational} for electromagnetic signal time reversal, Multiple Signal Classification (MUSIC) \cite{zhong2007music} for small scatterers, and Compressive Sensing \cite{massa2015compressive} for phaseless field data.
 For weak scatterer problems, effective approaches include First-Order Born Approximation, Backpropagation, and Rytov approximation \cite{chen2018computational}.
@@
 
-        % Quais formas de avaliar soluções e quais ferramentas já existem (incluir aquele trabalho do Kurrant que é software para câncer de mama).
-
-        % Em grande parte destes trabalhos, os algoritmos propostos são testados e avaliados em métricas como o mean square error (MSE) da estimativa do contraste pixel a pixel ou algo similar \cite{yin2023subspace,zhang2022023,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}.
-Este tipo de abordagem leva em consideração a precisão na estimativa do contraste na forma direta e, indiretamente, pode dar uma perspectiva de quão boa a reconstrução da posição e geometria dos objetos pode ser, uma vez que erros na geometria e posicionamento podem afetar nessa métrica.
-No entanto, uma geometria bem precisa com uma má estimativa do contraste pode resultar em um erro considerável neste tipo de métrica, por exemplo.
-Logo, aspectos comparar o desempenho no aspecto de quão bem a geometria e a posição dos objetos são recuperadas não são contemplados adequadamente por este tipo de métrica.
-Além disso, a métrica MSE não é adequada para avaliar algoritmos qualitativos, uma vez que estes não estimam o contraste do meio.
-Vale à pena destacar também a métrica Structural Similarity (SSIM) \cite{wang2004image} to quantitatively show the reconstruction visual quality, which is designed to compute the mismatch between reconstructed contrast results and corresponding GTs both on the pixel-wise level and perceptual level.
-Ao invés de fazer uma comparação pixel a pixel, a métrica leva em consideração aspectos de luminância, contraste e estrutura de uma imagem qualquer.
-Portanto, ao mesmo tempo que fornece uma quantificação mais profunda da qualidade de construção como um todo, ela não vai mensurar diretamente aspectos isolados como geometria e posição.
-
-        In most of these studies, the proposed algorithms are tested and evaluated using metrics such as the mean square error (MSE) of pixel-by-pixel contrast estimation or similar approaches \cite{yin2023subspace,zhang2023iterative,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}.
+        In most of these studies, the proposed algorithms are tested and evaluated using metrics such as the Mean Square Error (MSE) of pixel-by-pixel contrast estimation or similar approaches \cite{yin2023subspace,zhang2023iterative,salucci2022learned,wang2023push,liu2022som,bevacqua2021simple,bevacqua2021effective}.
 This type of approach directly considers the precision of contrast estimation and can indirectly provide perspective on how well the reconstruction of object position and geometry might be, since errors in geometry and positioning can affect this metric.
@@
 Each geometry (original and reconstructed) is converted into vectors, and the metric is calculated using a formula that performs the dot product and norm of these vectors.
-To the best of the authors' knowledge, this is the only metric that can isolately consider the geometry aspect of the scatterer, even though it is designed specifically for breast imaging.
-
-        % Descrever a lacuna para proposição de outros indicadores, tais como de posição e forma. Introduzir a minha proposta destacando vantagens, desvantagens e originalidade.
-
-        % O objetivo deste trabalho é fornecer mais métricas para auxiliar na avaliação do desempenho de algoritmos.
-Com uma gama maior de indicadores pode ser possível ter uma visão mais abrangente sobre a capacidade dos algoritmos em diferentes cenários.
-Por isso, nossa contribuição se baseia na proposição de dois novos indicadores para avaliar o desempenho dos algoritmos na recuperação da geometria e posição dos espalhadores.
-O primeiro indicador quantifica o erro de forma, enquanto o segundo quantifica o erro de posição.
-A originalidade do trabalho reside no fato de que estes indicadores podem calcular de maneira mais isolada esses dois aspectos que são relevantes da descrição do desempenho de algoritmos para o problema inverso de espalhamento eletromagnético.
-Além disso, estes indicadores são projetados para serem aplicáveis a qualquer algoritmo que reconstrua a imagem, independentemente de estimar ou não o contraste.
+To the best of the authors' knowledge, this is the only metric that can independently consider the geometry aspect of the scatterer, even though it is designed specifically for breast imaging.
 
@@
 Furthermore, these indicators are designed to be applicable to any algorithm that reconstructs images, regardless of whether it estimates contrast or not.
-
-        % Organização do texto
 
@@
 			The contrast function reconstructed by many algorithms -- such as BIM, DBIM, CSI, SOM, among others -- is commonly a discretized approximation of a continuous surface.
-Therefore, even if the original image contains only objects with well-defined boundaries and homogeneous contrast, the image of these objects obtained by the algorithms will have frequently smooth edges, i.e., the contrast value gradually varies between the background medium and the object's value.
+Therefore, even if the original image contains only objects with well-defined boundaries and homogeneous contrast, the image of these objects obtained by the algorithms will frequently have smooth edges, i.e., the contrast value gradually varies between the background medium and the object's value.
 Consequently, identifying a contour in the resulting image is heuristic because it requires selecting a criterion to define the contrast value at which a pixel can be considered as belonging to the object.
@@
 However, in scenarios where there is only one scatterer in the image, this approach is simple and effective.
-In fact, a single scatterer is the most objective way to test an algorithm's potential in recovering geometry, since the presence of multiple scatterers can degrade the algorithm's performance due to the influence of the induced currents in each scatterer on the scattering of the other.
+In fact, a single scatterer is the most objective way to test an algorithm's potential in recovering geometry, since the presence of multiple scatterers can degrade the algorithm's performance due to the influence of the induced currents in each scatterer on the scattering of the others.
 Furthermore, this approach poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods.
@@
 For example, if a star-shaped object with five points is reconstructed with one point distorted, this distortion will affect the object's centroid, thereby impacting the position error.
-However, this effect is expected, as any criterion for determining an object's position inherently considers the pixels defining it, as it is for its geometry.
+However, this effect is expected, as any criterion for determining an object's position inherently considers the pixels defining it, just as it does for its geometry.
 Furthermore, the proposed indicator is straightforward and versatile, applicable even in scenarios involving images with multiple objects.
@@
         The DOI dimensions were set to $2\lambda_b \times 2\lambda_b$, and all reconstructions were performed using a $40 \times 40$ pixel discretization.
+All implementations necessary for this work are available in the repository at \url{https://github.com/andre-batista/NPISPAEIS} for reproducibility purposes.
 
@@
                 \begin{figure*}[!htb]
-                    \subfigure[Ground-Truth]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/0}}
-                    \subfigure[LSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/1}}
-                    \subfigure[OSM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/2}} \\
-                    \subfigure[BIM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/3}}
-                    \subfigure[CSI]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/4}}
-                    \subfigure[SOM]{\includegraphics[width=0.33\textwidth]{./figs/shape/single/recons/5}}
+                    \centering
+                    \subfigure[Ground-Truth]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/0.eps}}
+                    \subfigure[LSM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/1.eps}}
+                    \subfigure[OSM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/2.eps}} \\
+                    \subfigure[BIM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/3.eps}}
+                    \subfigure[CSI]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/4.eps}}
+                    \subfigure[SOM]{\includegraphics[width=0.3\textwidth]{./experiments/shape/star/figs/5.eps}}
                     \caption{Shape recovering study, single scatterer: ground-truth and reconstructed images by each algorithm.}
@@
                     \centering
-                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_0.eps}}
-                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_1.eps}}
-                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_2.eps}}
-                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_3.eps}}
-                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/vary/figs/osm_4.eps}} \\
-                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_0.eps}}
-                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_1.eps}}
-                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_2.eps}}
-                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_3.eps}}
-                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/vary/figs/som_4.eps}}
+                    \subfigure[OSM, $\chi=0.25$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_0.eps}}
+                    \subfigure[OSM, $\chi=0.5$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_1.eps}}
+                    \subfigure[OSM, $\chi=0.75$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_2.eps}}
+                    \subfigure[OSM, $\chi=1$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_3.eps}}
+                    \subfigure[OSM, $\chi=1.5$]{\includegraphics[height=1.2in]{./experiments/shape/vary/figs/osm_4.eps}} \\
+                    \subfigure[SOM, $\chi=0.25$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_0.eps}}
+                    \subfigure[SOM, $\chi=0.5$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_1.eps}}
+                    \subfigure[SOM, $\chi=0.75$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_2.eps}}
+                    \subfigure[SOM, $\chi=1$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_3.eps}}
+                    \subfigure[SOM, $\chi=1.5$]{\includegraphics[height=1.in]{./experiments/shape/vary/figs/som_4.eps}}
                     \caption{Shape recovering study, varying contrast: reconstructed images by OSM and SOM for different contrast values.}
@@
                     \centering
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
-                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/shape/vary/figs/zeta_s.eps}\label{fig:shape:vary:indicators:zeta_s}} \hspace{0.01\columnwidth}
+                    \subfigure[]{\includegraphics[width=0.48\columnwidth]{./experiments/shape/vary/figs/dnl.eps}\label{fig:shape:vary:dnl}}
                     \caption{Shape recovering study, varying contrast: (a) shape error indicator $\zeta_S$ for OSM and SOM; (b) Degree of Nonlinearity (DNL) for each contrast value.}
@@
                     \centering
-                    \subfigure[]{\includegraphics[width=.5\columnwidth]{./experiments/average/figs/dnl.eps}\label{fig:shape:average:dnl}} \\
-                    \subfigure[]{\includegraphics[width=\columnwidth]{./experiments/average/figs/plot.eps}\label{fig:shape:average:zeta_s}}
+                    \subfigure[]{\includegraphics[width=.5\columnwidth]{./experiments/shape/average/figs/dnl.eps}\label{fig:shape:average:dnl}} \\
+                    \subfigure[]{\includegraphics[width=\columnwidth]{./experiments/shape/average/figs/plot.eps}\label{fig:shape:average:zeta_s}}
                     \caption{Shape recovering study, average performance: (a) Degree of Nonlinearity (DNL) for each scatterer; (b) shape error indicator $\zeta_S$ for each algorithm in each instance.}
@@
                     \centering
-                    \includegraphics[width=.8\columnwidth]{./experiments/average/figs/confidence_intervals.eps}
+                    \includegraphics[width=.8\columnwidth]{./experiments/shape/average/figs/confidence_intervals.eps}
                     \caption{Shape recovering study, average performance: Confidence intervals (95\%) for the shape error indicator $\zeta_S$ for each pair of algorithms.}
@@
                 \begin{figure*}[!htb]
-                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/0.eps}\label{fig:position:single:ground_truth}}
-                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/1.eps}}
-                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/2.eps}} \\
-                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/3.eps}}
-                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/4.eps}}
-                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/single/figs/5.eps}}
+                    \centering
+                    \subfigure[Ground-Truth]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/0.eps}\label{fig:position:single:ground_truth}}
+                    \subfigure[OSM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/1.eps}}
+                    \subfigure[BIM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/2.eps}} \\
+                    \subfigure[CSI]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/3.eps}}
+                    \subfigure[SOM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/4.eps}}
+                    \subfigure[CA]{\includegraphics[height=0.5\columnwidth]{../experiments/position/single/figs/5.eps}}
                     \caption{Position detection study, single scatterer: ground-truth and reconstructed images by each algorithm.}
@@
                 \begin{figure*}[!htb]
-                    \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/0.eps}\label{fig:position:multiple:ground_truth}}
-                    \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/1.eps}}
-                    \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/2.eps}} \\
-                    \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/3.eps}}
-                    \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/4.eps}}
-                    \subfigure[CA]{\includegraphics[height=0.55\columnwidth]{../experiments/position/multiple/figs/5.eps}}
+                    \centering
+                    \subfigure[Ground-Truth]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/0.eps}\label{fig:position:multiple:ground_truth}}
+                    \subfigure[OSM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/1.eps}}
+                    \subfigure[BIM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/2.eps}} \\
+                    \subfigure[CSI]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/3.eps}}
+                    \subfigure[SOM]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/4.eps}}
+                    \subfigure[CA]{\includegraphics[height=0.5\columnwidth]{../experiments/position/multiple/figs/5.eps}}
                     \caption{Position detection study, multiple scatterer: ground-truth and reconstructed images by each algorithm.}
@@
             Since the repository provides three-dimensional phantoms while our scattering model is two-dimensional, a representative cross-section focusing on the breast interior was extracted, as shown in Fig.
-\ref{fig:breast:phantom:ground_truth}.
+\ref{fig:breast:recons:ground_truth}.
 The resulting image contains 328 $\times$ 212 pixels with a spatial resolution of 0.5 mm $\times$ 0.5 mm per pixel.
 
-            The phantom includes four tissue types: fatty, transitional, fibroglandular, and skin.
+            The phantom includes four tissue types: fatty, transitional, fibroconnective/glandular, and skin.
 The breast is immersed in a homogeneous background medium with relative permittivity $\epsilon_{rb} = 10$ and conductivity $\sigma = 0$ S/m.
-The operating frequency was set to 1 GHz, with electrical properties of breast tissues determined using the Debye model.
+The operating frequency was set to 1 GHz, with electrical properties (both relative permittivity and conductivity) of breast tissues determined using the Debye model.
 
             The experimental configuration follows the previous studies: 80 incident sources, 80 measurement points, and 5\% noise level.
-Under these conditions, the DNL for this experiment is 0.05.
+Under these conditions, the DNL for this experiment is 0.013.
 Since the interior of the breast is a complex structure, keeping a low DNL value is an important strategy to facilitate the reconstruction.
+The resolution of the recovered image was set to 80 $\times$ 80 pixels.
+
+            Since fibroglandular tissue represents the region of primary interest within the breast, an adjustment to the indicator calculation methodology was necessary.
+This modification was required because fatty tissue does not exhibit zero contrast (as it is not homogeneous like the immersion medium).
+Therefore, object classification based solely on an absolute contrast threshold greater than zero would be inadequate.
+Consequently, the threshold for object classification in the original image was set as 70\% of the value between the maximum and minimum contrast values.
+Through this approach, the fibroglandular tissue region was effectively isolated, allowing for relevant shape and position error calculations.
 
@@
                 \begin{itemize}
-                    \item Threshold: 0.7;
-                    \item Regularization Method: Conjugate Gradient with 300 iterations.
+                    \item Threshold: 0.95;
+                    \item Regularization Method: Tikhonov with $\alpha = 1$.
                 \end{itemize}
@@
                 \begin{itemize}
-                    \item Threshold: 0.35;
+                    \item Threshold: 0.9;
                 \end{itemize}
@@
                 \begin{itemize}
-                    \item Regularization Method: Conjugate Gradient with 300 iterations.
-                    \item Stopping Criterion: 30 iterations.
+                    \item Regularization Method: Tikhonov with $\alpha = 10$
+                    \item Stopping Criterion: 10 iterations.
                 \end{itemize}
@@
                 \begin{itemize}
-                    \item Stopping Criterion: 300 iterations.
+                    \item Stopping Criterion: 1500 iterations.
                 \end{itemize}
@@
                 \begin{itemize}
-                    \item Stopping Criterion: 30 iterations.
-                    \item Eigenvalue Cutoff Index: 5.
-                \end{itemize}
-            \end{itemize}
+                    \item Stopping Criterion: 100 iterations.
+                    \item Eigenvalue Cutoff Index: 15.
+                \end{itemize}
+            \end{itemize}
+
+            Fig.
+\ref{fig:breast:recons} presents the reconstruction results obtained by each algorithm.
+All methods successfully detected the fibroglandular tissue region, although the quantitative algorithms varied in their contrast estimations.
+CSI and SOM underestimated the contrast values, while BIM had the closest estimation.
+As expected, the algorithms struggled to reconstruct the thin skin layer.
+However, the boundary between the fatty tissue and the immersion medium is observable in several reconstructions.
+
+            \begin{figure*}[!htb]
+                \centering
+                \subfigure[Ground-Truth]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/0.eps}\label{fig:breast:recons:ground_truth}}
+                \subfigure[LSM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/1.eps}}
+                \subfigure[OSM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/2.eps}} \\
+                \subfigure[BIM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/3.eps}} 
+                \subfigure[CSI]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/4.eps}}
+                \subfigure[SOM]{\includegraphics[height=0.55\columnwidth]{../experiments/breast/figs/5.eps}}
+                % \subfigure[CA]{\includegraphics[height=0.4\columnwidth]{../experiments/breast/figs/6.eps}}
+                \caption{Breast phantom study: ground-truth and reconstructed images by each algorithm.}
+                \label{fig:breast:recons}
+            \end{figure*}
+
+            Table \ref{tab:breast:indicators} presents the shape and position error indicators for each algorithm.
+The shape error values exceed 57\% for all methods, indicating significant challenges in accurately reconstructing the glandular tissue structure.
+Since this tissue size is small compared to the image dimensions, variations in the size and shape of the tissue reconstruction can significantly impact the shape indicator.
+Regarding position detection, all algorithms achieved relatively low position errors (below 5\%), with SOM demonstrating the best performance at 1.6\%.
+
+            \begin{table}[!htb]
+                \centering
+                \renewcommand{\arraystretch}{1.5}
+                \caption{Breast phantom study: shape and position error indicators for each algorithm.}
+                \label{tab:breast:indicators}
+                \begin{tabular}{cccccc}
+                    Method & LSM & OSM & BIM & CSI & SOM \\\hline %  & CA \\\hline
+                    $\zeta_S$ (\%) & 83.6 & 78.6 & 57.2 & 81.4 & 118.8 \\ % & 86.5 \\
+                    $\zeta_P$ (\%) & 2.2 & 4.3 & 3.1 & 3.5 & 1.6 %% & 4.2 \\
+                \end{tabular}   
+            \end{table}
 
@@
 \end{document}
-
-% Figure example.
-\begin{figure}[!t]
-    \centerline{\includegraphics[width=\columnwidth]{fig1.png}}
-    \caption{Magnetization as a function of applied field. It is good practice to explain the significance of the figure in the caption.}
-    \label{example}
-\end{figure}
-
-% Table example.
-\begin{table}
-    \caption{Units for Magnetic Properties}
-    \label{table}
-    \setlength{\tabcolsep}{3pt}
-    \begin{tabular}{|p{25pt}|p{75pt}|p{115pt}|}
-        \hline
-        Symbol& Quantity& Conversion from Gaussian and \par CGS EMU to SI $^{\mathrm{a}}$ \\\hline
-        $\Phi $& magnetic flux& 1 Mx $\to  10^{-8}$ Wb $= 10^{-8}$ V$\cdot $s \\
-        $B$& magnetic flux density, \par magnetic induction& 1 G $\to  10^{-4}$ T $= 10^{-4}$ Wb/m$^{2}$ \\
-        $H$& magnetic field strength& 1 Oe $\to  10^{3}/(4\pi )$ A/m \\
-        $m$& magnetic moment& 1 erg/G $=$ 1 emu \par $\to 10^{-3}$ A$\cdot $m$^{2} = 10^{-3}$ J/T \\
-        $M$& magnetization& 1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 10^{3}$ A/m \\
-        4$\pi M$& magnetization& 1 G $\to  10^{3}/(4\pi )$ A/m \\
-        $\sigma $& specific magnetization& 1 erg/(G$\cdot $g) $=$ 1 emu/g $\to $ 1 A$\cdot $m$^{2}$/kg \\
-        $j$& magnetic dipole \par moment& 1 erg/G $=$ 1 emu \par $\to 4\pi \times  10^{-10}$ Wb$\cdot $m \\
-        $J$& magnetic polarization& 1 erg/(G$\cdot $cm$^{3}) =$ 1 emu/cm$^{3}$ \par $\to 4\pi \times  10^{-4}$ T \\
-        $\chi , \kappa $& susceptibility& 1 $\to  4\pi $ \\
-        $\chi_{\rho }$& mass susceptibility& 1 cm$^{3}$/g $\to  4\pi \times  10^{-3}$ m$^{3}$/kg \\
-        $\mu $& permeability& 1 $\to  4\pi \times  10^{-7}$ H/m \par $= 4\pi \times  10^{-7}$ Wb/(A$\cdot $m) \\
-        $\mu_{r}$& relative permeability& $\mu \to \mu_{r}$ \\
-        $w, W$& energy density& 1 erg/cm$^{3} \to  10^{-1}$ J/m$^{3}$ \\
-        $N, D$& demagnetizing factor& 1 $\to  1/(4\pi )$ \\\hline
-        \multicolumn{3}{p{251pt}}{Vertical lines are optional in tables. Statements that serve as captions for the entire table do not need footnote letters. }\\
-        \multicolumn{3}{p{251pt}}{$^{\mathrm{a}}$Gaussian units are the same as cg emu for magnetostatics; Mx $=$ maxwell, G $=$ gauss, Oe $=$ oersted; Wb $=$ weber, V $=$ volt, s $=$ second, T $=$ tesla, m $=$ meter, A $=$ ampere, J $=$ joule, kg $=$ kilogram, H $=$ henry.}
-    \end{tabular}
-    \label{tab1}
-\end{table}

### 2025-07-25 eispy2d/library/result.py

@@ -1853,6 +1853,7 @@ def compute_zeta_tfpad(et_o, et_r):
 
 def compute_zeta_p(chi_o, chi_r):
     Xo, Xr = np.abs(chi_o), np.abs(chi_r)
+    # threshold2 = (np.amin(Xo) + .7*(np.amax(Xo)-np.amin(Xo)))
     threshold = (np.amin(np.abs(Xr))
                  + .5*(np.amax(np.abs(Xr))-np.amin(np.abs(Xr))))
 
@@ -1860,6 +1861,7 @@ def compute_zeta_p(chi_o, chi_r):
     maskr = np.zeros(Xr.shape, dtype=bool)
 
     masko[Xo > 0.] = True
+    # masko[Xo >= threshold2] = True
     maskr[Xr >= threshold] = True
 
     xo, yo = np.meshgrid(np.linspace(0, 1, Xo.shape[1]),
@@ -1882,10 +1884,12 @@ def compute_zeta_p(chi_o, chi_r):
 def compute_zeta_s(chi_o, chi_r, threshold=.5):
     Xo, Xr = np.abs(chi_o), np.abs(chi_r)
     Xrmin, Xrmax = np.amin(Xr), np.amax(Xr)
+    # threshold2 = (np.amin(Xo) + 0.7*(np.amax(Xo)-np.amin(Xo)))
     threshold = (Xrmin + threshold*(Xrmax-Xrmin))
-
     # Thresholding
     Xo[Xo > 0] = 1
+    # Xo[Xo <= threshold2] = 0
+    # Xo[Xo > threshold2] = 1
     Xr[Xr <= threshold] = 0
     Xr[Xr > threshold] = 1
     

### 2025-07-25 experiments/average/computednl.py

@@ -1,23 +1,0 @@
-"""
-Script to compute DNL for benchmark test cases.
-
-This script loads a benchmark dataset, computes the DNL for each test case,
-and saves the updated benchmark data with DNL values.
-"""
-
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-import benchmark as bmk
-
-# Load the benchmark dataset from the specified file and path
-benchmark = bmk.Benchmark(import_filename="average.bmk",
-                          import_filepath="../../data/shape/average/")
-
-# Compute DNL for each test case in the benchmark
-for n in range(30):
-    benchmark.testset.test[n].compute_dnl()
-
-# Save the updated benchmark data with computed DNL values
-# save_testset=True ensures that the test set data is also saved
-benchmark.save(file_path="../../data/shape/average/",
-               save_testset=True)

### 2025-07-25 experiments/average/gendata.py

@@ -1,45 +1,0 @@
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-
-import configuration as cfg
-import testset as tst
-from experiment import RANDOM_POLYGONS_PATTERN
-import result as rst
-import mom_cg_fft as mom
-
-name = 'average'
-NM = NS = 80
-Ro = 4.
-lambda_b = 1.
-epsilon_rb = 1.
-Lx = Ly = 2.
-E0 = 1.
-perfect_dielectric = True
-
-config = cfg.Configuration(name=name + '.cfg', number_measurements=NM,
-                           number_sources=NS, observation_radius=Ro,
-                           wavelength=lambda_b,
-                           background_permittivity=epsilon_rb,
-                           image_size=[Ly, Lx], magnitude=E0,
-                           perfect_dielectric=perfect_dielectric)
-
-contrast = .25
-object_size = .9
-resolution = (120, 120)
-map_pattern = RANDOM_POLYGONS_PATTERN
-sample_size = 30
-noise = 5.
-indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
-
-testset = tst.TestSet(name=name + '.tst', configuration=config,
-                      contrast=contrast, object_size=object_size, 
-                      resolution=resolution, map_pattern=map_pattern,
-                      sample_size=sample_size, noise=noise,
-                      indicators=indicators)
-
-testset.randomize_tests(compute_dnl=False)
-
-testset.generate_field_data(solver=mom.MoM_CG_FFT(tolerance=1e-3,
-                                                  maximum_iterations=5000))
-
-testset.save(file_path='./data/')

### 2025-07-25 experiments/average/launch.py

@@ -1,2 +1,0 @@
-import gendata
-import runexperiment

### 2025-07-25 experiments/average/runexperiment.py

@@ -1,43 +1,0 @@
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-
-import testset as tst
-import richmond as ric
-import regularization as reg
-import mom_cg_fft as mom
-import stopcriteria as stp
-import lsm
-import osm
-import bim
-import csi
-import som
-import benchmark as bmk
-
-name = 'average'
-resolution = (40, 40)
-
-testset = tst.TestSet(import_filename=name + '.tst',
-                      import_filepath='./data/')
-
-method = [
-    lsm.LinearSamplingMethod(alias='lsm',
-                             regularization=reg.ConjugatedGradient(300),
-                             sv_cutoff=None, threshold=.7),
-    osm.OrthogonalitySamplingMethod(threshold=.35),
-    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.ConjugatedGradient(300), 
-                            stp.StopCriteria(max_iterations=30)),
-    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=300)),
-    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
-                                        cutoff_index=5)
-]
-
-discretization = ric.Richmond(configuration=testset.test[0].configuration,
-                              elements=resolution)
-
-benchmark = bmk.Benchmark(name=name + '.bmk', method=method, 
-                          discretization=discretization, testset=testset)
-
-benchmark.run(parallelization=bmk.PARALLELIZE_EXECUTIONS, pre_save=True,
-              file_path='./data/')
-
-benchmark.save(file_path='./data/', save_testset=True)

### 2025-07-25 experiments/breast/gendata.py

@@ -1,5 +1,5 @@
 from loadphantom import BreastPhantomReader
-file_path = "../../data/breast/"
+file_path = "../../data/breast/class2/phantom1/"
 reader = BreastPhantomReader(file_path)
 
 freq = 1. # GHz

### 2025-07-25 experiments/breast/genfigures.py

@@ -1,6 +1,6 @@
 from matplotlib import pyplot as plt
 import sys
-sys.path.insert(1, '../../../eispy2d/library/')
+sys.path.insert(1, '../../eispy2d/library/')
 import casestudy as cst
 import result as rst
 
@@ -24,8 +24,8 @@ def configure_axes(axis, hide_x_labels=True, hide_y_labels=True):
         axis[0].set_yticklabels([])
 
 # Initialize case study
-mycase = cst.CaseStudy(import_filename='single.cst', 
-                       import_filepath='../../../data/position/single/')
+mycase = cst.CaseStudy(import_filename='breastphantom.cst', 
+                       import_filepath='../../data/breast/class2/phantom1/')
 filepath = './figs/'
 
 # Generate ground truth figure
@@ -37,11 +37,12 @@ save_figure(filepath, '0')
 
 # Methods to generate reconstructions
 methods = [
-    ('osm', '1', True, True),
-    ('bim', '2', True, True), 
-    ('csi', '3', False, False),  # Keep original labels for CSI
-    ('som', '4', False, True),
-    ('ca', '5', False, True)
+    ('lsm', '1', True, True),
+    ('osm', '2', True, True),
+    ('bim', '3', False, False), 
+    ('csi', '4', False, True),  # Keep original labels for CSI
+    ('som', '5', False, True),
+    ('ca',  '6', False, True)
 ]
 
 # Generate reconstruction figures

### 2025-07-25 experiments/breast/getsample.m

@@ -1,14 +1,0 @@
-clear
-
-filepath = './class3/phantom1';
-frequency = 1e9;
-epsilon_rb = 20;
-sigma_b = 0;
-new_res = [150,150];
-
-[epsilon_r,sigma,dx,dy,mi] = loadphantom2D ...
-    (filepath,frequency,epsilon_rb,sigma_b,new_res);
-
-plotsample(epsilon_r,sigma,dx,dy)
-
-save sample.mat dx dy epsilon_r sigma epsilon_rb sigma_b mi

### 2025-07-25 experiments/breast/getsampleset.m

@@ -1,21 +1,0 @@
-clear
-
-filepath = './class1/phantom1';
-namefile = 'class_1_1';
-frequency = 1e9;
-epsilon_rb = 20; % 20;
-sigma_b = 0;
-new_res = [150,150];
-slices = 5;
-
-[aux_epsilon_r,aux_sigma,dx,dy,aux_mi] = loadphantom2Dset ...
-    (filepath,frequency,epsilon_rb,sigma_b,new_res,slices);
-
-for i = 1:slices
-    epsilon_r = squeeze(aux_epsilon_r(i,:,:));
-    sigma = squeeze(aux_sigma(i,:,:));
-    mi = aux_mi{i};
-    plotsample(epsilon_r,sigma,dx,dy)
-    pause(1)
-    save([namefile,'_',num2str(i),'.mat'],'dx','dy','epsilon_r','sigma','epsilon_rb','sigma_b','mi');
-end

### 2025-07-25 experiments/breast/loadphantom2D.m

@@ -1,106 +1,0 @@
-function [epsilon_r,sigma_eff,dx,dy,mi] = loadphantom2D ...
-    (filepath,f,epsilon_rb,sigma_b,new_res)
-
-    % Constants
-    omega = 2*pi*f;
-    dx = .5e-3; dy = .5e-3; dz = .5e-3;
-    epsilon_0 = 8.854187817e-12;
-    
-    % Cole-Cole parameters - 500MHz < f < 20GHz
-    epsilon_inf = [2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.];
-    epsilon_delta = [.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31];
-    tau = 1e-12 * [16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585];
-    alpha = [.251, .069, .061, .055, .003, .047, .049, .063];
-    sigma_s = [.002, .02, .036, .083, .462, .713, .809, 1.37];
-
-    bi_file = fopen([filepath,'/breastInfo.txt'],'r');
-    breastInfo = fscanf(bi_file,'%s');
-    fclose(bi_file);
-
-    m_file = fopen([filepath '/mtype.txt'],'r');
-    mi = fscanf(m_file,'%f');
-    fclose(m_file);
-    
-    p_file = fopen([filepath '/pval.txt'],'r');
-    p_i = fscanf(p_file,'%f');
-    fclose(p_file);
-    
-    epsilon_star = epsilon_inf ...
-        + epsilon_delta./(1+(1j*omega*tau).^(1-alpha)) ...
-        + sigma_s/1j/omega/epsilon_0;
-    
-    bound_epsilon_r = real(epsilon_star);
-    bound_sigma_eff = -imag(epsilon_star)*omega*epsilon_0;
-    
-    epsilon_r = epsilon_rb * ones(size(mi));
-    sigma_eff = sigma_b * ones(size(mi));
-    
-    tissues = [3.3, 3.2, 3.1, 2, 1.3, 1.2, 1.1];
-    
-    for i = 1:length(tissues)
-        
-        epsilon_r(mi==tissues(i)) = p_i(mi==tissues(i))*bound_epsilon_r(i+1)...
-            +(1-p_i(mi==tissues(i)))*bound_epsilon_r(i);
-        
-        sigma_eff(mi==tissues(i)) = p_i(mi==tissues(i))*bound_sigma_eff(i+1)...
[…]

### 2025-07-25 experiments/breast/loadphantom2D.py

@@ -1,185 +1,0 @@
-import numpy as np
-from scipy.interpolate import RegularGridInterpolator
-import os
-
-def loadphantom2D(filepath, f, epsilon_rb, sigma_b, new_res=None):
-    """
-    Load a 2D breast phantom with electromagnetic properties.
-    
-    Parameters:
-    -----------
-    filepath : str
-        Path to the directory containing phantom data files
-    f : float
-        Frequency in Hz
-    epsilon_rb : float
-        Relative permittivity of background medium
-    sigma_b : float
-        Conductivity of background medium
-    new_res : tuple or None
-        New resolution (nx, ny) or (dx, dy) for resampling
-    
-    Returns:
-    --------
-    epsilon_r : ndarray
-        Relative permittivity distribution
-    sigma_eff : ndarray
-        Effective conductivity distribution
-    dx : float
-        Grid spacing in x direction
-    dy : float
-        Grid spacing in y direction
-    mi : ndarray
-        Indices of background medium pixels
-    """
-    
-    # Constants
-    omega = 2 * np.pi * f
-    dx = 0.5e-3
-    dy = 0.5e-3
-    dz = 0.5e-3
-    epsilon_0 = 8.854187817e-12
-    
-    # Cole-Cole parameters - 500MHz < f < 20GHz
-    epsilon_inf = np.array([2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.])
-    epsilon_delta = np.array([0.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31])
-    tau = 1e-12 * np.array([16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585])
-    alpha = np.array([0.251, 0.069, 0.061, 0.055, 0.003, 0.047, 0.049, 0.063])
-    sigma_s = np.array([0.002, 0.02, 0.036, 0.083, 0.462, 0.713, 0.809, 1.37])
-    
-    # Read breast information
-    with open(os.path.join(filepath, 'breastInfo.txt'), 'r') as bi_file:
-        breastInfo = bi_file.read().strip()
-    
-    # Read material type
-    with open(os.path.join(filepath, 'mtype.txt'), 'r') as m_file:
-        mi = np.fromfile(m_file, sep=' ')
-    
-    # Read property values
[…]

### 2025-07-25 experiments/breast/loadphantom2Dset.m

@@ -1,115 +1,0 @@
-function [epsilon_r,sigma_eff,dx,dy,mi] = loadphantom2Dset ...
-    (filepath,f,epsilon_rb,sigma_b,new_res,slices)
-
-    % Constants
-    omega = 2*pi*f;
-    dx = .5e-3; dy = .5e-3; dz = .5e-3;
-    epsilon_0 = 8.854187817e-12;
-    
-    % Cole-Cole parameters - 500MHz < f < 20GHz
-    epsilon_inf = [2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.];
-    epsilon_delta = [.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31];
-    tau = 1e-12 * [16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585];
-    alpha = [.251, .069, .061, .055, .003, .047, .049, .063];
-    sigma_s = [.002, .02, .036, .083, .462, .713, .809, 1.37];
-
-    bi_file = fopen([filepath,'/breastInfo.txt'],'r');
-    breastInfo = fscanf(bi_file,'%s');
-    fclose(bi_file);
-
-    m_file = fopen([filepath '/mtype.txt'],'r');
-    mi = fscanf(m_file,'%f');
-    fclose(m_file);
-    
-    p_file = fopen([filepath '/pval.txt'],'r');
-    p_i = fscanf(p_file,'%f');
-    fclose(p_file);
-    
-    epsilon_star = epsilon_inf ...
-        + epsilon_delta./(1+(1j*omega*tau).^(1-alpha)) ...
-        + sigma_s/1j/omega/epsilon_0;
-    
-    bound_epsilon_r = real(epsilon_star);
-    bound_sigma_eff = -imag(epsilon_star)*omega*epsilon_0;
-    
-    epsilon_r = epsilon_rb * ones(size(mi));
-    sigma_eff = sigma_b * ones(size(mi));
-    
-    tissues = [3.3, 3.2, 3.1, 2, 1.3, 1.2, 1.1];
-    
-    for i = 1:length(tissues)
-        
-        epsilon_r(mi==tissues(i)) = p_i(mi==tissues(i))*bound_epsilon_r(i+1)...
-            +(1-p_i(mi==tissues(i)))*bound_epsilon_r(i);
-        
-        sigma_eff(mi==tissues(i)) = p_i(mi==tissues(i))*bound_sigma_eff(i+1)...
[…]

### 2025-07-25 experiments/breast/loadphantom2Dset.py

@@ -1,206 +1,0 @@
-import numpy as np
-from scipy.interpolate import RegularGridInterpolator
-import os
-
-def loadphantom2Dset(filepath, f, epsilon_rb, sigma_b, new_res=None, slices=1):
-    """
-    Load a set of 2D slices from a 3D breast phantom with electromagnetic properties.
-    
-    Parameters:
-    -----------
-    filepath : str
-        Path to the directory containing phantom data files
-    f : float
-        Frequency in Hz
-    epsilon_rb : float
-        Relative permittivity of background medium
-    sigma_b : float
-        Conductivity of background medium
-    new_res : tuple or None
-        New resolution (ny, nz) or (dy, dz) for resampling
-    slices : int
-        Number of slices to extract from the phantom
-    
-    Returns:
-    --------
-    epsilon_r : ndarray
-        Relative permittivity distribution for all slices (slices x ny x nz)
-    sigma_eff : ndarray
-        Effective conductivity distribution for all slices (slices x ny x nz)
-    dx : float
-        Grid spacing in x direction
-    dy : float
-        Grid spacing in y direction
-    mi : list
-        List of background medium indices for each slice
-    """
-    
-    # Constants
-    omega = 2 * np.pi * f
-    dx = 0.5e-3
-    dy = 0.5e-3
-    dz = 0.5e-3
-    epsilon_0 = 8.854187817e-12
-    
-    # Cole-Cole parameters - 500MHz < f < 20GHz
-    epsilon_inf = np.array([2.293, 2.908, 3.140, 4.031, 9.941, 7.821, 6.151, 1.])
-    epsilon_delta = np.array([0.141, 1.2, 1.708, 3.654, 26.6, 41.48, 48.26, 66.31])
-    tau = 1e-12 * np.array([16.4, 16.88, 14.65, 14.12, 10.9, 10.66, 10.26, 7.585])
-    alpha = np.array([0.251, 0.069, 0.061, 0.055, 0.003, 0.047, 0.049, 0.063])
-    sigma_s = np.array([0.002, 0.02, 0.036, 0.083, 0.462, 0.713, 0.809, 1.37])
-    
-    # Read breast information
-    with open(os.path.join(filepath, 'breastInfo.txt'), 'r') as bi_file:
-        breastInfo = bi_file.read().strip()
-    
-    # Read material type
-    with open(os.path.join(filepath, 'mtype.txt'), 'r') as m_file:
[…]

### 2025-07-25 experiments/breast/phantom_read.m

@@ -1,87 +1,0 @@
-%% PHANTOM_READ - Obtain permittivity and conductivity information
-% This function reads the permittivity and conductivity information as in
-% [1].
-% Inputs:
-%   filepath:   String with path to the files (breastInfo,mtype,pval)
-%   f:          Linear frequency [Hz]
-% Outpus
-%   eps:    Relative permittivity
-%   sgma:   Conductivity [S/m]
-%   mi:     Media indexes:
-%       -1:  Immersion medium
-%       -2:  Skin
-%       -4:  Muscle
-%       1.1: Fibroconnective/glandular-1
-%       1.2: Fibroconnective/glandular-2
-%       1.3: Fibroconnective/glandular-3
-%       2:   Transitional
-%       3.1: Fatty-1
-%       3.2: Fatty-2
-%       3.3: Fatty-3
-
-function [eps,sgma,mi] = phantom_read(filepath,f)
-
-    % Read main data
-    bi = fileread([filepath '/breastInfo.txt']);
-    be = strfind(bi, '=');
-    s1 = str2double(bi(be(2)+1:be(2)+3));
-    s2 = str2double(bi(be(3)+1:be(3)+3));
-    s3 = str2double(bi(be(4)+1:be(4)+3));
-    
-    % Read media indexes
-    mi = textread([filepath '/mtype.txt'],'%f');
-    mi = reshape(mi,[s1 s2 s3]);
-
-    % Read p_i data
-    p_i = textread([filepath '/pval.txt'],'%f');
-    p_i = reshape(p_i,[s1 s2 s3]);
-    
-    % Genreal parameters
-    w = 2*pi*f;
-    eps_0= 8.85e-12;
-    
-    if f>3e9 && f<=10e9 % ref paper : instruction manual
-        % 3 adipose/fat , 1 fibroglandular
-        %[min 3_low 3_med 3_high 1_low 1_med 1_high max skin mus];
-        e_i = [2.293 2.848 3.116 3.987 12.99 13.81 14.2 23.2 15.93 21.66];
-        e_d = [0.092 1.104 1.592 3.545 24.4 35.55 40.49 46.05 23.83 33.24];
-        tau = 13e-12;
-        s = [0.005 0.005 0.05 0.08 0.397 0.738 0.824 1.306 0.831 0.886];
[…]

### 2025-07-25 experiments/breast/runexperiment.py

@@ -16,24 +16,26 @@ import som
 import circleapproximation as ca
 
 name = 'breastphantom'
-file_path = "../../data/breast/"
-resolution = (40, 40)
+file_path = "../../data/breast/class2/phantom1/"
+resolution = (80, 80)
 contrast_range = (0.1, 10.)
 
 test = ipt.InputData(import_filename=name + '.ipt', import_filepath=file_path)
 
 method = [
     lsm.LinearSamplingMethod(alias='lsm',
-                             regularization=reg.ConjugatedGradient(300),
-                             sv_cutoff=None, threshold=.7),
-    osm.OrthogonalitySamplingMethod(threshold=.35),
-    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.ConjugatedGradient(300), 
-                            stp.StopCriteria(max_iterations=30)),
-    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=1_000)),
-    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
+                             regularization=reg.Tikhonov(reg.TIK_FIXED,
+                                                         parameter=1e0),
+                             sv_cutoff=None, threshold=.95),
+    osm.OrthogonalitySamplingMethod(threshold=.90),
+    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.Tikhonov(reg.TIK_FIXED, 
+                                                           parameter=1e1),
+                            stp.StopCriteria(max_iterations=10)),
+    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=1_500)),
+    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=100),
                                         cutoff_index=15),
     ca.CircleApproximation(stc.OutputMode(stc.BEST_CASE, reference='zeta_s'),
-                           number_executions=1,
+                           number_executions=10,
                            contrast_range=contrast_range,
                            solver="de")
 ]

### 2025-07-25 experiments/breast/save_data.m

@@ -1,30 +1,0 @@
-clc, clear
-
-%% General parameters
-f = 1e9;
-nsamp = 100;
-bd_epsr = [1,5];
-bd_sig = [0,1];
-img_size = [50,50];
-
-%% Bounds
-bd = [20,270]; filepath = './class1/phantom1';      % class1 - phantom1
-% bd = [26,225]; filepath = './class1/phantom2';      % class1 - phantom2
-
-%% Collecting data
-[epsilon,sigma,mi] = phantom_read(filepath,f);
-i = round(linspace(bd(1),bd(2),nsamp+2));
-i([1,end]) = [];
-epsilon = bd_epsr(1) + diff(bd_epsr)*epsilon(i,:,:)/max(epsilon(:));
-sigma = bd_sig(1) + diff(bd_sig)*sigma(i,:,:)/max(sigma(:));
-[~,J,K] = size(epsilon);
-j = round(linspace(0,J+1,img_size(1)+2));
-j([1,end]) = [];
-k = round(linspace(0,K+1,img_size(2)+2));
-k([1,end]) = [];
-epsilon = epsilon(:,j,k);
-sigma = sigma(:,j,k);
-id = filepath(3:end);
-
-%% Saving data
-save([filepath,'/phantoms.mat'],'epsilon','sigma','bd_epsr','bd_sig','id')

### 2025-07-25 experiments/explicacoes-geradados.py

@@ -1,72 +1,0 @@
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-import configuration as cfg
-import inputdata as ipt
-import result as rst
-import draw
-import mom_cg_fft as mom
-import osm
-import regularization as reg
-import richmond as ric
-
-name = 'test.cfg'
-NM = NS = 40
-Ro = 3.
-lambda_b = 1.
-epsilon_rb = 1.
-Lx = Ly = 4.
-E0 = 1.
-perfect_dielectric = True
-
-config = cfg.Configuration(name=name, number_measurements=NM, number_sources=NS,
-                           observation_radius=Ro, wavelength=lambda_b,
-                           background_permittivity=epsilon_rb,
-                           image_size=[Ly, Lx], magnitude=E0,
-                           perfect_dielectric=perfect_dielectric)
-
-
-name = 'test.ipt'
-resolution = (150, 150)
-noise = 5.
-indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
-
-test = ipt.InputData(name=name, configuration=config, resolution=resolution, 
-                     noise=noise, indicators=indicators)
-
-epsilon_rd = 1.25
-chi = (epsilon_rd-epsilon_rb)/epsilon_rb
-l = 0.9
-position = [.4, .4]
-
-test.rel_permittivity, _ = draw.square(
-    l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
-    background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd,
-    center=position, rotate=0.
-)
-
-position = [-1, -1]
-
-test.rel_permittivity, _ = draw.triangle(
-    l, axis_length_x=Lx, axis_length_y=Ly,
-    background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd,
-    center=position, rotate=0., rel_permittivity=test.rel_permittivity
-)
-
-forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=5000,
-                         parallelization=True)
-
-_ = forward.solve(test)
-
-threshold = 0.35
-
-method = osm.OrthogonalitySamplingMethod(threshold=threshold)
-
-image = (50, 50)
-
-discretization = ric.Richmond(configuration=config, elements=image)
-
-result = method.solve(test, discretization=discretization)
-
-test.save(file_path='./data/')
-result.name = 'test-osm.rst'
-result.save(file_path='./data/')

### 2025-07-25 experiments/shape/average/computednl.py

@@ -1,0 +1,23 @@
+"""
+Script to compute DNL for benchmark test cases.
+
+This script loads a benchmark dataset, computes the DNL for each test case,
+and saves the updated benchmark data with DNL values.
+"""
+
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+import benchmark as bmk
+
+# Load the benchmark dataset from the specified file and path
+benchmark = bmk.Benchmark(import_filename="average.bmk",
+                          import_filepath="../../../data/shape/average/")
+
+# Compute DNL for each test case in the benchmark
+for n in range(30):
+    benchmark.testset.test[n].compute_dnl()
+
+# Save the updated benchmark data with computed DNL values
+# save_testset=True ensures that the test set data is also saved
+benchmark.save(file_path="../../../data/shape/average/",
+               save_testset=True)

### 2025-07-25 experiments/shape/average/gendata.py

@@ -1,0 +1,45 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import configuration as cfg
+import testset as tst
+from experiment import RANDOM_POLYGONS_PATTERN
+import result as rst
+import mom_cg_fft as mom
+
+name = 'average'
+NM = NS = 80
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+
+config = cfg.Configuration(name=name + '.cfg', number_measurements=NM,
+                           number_sources=NS, observation_radius=Ro,
+                           wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+contrast = .25
+object_size = .9
+resolution = (120, 120)
+map_pattern = RANDOM_POLYGONS_PATTERN
+sample_size = 30
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
+
+testset = tst.TestSet(name=name + '.tst', configuration=config,
+                      contrast=contrast, object_size=object_size, 
+                      resolution=resolution, map_pattern=map_pattern,
+                      sample_size=sample_size, noise=noise,
+                      indicators=indicators)
+
+testset.randomize_tests(compute_dnl=False)
+
+testset.generate_field_data(solver=mom.MoM_CG_FFT(tolerance=1e-3,
+                                                  maximum_iterations=5000))
+
+testset.save(file_path='../../../data/shape/average/')

### 2025-07-25 experiments/shape/average/runexperiment.py

@@ -1,0 +1,43 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import testset as tst
+import richmond as ric
+import regularization as reg
+import mom_cg_fft as mom
+import stopcriteria as stp
+import lsm
+import osm
+import bim
+import csi
+import som
+import benchmark as bmk
+
+name = 'average'
+resolution = (40, 40)
+
+testset = tst.TestSet(import_filename=name + '.tst',
+                      import_filepath='../../../data/shape/average/')
+
+method = [
+    lsm.LinearSamplingMethod(alias='lsm',
+                             regularization=reg.ConjugatedGradient(300),
+                             sv_cutoff=None, threshold=.7),
+    osm.OrthogonalitySamplingMethod(threshold=.35),
+    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.ConjugatedGradient(300), 
+                            stp.StopCriteria(max_iterations=30)),
+    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=300)),
+    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
+                                        cutoff_index=5)
+]
+
+discretization = ric.Richmond(configuration=testset.test[0].configuration,
+                              elements=resolution)
+
+benchmark = bmk.Benchmark(name=name + '.bmk', method=method, 
+                          discretization=discretization, testset=testset)
+
+benchmark.run(parallelization=bmk.PARALLELIZE_EXECUTIONS, pre_save=True,
+              file_path='../../../data/shape/average/',)
+
+benchmark.save(file_path='../../../data/shape/average/', save_testset=True)

### 2025-07-25 experiments/shape/star/gendata.py

@@ -1,0 +1,53 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import configuration as cfg
+import inputdata as ipt
+import result as rst
+import draw
+import mom_cg_fft as mom
+
+# Parameters
+name = 'star'
+file_path = '../../../data/shape/star/'
+NM = NS = 80
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+resolution = (120, 120)
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
+epsilon_rd = 1.25
+l = 0.9
+position = [.0, .0]
+
+config = cfg.Configuration(name=name + '.cfg', number_measurements=NM, 
+                           number_sources=NS, observation_radius=Ro, 
+                           wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+
+test = ipt.InputData(name=name + '.ipt', configuration=config, 
+                     resolution=resolution, noise=noise, indicators=indicators)
+
+chi = (epsilon_rd-epsilon_rb)/epsilon_rb
+
+test.rel_permittivity, _ = draw.star5(
+    l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
+    background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd,
+    center=position, rotate=0.
+)
+
+forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=5000,
+                         parallelization=True)
+
+_ = forward.solve(test)
+
+test.compute_dnl()
+
+test.save(file_path=file_path)

### 2025-07-25 experiments/shape/star/genfigures.py

@@ -1,0 +1,64 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+import casestudy as cst
+from matplotlib import pyplot as plt
+import result as rst
+import inputdata as ipt
+
+test = ipt.InputData(import_filename='star.ipt',
+                     import_filepath='../../../data/shape/star/')
+
+casestudy = cst.CaseStudy(import_filename='star.cst',
+                          import_filepath='../../../data/shape/star/')
+casestudy.test = test
+
+filepath = './figs/'
+plt.rcParams['image.cmap'] = 'Greys'
+plt.rcParams['font.family'] = 'serif'
+plt.rcParams['font.serif'] = 'Times New Roman'
+fig, axis, _ = rst.get_figure(1)
+test.draw(fontsize=20, axis=axis, title=False, vmax=0.35)
+# axis[0].set_xticks([-1, 0, 1])
+axis[0].set_xticklabels([])
+# # Ajustar os ticks da colorbar existente
+# if fig.axes[-1].images:  # Verifica se há uma imagem associada à última barra
+#     cbar = fig.axes[-1]
+#     cbar.set_ticks([0.1, 0.2, 0.3])  #
+plt.tight_layout()
+plt.savefig(filepath + '0.eps', format='eps')
+plt.close()
+axis = casestudy.reconstruction(fontsize=20, method='lsm', title=False)
+axis[0].set_xticklabels([])
+axis[0].set_yticklabels([])
+plt.tight_layout()
+plt.savefig(filepath + '1.eps', format='eps')
+plt.close()
+axis = casestudy.reconstruction(fontsize=20, method='osm', title=False)
+axis[0].set_xticklabels([])
+axis[0].set_yticklabels([])
+plt.tight_layout()
+plt.savefig(filepath + '2.eps', format='eps')
+plt.close()
+axis = casestudy.reconstruction(fontsize=20, method='bim', vmax=0.35, title=False)
+# axis[0].set_xticklabels([])
+# axis[0].set_yticklabels([])
+plt.tight_layout()
+plt.savefig(filepath + '3.eps', format='eps')
+plt.close()
+axis = casestudy.reconstruction(fontsize=20, method='csi', vmax=0.35, title=False)
+# axis[0].set_xticklabels([])
+axis[0].set_yticklabels([])
+plt.tight_layout()
+plt.savefig(filepath + '4.eps', format='eps')
[…]

### 2025-07-25 experiments/shape/star/runexperiment.py

@@ -1,0 +1,46 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import inputdata as ipt
+import casestudy as cst
+import richmond as ric
+import regularization as reg
+import mom_cg_fft as mom
+import stopcriteria as stp
+import lsm
+import osm
+import bim
+import csi
+import som
+
+name = 'star'
+filepath = '../../../data/shape/star/'
+resolution = (40, 40)
+
+test = ipt.InputData(import_filename=name + '.ipt',
+                     import_filepath=filepath)
+
+method = [
+    lsm.LinearSamplingMethod(alias='lsm',
+                             regularization=reg.ConjugatedGradient(300),
+                             sv_cutoff=None, threshold=.7),
+    osm.OrthogonalitySamplingMethod(threshold=.35),
+    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.ConjugatedGradient(300), 
+                            stp.StopCriteria(max_iterations=30)),
+    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=300)),
+    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
+                                        cutoff_index=5)
+]
+
+discretization = ric.Richmond(configuration=test.configuration,
+                              elements=resolution)
+
+casestudy = cst.CaseStudy(name=name + '.cst',
+                           method=method,
+                           discretization=discretization,
+                           test=test)
+
+casestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True,
+              file_path=filepath)
+
+casestudy.save(save_test=True, file_path=filepath)

### 2025-07-25 experiments/shape/vary/gendata.py

@@ -1,0 +1,57 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+import configuration as cfg
+import inputdata as ipt
+import result as rst
+import draw
+import mom_cg_fft as mom
+
+name = 'vary.cfg'
+NM = NS = 80
+Ro = 4.
+lambda_b = 1.
+epsilon_rb = 1.
+Lx = Ly = 2.
+E0 = 1.
+perfect_dielectric = True
+
+config = cfg.Configuration(name=name, number_measurements=NM, number_sources=NS,
+                           observation_radius=Ro, wavelength=lambda_b,
+                           background_permittivity=epsilon_rb,
+                           image_size=[Ly, Lx], magnitude=E0,
+                           perfect_dielectric=perfect_dielectric)
+
+epsilon_rd = [1.25, 1.5, 1.75, 2., 2.5]
+name = 'vary'
+resolution = (160, 160)
+noise = 5.
+indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
+
+forward = mom.MoM_CG_FFT(tolerance=1e-5, maximum_iterations=5000,
+                         parallelization=True)
+
+for n in range(len(epsilon_rd)):
+
+    print('Test %d... ' % n, end='')
+    test = ipt.InputData(name=name + '%d' % n + '.ipt', configuration=config,
+                         resolution=resolution, noise=noise,
+                         indicators=indicators)
+
+    chi = (epsilon_rd[n]-epsilon_rb)/epsilon_rb
+    l = 0.9
+    position = [.0, .0]
+
+    test.rel_permittivity, _ = draw.star5(
+        l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
+        background_rel_permittivity=epsilon_rb, 
+        object_rel_permittivity=epsilon_rd[n], center=position, rotate=0.
+    )
+    
+    print('solving forward problem... ', end='')
+    _ = forward.solve(test)
+    
+    print('computing DNL... ', end='')
+    test.compute_dnl()
+    
+    print('ok!')
+    test.save(file_path='../../../data/shape/vary/')

### 2025-07-25 experiments/shape/vary/genfigures.py

@@ -1,0 +1,236 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+import casestudy as cst
+import numpy as np
+from matplotlib import pyplot as plt
+import result as rst
+import configuration as cfg
+
+N = 5
+casestudies = [cst.CaseStudy(import_filename='vary%d.cst' % n,
+                             import_filepath='../../../data/shape/vary/') for n in range(N)]
+chi = np.array([.25, .5, .75, 1., 1.5])
+
+plt.rcParams['font.family'] = 'serif'
+plt.rcParams['font.serif'] = 'Times New Roman'
+plt.rcParams['font.size'] = 40
+
+filepath = './figs/'
+config = casestudies[0].test.configuration
+xlabel, ylabel = r'x [$\lambda_b$]', r'y [$\lambda_b$]'
+clb_contrast = r'$|\chi|$'
+xmin, xmax = cfg.get_bounds(config.Lx)
+ymin, ymax = cfg.get_bounds(config.Ly)
+extent = [xmin/config.lambda_b,
+          xmax/config.lambda_b,
+          ymin/config.lambda_b,
+          ymax/config.lambda_b]
+
+result = casestudies[0].results[0]
+X = cfg.get_contrast_map(epsilon_r=result.rel_permittivity,
+                         sigma=result.conductivity,
+                         configuration=config)
+X = np.abs(X)
+plt.figure(figsize=(10, 10))
+plt.imshow(X, origin='lower', extent=extent, cmap='Greys',
+           aspect='equal', vmin=0, vmax=1)
+# plt.colorbar(label=clb_contrast)
+plt.xticks([-1, 0, 1])
+plt.yticks([-1, 0, 1])
+plt.xlabel(xlabel)
+plt.ylabel(ylabel)
+# plt.subplots_adjust(left=0.15, right=0.85, top=0.9, bottom=0.1)
+# plt.show()
+plt.tight_layout(h_pad=0.6, w_pad=0.6)
+plt.savefig(filepath + 'osm_0.eps', format='eps', bbox_inches='tight')
+plt.close()
+
+result = casestudies[1].results[0]
+X = cfg.get_contrast_map(epsilon_r=result.rel_permittivity,
+                         sigma=result.conductivity,
+                         configuration=result.configuration)
+X = np.abs(X)
[…]

### 2025-07-25 experiments/shape/vary/runexperiment.py

@@ -1,0 +1,37 @@
+import sys
+sys.path.insert(1, '../../../eispy2d/library/')
+
+import casestudy as cst
+import richmond as ric
+import inputdata as ipt
+import osm
+import som
+import stopcriteria as stp
+
+name = 'vary'
+resolution = (40, 40)
+file_path = '../../../data/shape/vary/'
+
+tests = []
+for n in range(5):
+    tests.append(ipt.InputData(import_filename=name + '%d' % n + '.ipt',
+                               import_filepath=file_path))
+
+methods = [
+    osm.OrthogonalitySamplingMethod(threshold=.35),
+    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
+                                        cutoff_index=5)
+] 
+
+discretization = ric.Richmond(configuration=tests[0].configuration,
+                              elements=resolution)
+
+for n in range(len(tests)):
+
+    caseestudy = cst.CaseStudy(name=name + '%d' % n + '.cst', method=methods,
+                               discretization=discretization, test=tests[n])
+
+    caseestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True,
+                   file_path=file_path)
+
+    caseestudy.save(save_test=True, file_path=file_path)

### 2025-07-25 experiments/star/gendata.py

@@ -1,52 +1,0 @@
-import sys
-sys.path.insert(1, '../../../eispy2d/library/')
-
-import configuration as cfg
-import inputdata as ipt
-import result as rst
-import draw
-import mom_cg_fft as mom
-
-# Parameters
-name = 'star'
-NM = NS = 80
-Ro = 4.
-lambda_b = 1.
-epsilon_rb = 1.
-Lx = Ly = 2.
-E0 = 1.
-perfect_dielectric = True
-resolution = (120, 120)
-noise = 5.
-indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
-epsilon_rd = 1.25
-l = 0.9
-position = [.0, .0]
-
-config = cfg.Configuration(name=name + '.cfg', number_measurements=NM, 
-                           number_sources=NS, observation_radius=Ro, 
-                           wavelength=lambda_b,
-                           background_permittivity=epsilon_rb,
-                           image_size=[Ly, Lx], magnitude=E0,
-                           perfect_dielectric=perfect_dielectric)
-
-
-test = ipt.InputData(name=name + '.ipt', configuration=config, 
-                     resolution=resolution, noise=noise, indicators=indicators)
-
-chi = (epsilon_rd-epsilon_rb)/epsilon_rb
-
-test.rel_permittivity, _ = draw.star5(
-    l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
-    background_rel_permittivity=epsilon_rb, object_rel_permittivity=epsilon_rd,
-    center=position, rotate=0.
-)
-
-forward = mom.MoM_CG_FFT(tolerance=1e-3, maximum_iterations=5000,
-                         parallelization=True)
-
-_ = forward.solve(test)
-
-test.compute_dnl()
-
-test.save(file_path='./data/')

### 2025-07-25 experiments/star/runexperiment.py

@@ -1,43 +1,0 @@
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-
-import inputdata as ipt
-import casestudy as cst
-import richmond as ric
-import regularization as reg
-import mom_cg_fft as mom
-import stopcriteria as stp
-import lsm
-import osm
-import bim
-import csi
-import som
-
-name = 'star'
-resolution = (40, 40)
-
-test = ipt.InputData(import_filename=name + '.ipt')
-
-method = [
-    lsm.LinearSamplingMethod(alias='lsm',
-                             regularization=reg.ConjugatedGradient(300),
-                             sv_cutoff=None, threshold=.7),
-    osm.OrthogonalitySamplingMethod(threshold=.35),
-    bim.BornIterativeMethod(mom.MoM_CG_FFT(), reg.ConjugatedGradient(300), 
-                            stp.StopCriteria(max_iterations=30)),
-    csi.ContrastSourceInversion(stp.StopCriteria(max_iterations=300)),
-    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
-                                        cutoff_index=5)
-]
-
-discretization = ric.Richmond(configuration=test.configuration,
-                              elements=resolution)
-
-casestudy = cst.CaseStudy(name=name + '.cst',
-                           method=method,
-                           discretization=discretization,
-                           test=test)
-
-casestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True)
-
-casestudy.save(save_test=True)

### 2025-07-25 experiments/vary/gendata.py

@@ -1,57 +1,0 @@
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-import configuration as cfg
-import inputdata as ipt
-import result as rst
-import draw
-import mom_cg_fft as mom
-
-name = 'vary.cfg'
-NM = NS = 80
-Ro = 4.
-lambda_b = 1.
-epsilon_rb = 1.
-Lx = Ly = 2.
-E0 = 1.
-perfect_dielectric = True
-
-config = cfg.Configuration(name=name, number_measurements=NM, number_sources=NS,
-                           observation_radius=Ro, wavelength=lambda_b,
-                           background_permittivity=epsilon_rb,
-                           image_size=[Ly, Lx], magnitude=E0,
-                           perfect_dielectric=perfect_dielectric)
-
-epsilon_rd = [1.25, 1.5, 1.75, 2., 2.5]
-name = 'vary'
-resolution = (160, 160)
-noise = 5.
-indicators = [rst.SHAPE_ERROR, rst.POSITION_ERROR]
-
-forward = mom.MoM_CG_FFT(tolerance=1e-5, maximum_iterations=5000,
-                         parallelization=True)
-
-for n in range(len(epsilon_rd)):
-
-    print('Test %d... ' % n, end='')
-    test = ipt.InputData(name=name + '%d' % n + '.ipt', configuration=config,
-                         resolution=resolution, noise=noise,
-                         indicators=indicators)
-
-    chi = (epsilon_rd[n]-epsilon_rb)/epsilon_rb
-    l = 0.9
-    position = [.0, .0]
-
-    test.rel_permittivity, _ = draw.star5(
-        l, axis_length_x=Lx, axis_length_y=Ly, resolution=resolution,
-        background_rel_permittivity=epsilon_rb, 
-        object_rel_permittivity=epsilon_rd[n], center=position, rotate=0.
-    )
-    
-    print('solving forward problem... ', end='')
-    _ = forward.solve(test)
-    
-    print('computing DNL... ', end='')
-    test.compute_dnl()
-    
-    print('ok!')
-    test.save(file_path='../../data/shape/vary/')

### 2025-07-25 experiments/vary/genfigures.py

@@ -1,236 +1,0 @@
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-import casestudy as cst
-import numpy as np
-from matplotlib import pyplot as plt
-import result as rst
-import configuration as cfg
-
-N = 5
-casestudies = [cst.CaseStudy(import_filename='vary%d.cst' % n,
-                             import_filepath='../../data/shape/vary/') for n in range(N)]
-chi = np.array([.25, .5, .75, 1., 1.5])
-
-plt.rcParams['font.family'] = 'serif'
-plt.rcParams['font.serif'] = 'Times New Roman'
-plt.rcParams['font.size'] = 40
-
-filepath = './figs/'
-config = casestudies[0].test.configuration
-xlabel, ylabel = r'x [$\lambda_b$]', r'y [$\lambda_b$]'
-clb_contrast = r'$|\chi|$'
-xmin, xmax = cfg.get_bounds(config.Lx)
-ymin, ymax = cfg.get_bounds(config.Ly)
-extent = [xmin/config.lambda_b,
-          xmax/config.lambda_b,
-          ymin/config.lambda_b,
-          ymax/config.lambda_b]
-
-result = casestudies[0].results[0]
-X = cfg.get_contrast_map(epsilon_r=result.rel_permittivity,
-                         sigma=result.conductivity,
-                         configuration=config)
-X = np.abs(X)
-plt.figure(figsize=(10, 10))
-plt.imshow(X, origin='lower', extent=extent, cmap='Greys',
-           aspect='equal', vmin=0, vmax=1)
-# plt.colorbar(label=clb_contrast)
-plt.xticks([-1, 0, 1])
-plt.yticks([-1, 0, 1])
-plt.xlabel(xlabel)
-plt.ylabel(ylabel)
-# plt.subplots_adjust(left=0.15, right=0.85, top=0.9, bottom=0.1)
-# plt.show()
-plt.tight_layout(h_pad=0.6, w_pad=0.6)
-plt.savefig(filepath + 'osm_0.eps', format='eps', bbox_inches='tight')
-plt.close()
-
-result = casestudies[1].results[0]
-X = cfg.get_contrast_map(epsilon_r=result.rel_permittivity,
-                         sigma=result.conductivity,
-                         configuration=result.configuration)
-X = np.abs(X)
[…]

### 2025-07-25 experiments/vary/runexperiment.py

@@ -1,36 +1,0 @@
-import sys
-sys.path.insert(1, '../../eispy2d/library/')
-
-import casestudy as cst
-import richmond as ric
-import inputdata as ipt
-import osm
-import som
-import stopcriteria as stp
-
-name = 'vary'
-resolution = (40, 40)
-file_path = '../../data/shape/vary/'
-
-tests = []
-for n in range(5):
-    tests.append(ipt.InputData(import_filename=name + '%d' % n + '.ipt',
-                               import_filepath=file_path))
-
-methods = [
-    osm.OrthogonalitySamplingMethod(threshold=.35),
-    som.SubspaceBasedOptimizationMethod(stp.StopCriteria(max_iterations=30),
-                                        cutoff_index=5)
-] 
-
-discretization = ric.Richmond(configuration=tests[0].configuration,
-                              elements=resolution)
-
-for n in range(len(tests)):
-
-    caseestudy = cst.CaseStudy(name=name + '%d' % n + '.cst', method=methods,
-                               discretization=discretization, test=tests[n])
-
-    caseestudy.run(parallelization=cst.PARALLELIZE_METHOD, pre_save=True)
-
-    caseestudy.save(save_test=True, file_path=file_path)

### 2025-08-12 coverletter/cover_letter.tex
Fixes proposed by Ricardo

@@
 fa-cil-i-tat-ing
+Elec-tro-mag-net-ic
+pub-li-ca-tion
+con-sid-er-a-tion
+As-sess-ment
 }
@@
 % Main content
-I am writing to submit our manuscript entitled \textbf{``Novel Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering''} for consideration for publication in IEEE Transactions on Antennas and Propagation.
+I am writing to submit our manuscript entitled \textbf{``Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering''} for consideration for publication in IEEE Transactions on Antennas and Propagation.
 

### 2025-08-12 paper/main.tex
Fixes proposed by Ricardo

@@
 
-    \title{Novel Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering}
+    \title{Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering}
     \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
@@
 The evaluation of algorithms that solve the related electromagnetic inverse scattering problem typically relies on metrics such as Mean Square Error (MSE) or Structural Similarity (SSIM), which primarily assess contrast estimation accuracy but provide limited insight into the recovery of object geometry and position.
-This paper introduces two novel performance indicators specifically designed to evaluate electromagnetic inverse scattering algorithms: a shape error indicator that quantifies geometric reconstruction accuracy, and a position error indicator that measures object localization precision.
+To address this limitation, this paper introduces two novel performance indicators specifically designed to evaluate electromagnetic inverse scattering algorithms: a shape error indicator that quantifies geometric reconstruction accuracy, and a position error indicator that measures object localization precision.
 The proposed indicators are applicable to both qualitative and quantitative methods, even when they are combined in an experiment.
@@
 These indicators provide useful tools for algorithm development, benchmarking studies, and performance assessment in electromagnetic inverse scattering applications.
+
     \end{abstract}
@@
 
-        It is also worth highlighting the Structural Similarity (SSIM) metric \cite{wang2004image} to quantitatively show the reconstruction visual quality, which is designed to compute the mismatch between reconstructed contrast results and corresponding ground truths both on the pixel-wise level and perceptual level \cite{wang2023push,liu2025exploring}.
+        It is also worth highlighting the Structural Similarity (SSIM) metric \cite{wang2004image} for quantifying reconstruction visual quality, which is designed to compute the mismatch between reconstructed contrast results and corresponding ground truths, both at the pixel-wise level and perceptual level \cite{wang2023push,liu2025exploring}.
 Instead of performing a pixel-by-pixel comparison, this metric considers aspects of luminance, contrast, and structure of any given image.
@@
             This approach has advantages and disadvantages.
-If the reconstructed image contains multiple scatterers, and one or more of them has a contrast below this threshold, the methodology will fail to detect the contour of these objects.
-However, in scenarios where there is only one scatterer in the image, this approach is simple and effective.
-In fact, a single scatterer is the most objective way to test an algorithm's potential in recovering geometry, since the presence of multiple scatterers can degrade the algorithm's performance due to the influence of the induced currents in each scatterer on the scattering of the others.
-Furthermore, this approach poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods.
-Moreover, instead of using the values from the original image, it is more beneficial to use only the values from the reconstructed image, both to isolate the influence of error in the contrast estimate and to apply the metric to qualitative methods that do not estimate contrast.
-If, for some reason, the original contrast function involves soft boundaries of the objects, the threshold might also be applied to the original image.
+If the reconstructed image contains multiple scatterers where one or more has a contrast below this threshold, the methodology will fail to detect the contour of these objects.
+However, in scenarios with a single scatterer, this approach is simple and effective.
+Single scatterer scenarios represent the most objective way to test an algorithm's geometry recovery potential, since multiple scatterers can degrade performance due to mutual current induction effects between objects.
+
+            This approach poses no issues for algorithms capable of accurately capturing contours, such as machine learning-based methods.
+Furthermore, using only values from the reconstructed image (rather than the original image) helps isolate contrast estimation errors and enables metric application to qualitative methods that do not estimate contrast.
+When the original contrast function involves soft object boundaries, the threshold may also be applied to the original image for consistency.
 
@@
 
-            Considering this, the experiments in this section were designed for scenarios involving strong scatterers with small size, where traditional methods cannot adequately recover scatterer geometry.
+            Considering this, the experiments in this section were designed for scenarios involving strong scatterers with small dimensions, where traditional methods cannot adequately recover scatterer geometry.
 Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.
@@
 
-            Considering this, the experiments in this section were designed for scenarios involving strong scatterers with small dimensions, where traditional methods cannot adequately recover scatterer geometry.
-Therefore, the position error indicator $\zeta_P$ serves as a relevant metric for comparing algorithm performance in such challenging scenarios.
-
             For all subsequent experiments, LSM was removed and an other method was introduced.
-Since the analytical solution for scattering from an infinite dielectric cylinder is well-established \cite{harrington2001time}, it becomes possible to determine the optimal circular approximation (defined by radius, position, and contrast) that best fits the scattered field of any single scatterer.
+Since the analytical solution for scattering from an infinite dielectric cylinder is well-established \cite{harrington2001time}, it becomes possible to determine the optimal circular approximation (defined by radius, $x$-$y$ center position, and contrast) that best fits the scattered field of any single scatterer.
 

### 2025-08-12 buildmanuscriptfolder.py
Add a file for generating the manuscript zip file

@@ -1,0 +1,176 @@
+import os
+import zipfile
+import shutil
+import re
+from pathlib import Path
+
+def extract_referenced_figures(tex_file_path):
+    """
+    Extract all figure paths referenced in the LaTeX file
+    """
+    referenced_figures = set()
+    
+    with open(tex_file_path, 'r', encoding='utf-8') as f:
+        content = f.read()
+    
+    # Pattern to match \includegraphics{path} and \input{path}
+    patterns = [
+        r'\\includegraphics(?:\[[^\]]*\])?\{([^}]+)\}',
+        r'\\input\{([^}]+)\}'
+    ]
+    
+    for pattern in patterns:
+        matches = re.findall(pattern, content)
+        for match in matches:
+            # Clean up the path
+            fig_path = match.strip()
+            
+            # Handle different path formats
+            if fig_path.startswith('./'):
+                fig_path = fig_path[2:]  # Remove ./
+            elif fig_path.startswith('../'):
+                fig_path = fig_path[3:]  # Remove ../
+            
+            # Include figures from experiments folder (but not algorithms which are already in paper/)
+            if fig_path.startswith('experiments/'):
+                referenced_figures.add(fig_path)
+    
+    return referenced_figures
+
+def create_readme_file():
+    """
+    Create a README file with compilation instructions
+    """
+    readme_content = """# Manuscript Compilation Instructions
+
+This ZIP file contains all necessary files to compile the paper "Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering".
+
+## Files included:
+- `paper/main.tex` - Main LaTeX document
+- `paper/mybib.bib` - Bibliography file
+- `paper/figs/` - Figures used in the paper (local)
+- `paper/algorithms/` - Algorithm pseudocode files
+- `experiments/` - Figures from experiments referenced in the paper
+
+## Compilation Instructions:
+
+### Option 1: Using pdflatex (recommended)
+```bash
+cd paper
+pdflatex -shell-escape main.tex
+bibtex main
+pdflatex -shell-escape main.tex
+pdflatex -shell-escape main.tex
+```
+
+### Option 2: Using latexmk
+```bash
+cd paper
+latexmk -pdf -shell-escape main.tex
+```
+
+## Requirements:
+- LaTeX distribution with pdflatex
+- BibTeX for bibliography processing
+- epstopdf package (usually included in LaTeX distributions)
[…]

### 2025-08-26 paper/main.tex
Authorship update

@@
     \title{Performance Indicators for Shape and Position Assessment in Electromagnetic Inverse Scattering}
-    \author{Andr\'e Costa Batista, Ricardo Adriano, and Lucas S. Batista
+    \author{Andr\'e Costa Batista and Ricardo Adriano
     \thanks{This work was supported in part by the Brazilian agency CAPES (Coordination for the Improvement of Higher Education Personnel) under Grant 88887.463864/2019-00, the scholarship FAPEMIG-CNPQ (process APQ-06716-24), and CNPq (The National Council for Scientific and Technological Development).}
@@
 C.
-Batista, R.
-Adriano, and L.
-S.
-Batista are with the Department of Electrical Engineering, Universidade Federal de Minas Gerais, Belo Horizonte, MG 31270-901, Brazil (e-mail: andre-costa@ufmg.br; rluiz@ufmg.br; lusoba@ufmg.br).
+Batista and R.
+Adriano are with the Department of Electrical Engineering, Universidade Federal de Minas Gerais, Belo Horizonte, MG 31270-901, Brazil (e-mail: andre-costa@ufmg.br; rluiz@ufmg.br).
 A.
 C.
-Batista and L.
-S.
-Batista are also with Operations Research and Complex Systems Laboratory (ORCS Lab), Belo Horizonte, MG, Brazil.}}
+Batista is also with Operations Research and Complex Systems Laboratory (ORCS Lab), Belo Horizonte, MG, Brazil.}}
 
@@
 
-    % \section*{Acknowledgment}
-
-    %     Use the singular heading even if you have many acknowledgments.
-In most cases, sponsor and financial support acknowledgments are placed in the  unnumbered footnote on the first page, not here.
-
-    %     The authors would like to thank the reviewers for their valuable contributions.
-This work was supported in part by the Brazilian agencies FAPEMIG, CNPq, and CAPES (Coordination for the Improvement of Higher Education Personnel).
+    \section*{Acknowledgment}
+
+    The authors would like to thank Lucas S. Batista for his guidance and manuscript review.
 
